---
title: "10_projection_ensemble_17C"
date: 1st version "2024-12-10" this version"2025-10-27"
author: Marina Christofidis (marina.christofidis@griffithuni.edu.au)

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages

```{r}
library(terra)
library(tidyverse)
library(rasterVis)
library(here)
library(dplyr)
library(purrr)
library(stringr)
library(readr)
library(tmap)
library(leaflet)
library(sf)
library(ggplot2)
library(gganimate)
```


#Loop to find how many of the projection agree by decade and for each SSP that the amount of days over 17C is optimal or is similar to the amount of days over 17C in historical data in current aquaculture areas

```{r}
ssps <- c("ssp119", "ssp126", "ssp245", "ssp370", "ssp585") # Name the SSP projections from IPCC

for (i in 1:length(ssps)) { # For each SSP
  names <- list.files(here("output_data"), pattern = ssps[[i]], full.names = T) # Find files
  names2 <- names[grep("Optimal", names)] # Filter for files named "Optimal"
  
  for (z in 2:9) { # Loop over layers in future projections (excluding past, layer 1)
    all <- rast() # Reset the raster stack for each decade
    
    for (k in 1:length(names2)) { # Loop over the filtered files
      print(k)
      r <- rast(names2[[k]]) # Load the raster
      r2 <- r[[z]] # Extract the specific layer
      
      # Rename layers (decades)
      current_names <- names(r2)
      numeric_part <- as.numeric(sub("X", "", current_names)) # Remove the "X" prefix
      decade_labels <- paste0((numeric_part * 10) + 1, "_", (numeric_part * 10) + 10)
      names(r2) <- decade_labels # Assign new decade names
      
      all <- c(all, r2) # Add the layer to the raster stack
      decade <- names(r2) # Get the renamed decade labels
    }
    
    # Sum all projections to calculate the number of models that agree
    sum_r <- app(all, fun = sum, na.rm = T)
    
    # Save the result as a raster
    writeRaster(sum_r, 
                here(paste0("output_data/Results/Optimal_", ssps[[i]], "_", decade, ".tif")), 
                overwrite = TRUE)
  }
}
```
# to Map all the rasters created we need to Load necessary vectors

```{r}
finfish_aqua_TAS<-vect("D:/Documents_HD/USC_Climate_smart_aquaculture/R_Code/raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp")
```

```{r}
daysover_17C_historical<- read_rds(here("raw_data/Data17/jplMUR41_daysover_17C_TAS_20110101-20201231.rds")) %>%
  unwrap()
plot(daysover_17C_historical)
```

```{r}
finfish_aqua_TAS_reproj<-project(finfish_aqua_TAS, daysover_17C_historical)
```

```{r}
finfish_aqua_TAS_sf <- st_as_sf(finfish_aqua_TAS_reproj)
```
```{r}
finfish_aqua_TAS_df<- as.data.frame(finfish_aqua_TAS_reproj, xy= TRUE)
```

#loop to get all the files generated before and plot them and then save them
```{r}
# Define SSP projections
ssps <- c("ssp119", "ssp126", "ssp245", "ssp370", "ssp585")

# Loop through each SSP
for (i in seq_along(ssps)) {
  # Define file pattern to locate saved rasters
  pattern <- paste0("Optimal_", ssps[i])
  
  # List raster files matching the pattern
  raster_files <- list.files(here("output_data/Results"), pattern = pattern, full.names = TRUE)
  
  # Loop through each raster file
  for (raster_file in raster_files) {
    # Load the raster
    raster <- rast(raster_file)
    
    # Generate plot title based on file name
    file_name <- tools::file_path_sans_ext(basename(raster_file)) # Get the base file name without extension
    decade <- gsub(".*_", "", file_name) # Extract the decade info from the file name
    title <- paste0("Number of models that agree area is \n an analogue in ", decade, "\n projection ", toupper(ssps[i]))
    
    # Generate the tmap plot
    plot <- tm_shape(raster) +
      tm_raster(style = "cont",
                breaks = seq(min(raster[], na.rm = TRUE),
                             max(raster[], na.rm = TRUE),
                             length.out = nlyr(raster) + 1),
                palette = "-viridis",
                title = title) +
      tm_shape(finfish_aqua_TAS_sf) + # places where the is aquaculture currently (check if you have already loaded)
      tm_borders(col = "black") +
      tm_basemap("Esri.WorldImagery") +
      tm_layout(legend.outside = TRUE,
                legend.outside.position = "right",
                legend.outside.size = 0.30)
    
    # Save the plot
    output_plot_path <- here("Figures/Plots", paste0(file_name, ".png"))
    tmap_save(plot, output_plot_path, width = 8, height = 6, dpi = 300)
    
    # Print a message to track progress
    message("Saved plot: ", output_plot_path)
  }
}

```

#Loop to find how many of the projection agree by decade and for each SSP that the amount of days over 17C is Suitable or is similar to the amount of days over 17C in historical data in current aquaculture areas

```{r}
ssps <- c("ssp119", "ssp126", "ssp245", "ssp370", "ssp585") # Name the SSP projections from IPCC

for (i in 1:length(ssps)) { # For each SSP
  names <- list.files(here("output_data"), pattern = ssps[[i]], full.names = T) # Find files
  names2 <- names[grep("Suitable", names)] # Filter for files named "Optimal"
  
  for (z in 2:9) { # Loop over layers in future projections (excluding past, layer 1)
    all <- rast() # Reset the raster stack for each decade
    
    for (k in 1:length(names2)) { # Loop over the filtered files
      print(k)
      r <- rast(names2[[k]]) # Load the raster
      r2 <- r[[z]] # Extract the specific layer
      
      # Rename layers (decades)
      current_names <- names(r2)
      numeric_part <- as.numeric(sub("X", "", current_names)) # Remove the "X" prefix
      decade_labels <- paste0((numeric_part * 10) + 1, "_", (numeric_part * 10) + 10)
      names(r2) <- decade_labels # Assign new decade names
      
      all <- c(all, r2) # Add the layer to the raster stack
      decade <- names(r2) # Get the renamed decade labels
    }
    
    # Sum all projections to calculate the number of models that agree
    sum_r <- app(all, fun = sum, na.rm = T)
    
    # Save the result as a raster
    writeRaster(sum_r, 
                here(paste0("output_data/Results/Suitable_", ssps[[i]], "_", decade, ".tif")), 
                overwrite = TRUE)
  }
}
```
#loop to get all the files generated before and plot them and then save them
```{r}
# Define SSP projections
ssps <- c("ssp119", "ssp126", "ssp245", "ssp370", "ssp585")

# Loop through each SSP
for (i in seq_along(ssps)) {
  # Define file pattern to locate saved rasters
  pattern <- paste0("Suitable_", ssps[i])
  
  # List raster files matching the pattern
  raster_files <- list.files(here("output_data/Results"), pattern = pattern, full.names = TRUE)
  
  # Loop through each raster file
  for (raster_file in raster_files) {
    # Load the raster
    raster <- rast(raster_file)
    
    # Generate plot title based on file name
    file_name <- tools::file_path_sans_ext(basename(raster_file)) # Get the base file name without extension
    decade <- gsub(".*_", "", file_name) # Extract the decade info from the file name
    title <- paste0("Number of models that agree area is \n an analogue in ", decade, "\n projection ", toupper(ssps[i]))
    
    # Generate the tmap plot
    plot <- tm_shape(raster) +
      tm_raster(style = "cont",
                breaks = seq(min(raster[], na.rm = TRUE),
                             max(raster[], na.rm = TRUE),
                             length.out = nlyr(raster) + 1),
                palette = "-viridis",
                title = title) +
      tm_shape(finfish_aqua_TAS_sf) + # places where the is aquaculture currently (check if you have already loaded)
      tm_borders(col = "black") +
      tm_basemap("Esri.WorldImagery") +
      tm_layout(legend.outside = TRUE,
                legend.outside.position = "right",
                legend.outside.size = 0.30)
    
    # Save the plot
    output_plot_path <- here("Figures/Plots", paste0(file_name, ".png"))
    tmap_save(plot, output_plot_path, width = 8, height = 6, dpi = 300)
    
    # Print a message to track progress
    message("Saved plot: ", output_plot_path)
  }
}

```

# go to 10_B_projection_ensemble_21C_EF_oct25
