---
title: "11_Overlapping Suitable and optimal stress scenarios(17C) with analogues(21.5C)"
date: 1st version "2025-01-06" this version"2025-10-27"
author: Marina Christofidis (marina.christofidis@griffithuni.edu.au)

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(terra)
library(tidyverse)
library(rasterVis)
library(here)
library(dplyr)
library(purrr)
library(stringr)
library(readr)
library(tmap)
library(leaflet)
library(sf)
library(ggplot2)
library(magick)
library(reshape2)
library(viridisLite)
```

#get all the results of the analogues and overlap with results of stress being (1) suitable and then (2) Optimal stress levels.
```{r}
# Required libraries
library(terra)
library(here)

# List of SSPs and Patterns
ssps <- c("ssp119", "ssp126", "ssp245", "ssp370", "ssp585")  # SSP scenarios
patterns <- c("suitable", "optimal")                        # Patterns to combine with "analogue"

# Define folders
Results_folder <- here("output_data/Results")  # Input folder
Combined_results_folder <- here("output_data/Combined_Results")  # Output folder

# Create the output folder if it doesn't exist
if (!dir.exists(Combined_results_folder)) {
  dir.create(Combined_results_folder, recursive = TRUE)
}

# Loop through each SSP
for (ssp in ssps) {
  
  # Loop through decades with ranges like 2021_2030
  for (start_year in seq(2021, 2091, by = 10)) {  # Start years for decades
    end_year <- start_year + 9
    decade_range <- paste0(start_year, "_", end_year)  # e.g., "2021_2030"
    
    # Load analogue raster
    analogue_file <- file.path(Results_folder, paste0("analogue_", ssp, "_", decade_range, ".tif"))
    if (!file.exists(analogue_file)) {
      print(paste("Missing analogue file:", analogue_file))  # Debug message
      next  # Skip if analogue file is missing
    }
    analogue_raster <- rast(analogue_file)  # Load analogue raster
    
    # Process each pattern to combine with "analogue"
    for (pattern in patterns) {
      
      # Load pattern raster
      pattern_file <- file.path(Results_folder, paste0(pattern, "_", ssp, "_", decade_range, ".tif"))
      if (!file.exists(pattern_file)) {
        print(paste("Missing", pattern, "file:", pattern_file))  # Debug message
        next  # Skip if pattern file is missing
      }
      pattern_raster <- rast(pattern_file)  # Load pattern raster
      
      # Check raster compatibility
      if (!compareGeom(analogue_raster, pattern_raster)) {
        print(paste("Incompatible rasters for:", ssp, decade_range, pattern))  # Debug message
        next
      }
      
      # Combine the rasters (e.g., sum)
      combined_raster <- analogue_raster + pattern_raster
      
      # Save combined raster
      output_file <- file.path(Combined_results_folder, paste0(ssp, "_", decade_range, "_analogue_", pattern, "_combined.tif"))
      writeRaster(combined_raster, output_file, overwrite = TRUE)
      print(paste("Saved:", output_file))  # Debug message
    }
  }
}
```
#creating the figures of the results- combined analogue with Optimal stress and combined analogue with Suitable stress

```{r}
# Define folders
Combined_results_folder <- here("output_data/Combined_Results")
Figures_folder <- here("Figures/Combined_results_ggplot")

# Create output folder for Figures if it doesn't exist
if (!dir.exists(Figures_folder)) {
  dir.create(Figures_folder)
}

# List all combined raster files
combined_files <- list.files(Combined_results_folder, pattern = "\\.tif$", full.names = TRUE)

# Loop through each combined raster file
for (file in combined_files) {
  # Read the raster
  raster_data <- rast(file)
  
  # Convert raster to data frame for ggplot
  raster_df <- as.data.frame(raster_data, xy = TRUE)  # Include coordinates
  
  
  # Extract filename components for labeling
  file_name <- basename(file)
  parts <- unlist(strsplit(file_name, "_"))
  ssp <- parts[1]  # e.g., "ssp119"
  decade <- parts[2]  # e.g., "2020_2030"
  pattern <- parts[4]  # e.g., "Optimal"
  
  # Plot using ggplot
  p <- ggplot(data = raster_df, aes(x = x, y = y, fill = sum)) +  # Use 'sum' for the raster values
    geom_tile() +
    scale_fill_viridis_c(option = "viridis", na.value = "white") +  # Viridis color scale
    labs(
      title = paste0("Combined Result: ", ssp, " - ", decade, " - ", pattern),
      fill = "Value"
    ) +
    theme_minimal() +
    coord_fixed()  # Preserve aspect ratio
  
  # Save the figure
  output_figure <- file.path(Figures_folder, paste0(file_name, ".png"))
  ggsave(output_figure, plot = p, width = 8, height = 6, dpi = 300)
}

print("Figures saved successfully!")
```


#Saving all figures of the combined results with tmap instead of ggplot-using -Viridis color palette
```{r}

# Define folders
Combined_results_folder <- here("output_data/Combined_Results")
Figures_folder <- here("Figures/Combined_results_tmap/minusviridis")

# Create output folder for Figures if it doesn't exist
if (!dir.exists(Figures_folder)) {
  dir.create(Figures_folder, recursive = TRUE)
}

# List all combined raster files
combined_files <- list.files(Combined_results_folder, pattern = "\\.tif$", full.names = TRUE)

# Loop through each combined raster file
for (file in combined_files) {
  # Read the raster
  raster <- rast(file)  # Use raster directly, not data frame
  
  # Extract filename components for labeling
  file_name <- basename(file)
  parts <- unlist(strsplit(file_name, "_"))
  ssp <- parts[1]  # e.g., "ssp119"
  decade_range <- parts[2]  # e.g., "2021_2030"
  pattern <- parts[4]  # e.g., "optimal"
  title <- paste0("Combined Result: ", ssp, " - ", decade_range, " - ", pattern)
  
  # Create tmap plot
  tmapplot <- tm_shape(raster) +  # Use SpatRaster here
    tm_raster(
      style = "cont",
      breaks = seq(min(raster[], na.rm = TRUE),
                             max(raster[], na.rm = TRUE),
                             length.out = nlyr(raster) + 1),
      palette = "-viridis",
      title = "Value"
    ) +
    tm_basemap("Esri.WorldImagery") +  # Optional basemap
    tm_shape(finfish_aqua_TAS_sf) + # places where the is aquaculture currently (check if you have already loaded)
      tm_borders(col = "black") +
    tm_layout(
      title = title,
      legend.outside = TRUE,
      legend.outside.position = "right",
      legend.outside.size = 0.30
    )
  
  # Save the figure
  output_figure <- file.path(Figures_folder, paste0(file_name, ".png"))
  tmap_save(tmapplot, filename = output_figure, width = 8, height = 6, dpi = 300)
}

print("Figures saved successfully!")
```
#valing all in tmap with viridis 

```{r}

# Define folders
Combined_results_folder <- here("output_data/Combined_Results")
Figures_folder <- here("Figures/Combined_results_tmap/viridis")

# Create output folder for Figures if it doesn't exist
if (!dir.exists(Figures_folder)) {
  dir.create(Figures_folder, recursive = TRUE)
}

# List all combined raster files
combined_files <- list.files(Combined_results_folder, pattern = "\\.tif$", full.names = TRUE)

# Loop through each combined raster file
for (file in combined_files) {
  # Read the raster
  raster <- rast(file)  # Use raster directly, not data frame
  
  # Extract filename components for labeling
  file_name <- basename(file)
  parts <- unlist(strsplit(file_name, "_"))
  ssp <- parts[1]  # e.g., "ssp119"
  decade_range <- parts[2]  # e.g., "2021_2030"
  pattern <- parts[4]  # e.g., "optimal"
  title <- paste0("Combined Result: ", ssp, " - ", decade_range, " - ", pattern)
  
  # Create tmap plot
  tmapplot <- tm_shape(raster) +  # Use SpatRaster here
    tm_raster(
      style = "cont",
      breaks = seq(min(raster[], na.rm = TRUE),
                             max(raster[], na.rm = TRUE),
                             length.out = nlyr(raster) + 1),
      palette = "viridis",
      title = "Value"
    ) +
    tm_basemap("Esri.WorldImagery") +  # Optional basemap
    tm_shape(finfish_aqua_TAS_sf) + # places where the is aquaculture currently (check if you have already loaded)
      tm_borders(col = "black") +
    tm_layout(
      title = title,
      legend.outside = TRUE,
      legend.outside.position = "right",
      legend.outside.size = 0.30
    )
  
  # Save the figure
  output_figure <- file.path(Figures_folder, paste0(file_name, ".png"))
  tmap_save(tmapplot, filename = output_figure, width = 8, height = 6, dpi = 300)
}

print("Figures saved successfully!")
```


#saving all in tmap with other color- inferno palette
```{r}

# Define folders
Combined_results_folder <- here("output_data/Combined_Results")
Figures_folder <- here("Figures/Combined_results_tmap/inferno")

# Create output folder for Figures if it doesn't exist
if (!dir.exists(Figures_folder)) {
  dir.create(Figures_folder, recursive = TRUE)
}

# List all combined raster files
combined_files <- list.files(Combined_results_folder, pattern = "\\.tif$", full.names = TRUE)

# Loop through each combined raster file
for (file in combined_files) {
  # Read the raster
  raster <- rast(file)  # Use raster directly, not data frame
  
  # Extract filename components for labeling
  file_name <- basename(file)
  parts <- unlist(strsplit(file_name, "_"))
  ssp <- parts[1]  # e.g., "ssp119"
  decade_range <- parts[2]  # e.g., "2020_2030"
  pattern <- parts[4]  # e.g., "optimal"
  title <- paste0("Combined Result: ", ssp, " - ", decade_range, " - ", pattern)
  
  # Create tmap plot
  tmapplot <- tm_shape(raster) +  # Use SpatRaster here
    tm_raster(
      style = "cont",
      breaks = seq(min(raster[], na.rm = TRUE),
                             max(raster[], na.rm = TRUE),
                             length.out = nlyr(raster) + 1),
      palette = "inferno",
      title = "Value"
    ) +
    tm_basemap("Esri.WorldImagery") +  # Optional basemap
    tm_shape(finfish_aqua_TAS_sf) + # places where the is aquaculture currently (check if you have already loaded)
      tm_borders(col = "black") +
    tm_layout(
    title = title,
        legend.outside = TRUE,
      legend.outside.position = "right",
      legend.outside.size = 0.30
    )
  
  # Save the figure
  output_figure <- file.path(Figures_folder, paste0(file_name, ".png"))
  tmap_save(tmapplot, filename = output_figure, width = 8, height = 6, dpi = 300)
}

print("Figures saved successfully!")
```

```{r}
#saving all in tmap with other color -inferno palette

# Define folders
Combined_results_folder <- here("output_data/Combined_Results")
Figures_folder <- here("Figures/Combined_results_tmap/minusinferno")

# Create output folder for Figures if it doesn't exist
if (!dir.exists(Figures_folder)) {
  dir.create(Figures_folder, recursive = TRUE)
}

# List all combined raster files
combined_files <- list.files(Combined_results_folder, pattern = "\\.tif$", full.names = TRUE)

# Loop through each combined raster file
for (file in combined_files) {
  # Read the raster
  raster <- rast(file)  # Use raster directly, not data frame
  
  # Extract filename components for labeling
  file_name <- basename(file)
  parts <- unlist(strsplit(file_name, "_"))
  ssp <- parts[1]  # e.g., "ssp119"
  decade_range <- parts[2]  # e.g., "2020_2030"
  pattern <- parts[4]  # e.g., "optimal"
  title <- paste0("Combined Result: ", ssp, " - ", decade_range, " - ", pattern)
  
  # Create tmap plot
  tmapplot <- tm_shape(raster) +  # Use SpatRaster here
    tm_raster(
      style = "cont",
      breaks = seq(min(raster[], na.rm = TRUE),
                             max(raster[], na.rm = TRUE),
                             length.out = nlyr(raster) + 1),
      palette = "-inferno",
      title = "Value"
    ) +
    tm_basemap("Esri.WorldImagery") +  # Optional basemap
    tm_shape(finfish_aqua_TAS_sf) + # places where the is aquaculture currently (check if you have already loaded)
      tm_borders(col = "black") +
    tm_layout(
    title = title,
        legend.outside = TRUE,
      legend.outside.position = "right",
      legend.outside.size = 0.30
    )
  
  # Save the figure
  output_figure <- file.path(Figures_folder, paste0(file_name, ".png"))
  tmap_save(tmapplot, filename = output_figure, width = 8, height = 6, dpi = 300)
}

print("Figures saved successfully!")
```

#magma
```{r}

# Define folders
Combined_results_folder <- here("output_data/Combined_Results")
Figures_folder <- here("Figures/Combined_results_tmap/magma")

# Create output folder for Figures if it doesn't exist
if (!dir.exists(Figures_folder)) {
  dir.create(Figures_folder, recursive = TRUE)
}

# List all combined raster files
combined_files <- list.files(Combined_results_folder, pattern = "\\.tif$", full.names = TRUE)

# Loop through each combined raster file
for (file in combined_files) {
  # Read the raster
  raster <- rast(file)  # Use raster directly, not data frame
  
  # Extract filename components for labeling
  file_name <- basename(file)
  parts <- unlist(strsplit(file_name, "_"))
  ssp <- parts[1]  # e.g., "ssp119"
  decade_range <- parts[2]  # e.g., "2020_2030"
  pattern <- parts[4]  # e.g., "optimal"
  title <- paste0("Combined Result: ", ssp, " - ", decade_range, " - ", pattern)
  
  # Create tmap plot
  tmapplot <- tm_shape(raster) +  # Use SpatRaster here
    tm_raster(
      style = "cont",
      breaks = seq(min(raster[], na.rm = TRUE),
                             max(raster[], na.rm = TRUE),
                             length.out = nlyr(raster) + 1),
      palette = "magma",
      title = "Value"
    ) +
    tm_basemap("Esri.WorldImagery") +  # Optional basemap
    tm_shape(finfish_aqua_TAS_sf) + # places where the is aquaculture currently (check if you have already loaded)
      tm_borders(col = "black") +
    tm_layout(
    title = title,
        legend.outside = TRUE,
      legend.outside.position = "right",
      legend.outside.size = 0.30
    )
  
  # Save the figure
  output_figure <- file.path(Figures_folder, paste0(file_name, ".png"))
  tmap_save(tmapplot, filename = output_figure, width = 8, height = 6, dpi = 300)
}

print("Figures saved successfully!")
```

   
