---
title: "Reclassification of the ESM agreement and maps in Viridis-confidence level assessment"
date: first version"2025-01-16"/ this version 27 Oct 2025
author: Marina Christofidis (marina.christofidis@griffithuni.edu.au)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Summary: In this code we create the maps of the agreement between ESMs and after that we create a composite map with every decade in the X axis and SSPs in the Y axis WITH ONLY CLIMATE ANALOGUES WITHOUT CONSIDERING CONSTRAINTS.

#upload possible packages needed 
```{r}
library(terra)
library(here)
library(tidyverse)
library(rasterVis)
library(here)
library(dplyr)
library(purrr)
library(stringr)
library(readr)
library(tmap)
library(leaflet)
library(sf)
library(ggplot2)
library(reshape2)
library(viridisLite)
```

#get all the results of the combined analogues and stress category (we named as patterns) such as suitable (1) and then (2) Optimal and sum the amount of models that agree making it more complex we defined as a 
#No analogue (<25%),
#Low confidence analogue (≥25% analogue<50% ), 
#Medium confidence analogue (≥50%<analog<75%),
#High confidence analogue (≥75%)

```{r}
#after loading required libraries

# Define SSPs and Patterns
ssps <- c("ssp119", "ssp126", "ssp245", "ssp370", "ssp585")  # SSP scenarios
patterns <- c("suitable", "optimal")                        # Patterns to combine with "analogue"

# Define Input and Output Directories
Results_folder <- here("output_data/Combined_Results")  # Input folder
ESM_Agreement_results_folder <- here("output_data/Combined_Results/ESM_agreement")  # Output folder

# Create the output folder if it doesn't exist
if (!dir.exists(ESM_Agreement_results_folder)) {
  dir.create(ESM_Agreement_results_folder, recursive = TRUE)
}

# Loop through each SSP
for (ssp in ssps) {
  
  # Loop through each pattern
  for (pattern in patterns) {
    
    # Loop through decades with ranges like 2021_2030
    for (start_year in seq(2021, 2091, by = 10)) {  # Start years for decades
      end_year <- start_year + 9
      decade_range <- paste0(start_year, "_", end_year)  # e.g., "2021_2030"
      
      # Construct the file path for the combined analogue raster
      combined_analogue_file <- file.path(Results_folder, paste0(ssp, "_", decade_range, "_analogue_", pattern, "_combined.tif"))
      
      # Check if the file exists
      if (!file.exists(combined_analogue_file)) {
        message(paste("Missing analogue file:", combined_analogue_file))  # Debug message
        next  # Skip to the next iteration if the file is missing
      }
      
      # Load the analogue raster
      analogue_raster <- rast(combined_analogue_file)
      
      # Determine the maximum number of models based on SSP
      max_models <- switch(ssp, 
                     "ssp119" = 8, 
                     18)  # For all other SSPs, max_models is set to 18
      
      # Define reclassification matrix
      reclass_matrix <- matrix(c(
        0, floor(0.25 * max_models), 0,  # <25% -> No-analogue
        floor(0.25 * max_models),mean(0.50 * max_models) , 1, #≥25% analogue<50% agreement -> low confidence analog
        mean(0.50 * max_models), ceiling (0.75 * max_models), 2,# ≥50%<analog<75% -> medium confidence analog
        ceiling(0.75 * max_models), max_models, 3  # ≥75% agreement -> High confidence analogue
      ), ncol = 3, byrow = TRUE)
      
      # Reclassify the raster
      reclassified_raster <- classify(analogue_raster, reclass_matrix, include.lowest = TRUE)
      
      # Save the reclassified raster
      output_file <- file.path(ESM_Agreement_results_folder, paste0(ssp, "_", decade_range, "_analogue_", pattern, "_ESM_Agreement.tif"))
      writeRaster(reclassified_raster, output_file, overwrite = TRUE)
      message(paste("Saved:", output_file))  # Debug message
    }
  }
}

```

#plot the legend by itself to use in figures and presentations
```{r}

plot.new()  # Creates a blank plot
legend("center", 
       legend = c("No analogue (<25%)", "Low confidence analogue (≥25% analogue<50% )", 
                  "Medium confidence analogue (≥50%<analog<75%)", "High confidence analogue (≥75%)"), 
       fill = c("#fcd225", "#c03a83", "#8606a6", "#0d0887"), 
       bty = "n", cex = 1.2)  # Larger text for clarity
dev.off()
```

#another legend type could be 
```{r}

plot.new()  # Creates a blank plot
legend("center", 
       legend = c("25% or less", 
                  "25% to less than 50%", 
                  "50% to less than 75%", 
                  "75% or more"), 
       fill = c("#fcd225", "#c03a83", "#8606a6", "#0d0887"), 
        title = "percentage of ESMs agree it's an analogue",  # Add legend title
       bty = "n", cex = 1.2)  # Larger text for clarity
dev.off()
```
#"No analogue (<25%)", "Low confidence analogue (≥25% analogue<50% )", 
                  "Medium confidence analogue (≥50%<analog<75%)", "High confidence analogue (≥75%)"
```{r}
plot.new()  # Creates a blank plot
legend("topright", inset = c(0.2, 0),  # Move it further outside
       legend = c("No analogue (<25%)",
                  "Low confidence analogue (≥25% analogue<50% )", 
                  "Medium confidence analogue (≥50%<analog<75%)",
                  "High confidence analogue (≥75%)"), 
       fill = c("#fcd225", "#c03a83", "#8606a6", "#0d0887"), 
       title = "ESMs agree it's an analogue",  # Add legend title
       title.adj = 0,  # Align title to the left
       xpd = TRUE)
```


#plot the figures themselves in Viridis with tasmania as an overlay

```{r}
# Load Required Libraries
library(terra)
library(here)
library(sf)  # For reading shapefiles

# Define Input and Output Directories
ESM_Agreement_results_folder <- here("output_data/Combined_Results/ESM_agreement")
Plots_folder <- here("Figures/ESM_Agreement_Plots_viridis")

# Define Tasmania shapefile path 
tasmania_shapefile_path <- here("raw_data/tassie_shp.gpkg")  

# Create Output Directory for Plots if it doesn't exist
if (!dir.exists(Plots_folder)) {
  dir.create(Plots_folder, recursive = TRUE)
}

# Load Tasmania shapefile (only if it exists)
tasmania_sf <- NULL
if (file.exists(tasmania_shapefile_path)) {
  tasmania_sf <- st_read(tasmania_shapefile_path, quiet = TRUE)
  message("Tasmania shapefile loaded successfully")
} else {
  message("Tasmania shapefile not found at: ", tasmania_shapefile_path)
  message("Please update the path or the plots will be created without the Tasmania overlay")
}

# List All Reclassified Raster Files
raster_files <- list.files(ESM_Agreement_results_folder, pattern = "\\.tif$", full.names = TRUE)

# Loop Through Each Raster File
for (file in raster_files) {
  # Read the Raster
  reclassified_raster <- rast(file)
  
  # Extract Filename Components for Plot Title
  file_name <- basename(file)
  parts <- unlist(strsplit(file_name, "_"))
  ssp <- parts[1]  # e.g., "ssp119"
  decade_range <- paste(parts[2], parts[3], sep = "_")  # Ensure full range (e.g., "2021_2030")
  pattern <- parts[5]  # e.g., "optimal"
  
  # Define Plot File Path
  plot_file <- file.path(Plots_folder, paste0(ssp, "_", decade_range, "_analogue_", pattern, "_ESM_Agreement_Plot_viridis.png"))
  
  # Open PNG Device
  png(filename = plot_file, width = 800, height = 600)
  
  # Adjust margins: 
  par(mar = c(1, 1, 1, 1))  # c(bottom, left, top, right)
  
  # Plot the raster without legend
  plot(reclassified_raster, col = c("#fcd225", "#c03a83", "#8606a6", "#0d0887"), legend = FALSE)
  
  # Overlay Tasmania shapefile  if available
  if (!is.null(tasmania_sf)) {
    plot(st_geometry(tasmania_sf), col = "white", border = "#373737", lwd = 0.5, add = TRUE)
  }
  
  # Add legend
  legend("topright", inset = c(-0.25, 0),  # Move it further outside
         legend = c("25% or less", 
                    "25% to 50%", 
                    "50% to 75%", 
                    "75% or more"), 
         fill = c("#fcd225", "#c03a83", "#8606a6", "#0d0887"), 
         title = "ESMs agree it's an analogue",  # Add legend title
         title.adj = 0,  # Align title to the left
         xpd = TRUE)
  
  # Close PNG Device
  dev.off()
  
  # Debug Message
  message(paste("Saved plot:", plot_file))
}

print("All plots saved successfully!")
```

#Composite maps with Viridis
```{r}
# Create composite map for ESM Agreement plots with updated legend
#--------------------------------------------------------------------------
library(png)
library(grid)
library(webshot2)
library(here)

# Define input and output directories
plots_folder <- here("Figures/ESM_Agreement_Plots_viridis")
output_folder <- here("Figures/ESM_Agreement_Plots_viridis")

# Create output directory if it doesn't exist
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)
}

# List all PNG files in the plots folder
plot_files <- list.files(plots_folder, pattern = ".*_ESM_Agreement_Plot_viridis\\.png$", full.names = TRUE)

if (length(plot_files) == 0) {
  stop("No ESM Agreement plot files found in ", plots_folder)
}

# Extract metadata from filenames
extract_metadata <- function(filename) {
  basename <- basename(filename)
  parts <- strsplit(basename, "_")[[1]]
  
  # Extract SSP, decade, and pattern
  ssp <- parts[1]
  decade_start <- parts[2]
  decade_end <- parts[3]
  decade_range <- paste(decade_start, decade_end, sep="_")
  pattern <- parts[5]  # "optimal" or "suitable"
  
  return(list(
    ssp = ssp,
    decade = decade_range,
    pattern = pattern,
    path = filename
  ))
}

# Get metadata for all files
all_metadata <- lapply(plot_files, extract_metadata)

# Get unique patterns, SSPs, and decades
patterns <- unique(sapply(all_metadata, function(x) x$pattern))
ssps <- unique(sapply(all_metadata, function(x) x$ssp))
decades <- unique(sapply(all_metadata, function(x) x$decade))

# Sort them
ssps <- sort(ssps)
decades <- sort(decades)

# Process each pattern separately
for (pattern in patterns) {
  cat("Creating composite map for pattern:", pattern, "\n")
  
  # Filter files for this pattern
  pattern_metadata <- all_metadata[sapply(all_metadata, function(x) x$pattern == pattern)]
  
  # Create individual maps directory for this pattern
  individual_maps_dir <- file.path(output_folder, paste0("individual_maps_", pattern))
  if (!dir.exists(individual_maps_dir)) {
    dir.create(individual_maps_dir, recursive = TRUE)
  }
  
  # Process each file to create standardized individual maps
  for (metadata in pattern_metadata) {
    # Extract information
    ssp <- metadata$ssp
    decade <- metadata$decade
    orig_path <- metadata$path
    
    # Define output path for the standardized image
    output_path <- file.path(individual_maps_dir, 
                            paste0(pattern, "_", ssp, "_", decade, ".png"))
    
    # Simply copy the file (we're assuming the images are already well-formatted)
    file.copy(orig_path, output_path, overwrite = TRUE)
  }
  
  # Create HTML for composite view
  html_file <- file.path(output_folder, paste0("ESM_Agreement_composite_", pattern, ".html"))
  
  html_content <- c(
    "<!DOCTYPE html>",
    "<html>",
    "<head>",
    paste0("<title>ESM Agreement Composite Map: ", pattern, "</title>"),
    "<style>",
    "body { font-family: Arial, sans-serif; margin: 20px; }",
    "table { border-collapse: collapse; width: 100%; border: 1px solid #ddd; }",
    "th, td { padding: 0; margin: 0; }",
    "th { background-color: #f2f2f2; padding: 8px; font-weight: bold; text-align: center; }",
    "td { position: relative; height: 0; padding-bottom: 12%; /* Force aspect ratio */ }",
    "img { position: absolute; top: 0; left: 0; width: 100%; height: 100%; object-fit: contain; }",
    ".title { text-align: center; font-size: 24px; font-weight: bold; margin: 20px 0; }",
    ".ssp-label { width: 60px; text-align: right; padding-right: 10px; }",
    ".legend { margin-top: 20px; text-align: center; }",
    ".legend-item { display: inline-block; margin: 0 10px; }",
    ".legend-color { display: inline-block; width: 20px; height: 20px; margin-right: 5px; vertical-align: middle; }",
    "</style>",
    "</head>",
    "<body>",
    paste0("<div class='title'>ESM Agreement for ", toupper(substr(pattern, 1, 1)), 
           substr(pattern, 2, nchar(pattern)), " climate analogues</div>"),
    "<table>",
    "<tr><th></th>"
  )
  
  # Add decade headers
  for (decade in decades) {
    html_content <- c(html_content, paste0("<th>", decade, "</th>"))
  }
  html_content <- c(html_content, "</tr>")
  
  # Add rows with SSP labels and images
  for (ssp in ssps) {
    html_content <- c(html_content, "<tr>")
    html_content <- c(html_content, paste0("<th class='ssp-label'>", ssp, "</th>"))
    
    for (decade in decades) {
      # Path to the image
      img_path <- paste0("individual_maps_", pattern, "/", 
                        pattern, "_", ssp, "_", decade, ".png")
      img_full_path <- file.path(output_folder, img_path)
      
      # Check if the image exists
      if (file.exists(img_full_path)) {
        html_content <- c(html_content, paste0("<td><img src='", img_path, 
                                            "' alt='", ssp, " - ", decade, "'></td>"))
      } else {
        # Empty cell if image doesn't exist
        html_content <- c(html_content, "<td style='background-color: #f9f9f9;'></td>")
      }
    }
    
    html_content <- c(html_content, "</tr>")
  }
  
  # Add legend with updated descriptions
  html_content <- c(
    html_content,
    "</table>",
    "<div class='legend'>",
     "<div class='legend-item'><div class='legend-color' style='background-color: #fcd225;'></div>No analogue (&lt;25%)</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #c03a83;'></div>Low confidence (≥25% to &lt;50%)</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #8606a6;'></div>Medium confidence(≥50% to &lt;75%)</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #0d0887;'></div>High confidence (≥75%)</div>",
    "</div>",
    "</body>",
    "</html>"
  )
  
  # Write the HTML file
  writeLines(html_content, html_file)
  
  cat("HTML composite view saved to:", html_file, "\n")
  
  # Convert HTML to PNG
  png_file <- file.path(output_folder, paste0("ESM_Agreement_composite_", pattern, ".png"))
  
  # Try to convert HTML to PNG using webshot2
  tryCatch({
    webshot2::webshot(
      url = html_file,
      file = png_file,
      delay = 2,  # Wait 2 seconds for everything to render
      zoom = 2    # Higher resolution
    )
    cat("Composite map saved as PNG:", png_file, "\n")
  }, error = function(e) {
    cat("Error converting HTML to PNG:", e$message, "\n")
    cat("Please open the HTML file in a browser and save as PNG manually:\n", html_file, "\n")
  })
}

cat("\nAll ESM Agreement composite maps processed!\n")
```


#modern composites #FOR PUBLICATION
# Note: This script will attempt to use magick for image cropping
# Install if needed: install.packages("magick")
```{r}
#Composite maps with Viridis - Updated with Modern Header Styling
# Create composite map for ESM Agreement plots with modern header styling
#--------------------------------------------------------------------------
library(png)
library(grid)
library(webshot2)
library(here)

# Define input and output directories
plots_folder <- here("Figures/ESM_Agreement_Plots_viridis")
output_folder <- here("Figures/ESM_Agreement_Plots_viridis")

# Create output directory if it doesn't exist
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)
}

# List all PNG files in the plots folder
plot_files <- list.files(plots_folder, pattern = ".*_ESM_Agreement_Plot_viridis\\.png$", full.names = TRUE)

if (length(plot_files) == 0) {
  stop("No ESM Agreement plot files found in ", plots_folder)
}

# Function to format SSP labels properly
format_ssp_label <- function(ssp_raw) {
  # Convert from formats like "ssp119" to "SSP1-1.9"
  ssp_upper <- toupper(ssp_raw)
  
  # Handle different SSP formats
  if (grepl("SSP119", ssp_upper)) return("SSP1-1.9")
  if (grepl("SSP126", ssp_upper)) return("SSP1-2.6")
  if (grepl("SSP245", ssp_upper)) return("SSP2-4.5")
  if (grepl("SSP370", ssp_upper)) return("SSP3-7.0")
  if (grepl("SSP585", ssp_upper)) return("SSP5-8.5")
  
  # Fallback: return as uppercase if no match
  return(ssp_upper)
}

# Function to format decade labels properly
format_decade_label <- function(decade_raw) {
  # Convert from formats like "2021_2030" to "2021-2030"
  parts <- strsplit(decade_raw, "_")[[1]]
  
  if (length(parts) == 2) {
    start_year <- parts[1]
    end_year <- parts[2]
    return(paste0(start_year, "-", end_year))
  }
  
  # Fallback: return original if can't parse
  return(decade_raw)
}

# Extract metadata from filenames
extract_metadata <- function(filename) {
  basename <- basename(filename)
  parts <- strsplit(basename, "_")[[1]]
  
  # Extract SSP, decade, and pattern
  # Format: ssp119_2021_2030_analogue_optimal_ESM_Agreement_Plot_viridis.png
  ssp_raw <- parts[1]
  decade_start <- parts[2]
  decade_end <- parts[3]
  decade_range <- paste(decade_start, decade_end, sep="_")
  pattern <- parts[5]  # "optimal" or "suitable"
  
  return(list(
    ssp = ssp_raw,
    ssp_formatted = format_ssp_label(ssp_raw),
    decade = decade_range,
    decade_formatted = format_decade_label(decade_range),
    pattern = pattern,
    path = filename
  ))
}

# Get metadata for all files
all_metadata <- lapply(plot_files, extract_metadata)

# Get unique patterns, SSPs, and decades (using raw values for processing)
patterns <- unique(sapply(all_metadata, function(x) x$pattern))
ssps <- unique(sapply(all_metadata, function(x) x$ssp))
decades <- unique(sapply(all_metadata, function(x) x$decade))

# Sort them
ssps <- sort(ssps)
decades <- sort(decades)

# Get formatted versions for display (fix the mapping issue)
ssps_formatted <- sapply(ssps, function(x) format_ssp_label(x))
decades_formatted <- sapply(decades, function(x) format_decade_label(x))

# Create proper mapping for sorted display
ssp_mapping <- setNames(ssps_formatted, ssps)
decade_mapping <- setNames(decades_formatted, decades)

# Process each pattern separately
for (pattern in patterns) {
  cat("Creating composite map for pattern:", pattern, "\n")
  
  # Filter files for this pattern
  pattern_metadata <- all_metadata[sapply(all_metadata, function(x) x$pattern == pattern)]
  
  # Create individual maps directory for this pattern (with v3 suffix for new styling)
  individual_maps_dir <- file.path(output_folder, paste0("individual_maps_", pattern, "_v3"))
  if (!dir.exists(individual_maps_dir)) {
    dir.create(individual_maps_dir, recursive = TRUE)
  }
  
  # Process each file to create standardized individual maps
  for (metadata in pattern_metadata) {
    # Extract information
    ssp <- metadata$ssp
    decade <- metadata$decade
    orig_path <- metadata$path
    
    # Define output path for the standardized image
    output_path <- file.path(individual_maps_dir, 
                            paste0(pattern, "_", ssp, "_", decade, ".png"))
    
    # Read, crop (to remove borders and keep only map), and save the image
    tryCatch({
      library(magick)
      img <- image_read(orig_path)
      
      # Get image dimensions
      info <- image_info(img)
      width <- info$width
      height <- info$height
      
      # Crop to remove borders from all sides - CUSTOM cropping
      # Remove borders: left 15%, right 15%, top 5% (perfect), bottom 5%
      crop_left <- floor(width * 0.15)     # Start 15% from left
      crop_top <- floor(height * 0.05)     # Start 5% from top (perfect)
      crop_width <- floor(width * 0.70)    # Keep 70% of width (15% + 70% = 85%, removing 15% from right)
      crop_height <- floor(height * 0.90)  # Keep 90% of height (5% + 90% = 95%, removing 5% from bottom)
      
      # Crop: geometry format is "WIDTHxHEIGHT+X_OFFSET+Y_OFFSET"
      crop_geometry <- paste0(crop_width, "x", crop_height, "+", crop_left, "+", crop_top)
      cropped_img <- image_crop(img, crop_geometry)
      
      # Save cropped image
      image_write(cropped_img, output_path)
      
    }, error = function(e) {
      # If magick fails, just copy the original file
      cat("Warning: Could not crop image", orig_path, ". Using original.\n")
      cat("Error:", e$message, "\n")
      file.copy(orig_path, output_path, overwrite = TRUE)
    })
  }
  
  # Create HTML for composite view with MODERN STYLING (matching constrained approach)
  html_file <- file.path(output_folder, paste0("ESM_Agreement_composite_", pattern, "_v3.html"))
  
  html_content <- c(
    "<!DOCTYPE html>",
    "<html>",
    "<head>",
    paste0("<title>", pattern, " Climate Analogues</title>"),
    "<style>",
    "* { margin: 0; padding: 0; box-sizing: border-box; }",
    "body { font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif; background: #f8f9fa; padding: 15px; }",
    ".container { max-width: 1400px; margin: 0 auto; background: white; border-radius: 8px; overflow: hidden; box-shadow: 0 4px 12px rgba(0,0,0,0.1); }",
    ".header { background: linear-gradient(135deg, #667eea 0%, #764ba2 100%); color: white; padding: 20px; text-align: center; }",
    ".title { font-size: 28px; font-weight: 600; margin-bottom: 5px; }",
    ".subtitle { font-size: 14px; opacity: 0.9; }",
    ".grid-container { display: grid; padding: 0; gap: 2px; background: #e9ecef; border-spacing: 2px; }",
    paste0(".grid-container { grid-template-columns: 80px repeat(", length(decades), ", 1fr); }"),
    ".grid-header { background: #495057; color: white; font-weight: 600; font-size: 13px; display: flex; align-items: center; justify-content: center; padding: 12px 8px; }",
    ".grid-cell { background: white; position: relative; padding: 2px; border: 1px solid #eee; }",
    ".grid-cell::after { content: ''; display: block; padding-bottom: 75%; /* Maintain aspect ratio */ }",
    ".grid-cell img { position: absolute; top: 0; left: 0; width: 100%; height: 100%; object-fit: cover; }",
    ".row-header { background: #6c757d; color: white; font-weight: 600; font-size: 12px; writing-mode: horizontal-tb; display: flex; align-items: center; justify-content: center; padding: 8px; }",
    ".legend { padding: 20px; background: #f8f9fa; border-top: 1px solid #dee2e6; }",
    ".legend-title { font-weight: 600; margin-bottom: 10px; color: #495057; font-size: 14px; }",
    ".legend-items { display: flex; justify-content: center; flex-wrap: wrap; gap: 15px; }",
    ".legend-item { display: flex; align-items: center; font-size: 16px; }",
    ".legend-color { width: 18px; height: 18px; border-radius: 3px; margin-right: 6px; border: 1px solid rgba(0,0,0,0.1); }",
    "@media (max-width: 768px) { .grid-container { grid-template-columns: 60px repeat(", length(decades), ", 1fr); } .title { font-size: 20px; } }",
    "</style>",
    "</head>",
    "<body>",
    "<div class='container'>",
    "<div class='grid-container'>"
  )
  
  # Add headers row with formatted decade labels
  html_content <- c(html_content, "<div class='grid-header'></div>") # Empty corner
  for (decade in decades) {
    formatted_decade <- decade_mapping[decade]
    html_content <- c(html_content, paste0("<div class='grid-header'>", formatted_decade, "</div>"))
  }
  
  # Add data rows with formatted SSP labels
  for (ssp in ssps) {
    formatted_ssp <- ssp_mapping[ssp]
    html_content <- c(html_content, paste0("<div class='row-header'>", formatted_ssp, "</div>"))
    
    for (decade in decades) {
      # Path to the image (updated for v3 folder)
      img_path <- paste0("individual_maps_", pattern, "_v3/", 
                        pattern, "_", ssp, "_", decade, ".png")
      img_full_path <- file.path(output_folder, img_path)
      
      # Check if the image exists
      if (file.exists(img_full_path)) {
        formatted_decade <- decade_mapping[decade]
        html_content <- c(html_content, paste0("<div class='grid-cell'><img src='", img_path, 
                                            "' alt='", formatted_ssp, " - ", formatted_decade, "'></div>"))
      } else {
        # Empty cell if image doesn't exist
        html_content <- c(html_content, "<div class='grid-cell' style='background-color: #f9f9f9;'></div>")
      }
    }
  }
  
  # Close grid and add legend
  html_content <- c(
    html_content,
    "</div>",
    "<div class='legend'>",
    "<div class='legend-title'> Confidence level(Agreement among ESMs)</div>",
    "<div class='legend-items'>",
     "<div class='legend-item'><div class='legend-color' style='background-color: #fcd225;'></div>No analogue (&lt;25%)</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #c03a83;'></div>Low confidence (≥25% to &lt;50%)</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #8606a6;'></div>Medium confidence(≥50% to &lt;75%)</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #0d0887;'></div>High confidence (≥75%)</div>",
    "</div>",
    "</div>",
    "</div>",
    "</body>",
    "</html>"
  )
  
  # Write the HTML file
  writeLines(html_content, html_file)
  
  cat("HTML composite view saved to:", html_file, "\n")
  
  # Convert HTML to PNG (with v3 suffix)
  png_file <- file.path(output_folder, paste0("ESM_Agreement_composite_", pattern, "_v3.png"))
  
  # Try to convert HTML to PNG using webshot2
  tryCatch({
    webshot2::webshot(
      url = html_file,
      file = png_file,
      delay = 2,  # Wait 2 seconds for everything to render
      zoom = 2    # Higher resolution
    )
    cat("Composite map saved as PNG:", png_file, "\n")
  }, error = function(e) {
    cat("Error converting HTML to PNG:", e$message, "\n")
    cat("Please open the HTML file in a browser and save as PNG manually:\n", html_file, "\n")
  })
}

```

#next code to be used is 13_MSP_contraints_shipping_EF_Oct25 and then following the 13_MSP_FINAL_Code_function_Constraints_EF_Oct25 where we map the constraints to aquaculture.
