---
title: "Code_contraints_shipping"
date: 1st version "2024-10-23" this version"2025-10-27"
author: Marina Christofidis (marina.christofidis@griffithuni.edu.au)


---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load the possible packages being used 
```{r}
library(ncdf4)
library(raster)
library(sf)
library(here)
library(tidyverse)
library(tmap)
library(terra)
library(dplyr)
library(stars)


```

#create a bounding box for our region of interest->
#create a bounding box for Tasmania #latitude = c(-57, -36) #longitude = c(10, 162)
```{r}
xmin <- 140.0
ymin <- -57
xmax <- 162
ymax <- -36
```


#create a polygon from the bounding box as the region of interest match
```{r}
bbox_coords<- matrix(c(xmin, ymin,
                        xmax, ymin,
                        xmax, ymax,
                        xmin, ymax,
                        xmin, ymin), 
                      ncol = 2, byrow = TRUE)

# Create an sf polygon object
bbox_polygon <- st_polygon(list(bbox_coords))
bbox_sf_TAS <- st_sfc(bbox_polygon, crs = 4326)  # if we want WGS 84 coordinate system

```


```{r}
BBOX_Valid<- st_make_valid(bbox_sf_TAS)
```
```{r}
BBOX_TAS_3577<-st_transform(BBOX_Valid, 3577)
```


#shipping lanes upload
#shipping AMSA

```{r}
shipping<-st_read(here("raw_data/Vessel Traffic Data August 2024/cts_srr_08_2024_pt/cts_srr_08_2024_pt/cts_srr_08_2024_pt.shp"))
```
```{r}
qtm(shipping)
```


```{r}
# Crop shipping to bounding box
shipping_bbox <- st_crop(shipping, BBOX_Valid)

# Reproject coordinates
shipping_prj <- st_transform(shipping_bbox, crs = 3577)
```
#create the 1km buffer
```{r}
shipping_buffer <- st_buffer(shipping_prj, dist = 1000)

```
# Filter
```{r}
unique(shipping_buffer$TYPE)
shipping_filt <- shipping_buffer %>%
  filter(grepl("Tanker|Cargo", TYPE))
unique(shipping_filt$TYPE)
```

```{r}
# Create column of 1's
shipping_filt$value <- 1
```


```{r}
# Transform crs
shipping_final <- st_transform(shipping_filt, crs = 3577)
```

#make lines
#maintaining other columns with all values 
```{r}
shipping_priority <- shipping_final %>%
  group_by(CRAFT_ID) %>%
  filter(n() > 1) %>% #ensures that only groups with more than one point are kept, which is necessary to form a valid line string (if I didn't use this all the data set went bad)
  summarise(totalvalue= sum(value),
            do_union = TRUE,
            LON = list(LON),
            LAT = list(LAT)) %>%
  st_cast("MULTILINESTRING")
```

#plot
```{r}
tm_shape(shipping_priority)+
  tm_lines()
```
#shipping priority filtering by quantile

#separating by quantile
```{r}
top_quantile_threshold <- quantile(shipping_priority$totalvalue, 0.75)
```
```{r}
# Filter the SpatVector to keep only features in the highest (top 25%) quantile
highest_quantile_shipping_priority <- subset(shipping_priority, totalvalue >= top_quantile_threshold)
```

```{r}
qtm(highest_quantile_shipping_priority)
```

```{r}
library(terra)
library(sf)
library(here)

# Ensure bbox_ext is in EPSG:3577 (Australian Albers)
bbox_ext <- ext(xmin, xmax, ymin, ymax)  # Define your bounding box

# Create a raster with the correct CRS (EPSG:3577)
output_raster <- rast(bbox_ext, res = 0.02, crs = "EPSG:3577")

# Check if 'totalvalue' exists in the vector data
if (!"totalvalue" %in% names(highest_quantile_shipping_priority)) {
  stop("The field 'totalvalue' does not exist in the vector data.")
}

# Handle any NA values in 'totalvalue'
if (anyNA(highest_quantile_shipping_priority$totalvalue)) {
  warning("The 'totalvalue' field contains missing values.")
  highest_quantile_shipping_priority$totalvalue[is.na(highest_quantile_shipping_priority$totalvalue)] <- 0
}

# Rasterize the vector data
shipping_priority_r <- rasterize(
  highest_quantile_shipping_priority,
  output_raster,
  field = "totalvalue",
  fun = "sum"
)

# Ensure the CRS of the raster is EPSG:3577 (already handled by raster creation)
cat("Raster CRS:", crs(shipping_priority_r), "\n")

# Check if rasterization was successful
if (is.null(shipping_priority_r)) {
  stop("Rasterization failed. Check input data and parameters.")
}

# Ensure the 'output_data' directory exists
dir.create(here('output_data'), recursive = TRUE, showWarnings = FALSE)

# Write the raster to a file
writeRaster(
  shipping_priority_r, 
  filename = here('output_data/shipping_priority_r.tif'), 
  overwrite = TRUE
)

# Confirm the file was saved
if (file.exists(here('output_data/shipping_priority_tasmania_reproj.tif'))) {
  cat("Raster file successfully saved!\n")
} else {
  cat("Failed to save raster file.\n")
}

# Plot to verify
plot(shipping_priority_r)
```

#go to code 13_MSP_FINAL_Code_function_Constraints_EF_Oct25