---
title: "MSP1_Code_function_Constraints"
date: 1st version "2025-03-14" this version"2025-10-27"
author: Marina Christofidis (marina.christofidis@griffithuni.edu.au)
---

#In this code we create a function to map the constraints to aquaculture and the overlapp them creating a constraints mask that will be used later. we also crete a figure of the constraint maps with marine zones 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages needed
```{r}
library(raster)
library(sf)
library(here)
library(tidyverse)
library(tmap)
library(terra)
library(dplyr)
library(fasterize)
```
```{r}
#create a bounding box for our region of interest->
xmin <- 140.995
ymin <- -47.255
xmax <- 153.005
ymax <- -38.995
```


#create a polygon from the bounding box as the region of interest match
```{r}
bbox_coords<- matrix(c(xmin, ymin,
                        xmax, ymin,
                        xmax, ymax,
                        xmin, ymax,
                        xmin, ymin), 
                      ncol = 2, byrow = TRUE)

# Create an sf polygon object
bbox_polygon <- st_polygon(list(bbox_coords))
bbox_sf_TAS <- st_sfc(bbox_polygon, crs = 4326)  # if we want WGS 84 coordinate system

```


#check if BBox is valid and reproject it
```{r}
BBOX_Valid<- st_make_valid(bbox_sf_TAS)
#turn it into a valid polygon
BBOX_TAS_3577<-st_transform(BBOX_Valid, 3577)
```


#create the function
#model workflow to make binary rasters of constraints
```{r}
create_binary_constraint <- function(vector_data, 
                                   constraint_name,
                                   output_folder = "output_data/Constraints",  # Added this parameter
                                   unsuitable_value = 0,
                                   suitable_value = 1) {
  
  # Ensure vector_data is valid
  vector_data <- st_make_valid(vector_data)
  
  # Create template raster explicitly
  template_raster <- rast(
    ext(140.0, 162, -57, -36),
    resolution = 0.005,
    crs = "EPSG:4326"
  )
  
  # Project template to match vector data CRS
  template_3577 <- project(template_raster, "EPSG:3577")
  
  # Initialize raster with suitable values
  constraint <- init(template_3577, suitable_value)
  
  # Convert to SpatVector for terra
  vector_data_vect <- vect(vector_data)
  
  # Rasterize
  constraint <- terra::rasterize(
    vector_data_vect, 
    constraint,
    field = unsuitable_value,
    update = TRUE,
    touches = TRUE
  )
  
  # Create output directory if it doesn't exist
  dir.create(here(output_folder), recursive = TRUE, showWarnings = FALSE)
  
  # Save the constraint
  writeRaster(constraint,
             filename = here(output_folder, paste0(constraint_name, "_constraint.tif")),
             overwrite = TRUE)
  
  # Create verification plots
  par(mfrow=c(1,2))
  plot(constraint, 
       main = paste0(constraint_name, " Constraints\n(0 = Unsuitable, 1 = Suitable)"),
       col = c("red", "green"))
  
  plot(constraint, main = "Verification with Original Data")
  plot(vector_data_vect, add = TRUE, col = "blue")
  
  # Print summary statistics
  cat("\nSummary for", constraint_name, "constraint:\n")
  print(freq(constraint))
  
  return(constraint)
}
```

#Creating the other ocean uses layers one by one 

#Reefs 
#Upload the data, transform it to the projection we are using Australian Albers EPSG 3577 and take a look
```{r}
Seamap_Tas2009<-st_read(here("raw_data/SeamapAus_TAS_SeamapTas/SeamapAus_TAS_SeamapTasPolygon.shp"))

#plot(Seamap_Tas2009)

Seamap_Tas2009_reproj<-st_transform(Seamap_Tas2009, 3577)

plot(Seamap_Tas2009_reproj)
```
#Filter only the reefs- Our dataset has many other types f substrata and we need to filter only the reefs for it

```{r}
# Process the reef data and filter only the reefs
reefs <- Seamap_Tas2009_reproj %>%
  filter(SM_HAB_CLS %in% c("Reef", "High profile reef", 
                           "Medium profile reef", "Low profile reef", 
                           "Patchy reef")) %>%
  st_make_valid() %>%
  mutate(constraint = 1)  # Add a column for rasterization

```

#Create reef binary constraint layer
```{r}
reef_constraint <- create_binary_constraint(
  vector_data = reefs,
  constraint_name = "reef",
  output_folder = "output_data/Constraints_2024"  # folder name
)
```

#Constraints due to Conservation
#Constraint Federal Parks
#Upload and project the vectors
#CAPAD 2024-data with adaptations brought by the south-east-network-management-plan-2025.pdf 
```{r}
#federal marine parks
AMPAs<- st_read(here("raw_data/CAPAD_2024_Marine/Collaborative_Australian_Protected_Areas_Database_(CAPAD)_2024_-_Marine.shp"))

AMPAs_3577<-st_transform(AMPAs, 3577)

```
#Focus on Tasmania our Region of intererest
```{r}

# Check what zones exist in Tasmania region
AMPAs_TAS <- AMPAs_3577 %>%
  st_intersection(BBOX_TAS_3577) #  Tasmania boundary BBOX

# Look at unique zone types in Tasmania
unique_IUCN <- AMPAs_TAS %>%
  pull(IUCN) %>%
  unique()

print("Zone types in Tasmania:")
print(unique_IUCN)
```
```{r}
# Change IUCN values for specific row numbers to follow south-east-network-management-plan-2025.pdf 
AMPAs_TAS_25 <- AMPAs_TAS
```

```{r}
AMPAs_TAS_25 <- AMPAs_TAS_25 %>%
  mutate(IUCN = case_when(
    PA_PID %in% c("124_0002_M", "151_0001_M", "093_0001_M", "115_0003_M") ~ "II",
    TRUE ~ IUCN
  ))
```

# Save the modified dataframe as GPKG in the raw_data folder
```{r}
st_write(AMPAs_TAS_25, 
         here("raw_data", "AMPAs_TAS_25_modified.gpkg"), 
         delete_dsn = TRUE)  # This overwrites if file already exists

```
#FILTER TO
#Include all strict protection zones (IUCN IA)
#Include all National Park level zones (IUCN II)
#Include restrictive IUCN IV zones
#Exclude multiple use and general use zones (IUCN VI)
#Exclude unzoned areas

#IUCN IA, II zones typically don't allow aquaculture
#Some IUCN IV zones might restrict aquaculture
#IUCN VI zones (Multiple Use, General Use) typically allow aquaculture with proper permits (IA, B , II, III, IV) should be more strict
```{r}
AMPAs_filtered <- AMPAs_TAS_25 %>%
  filter(IUCN %in% c( "I", "Ia", "II", "III",
        "IV"
  )) %>%
  st_make_valid() %>%
  mutate(constraint = 1)
```


#Create the AMPAs exclusive binary layer
```{r}
AMPAs_constraint <- create_binary_constraint(
  vector_data = AMPAs_filtered,
  constraint_name = "AMPAs",
  output_folder = "output_data/Constraints_2024"
)
```


#Constraints of Tasmanian marine Parks 
#Upload and project the vectors
```{r}
Marine_Parks_TAS<- st_read(here("raw_data/LIST_MARINE_NATURE_RESERVES_STATEWIDE/list_marine_nature_reserves_statewide.shp"))

Marine_parks_TAS_reproj<-st_transform(Marine_Parks_TAS, 3577)
```

```{r}
#marine_parks_filtered <- marine_parks_tas_reproj %>%
 # filter(ZONE_TYPE %in% c("No Take Zone", "Restricted Take Zone")) %>%
 # st_make_valid() %>%
 #mutate(constraint = 1)
```

#Create the Marine parks constraints layer
```{r}
marine_parks_constraint <- create_binary_constraint(
  vector_data = Marine_parks_TAS_reproj,
  constraint_name = "marine_parks",
  output_folder = "output_data/Constraints_2024"
)
```

  
#Load and transform kelp data
```{r}
kelp_data <- st_read(here("raw_data/GIANT_KELP_AERIAL_SURVEY_2019_STATEWIDE/Giant_Kelp_Aerial_Survey_2019_statewide.shp"))
kelp_data_3577 <- st_transform(kelp_data, "EPSG:3577")

```
#Create kelp binary constraint layer
```{r}
kelp_constraint <- create_binary_constraint(
  vector_data = kelp_data_3577,
  constraint_name = "kelp",
  output_folder = "output_data/Constraints_2024"
)

```




#Shipping constraints

```{r}
# Load and prepare shipping data
shipping_priority_Tasmania <- rast(here("output_data/shipping_priority_Tasmania.tif"))
crs(shipping_priority_Tasmania) <- "EPSG:4326"
shipping_priority_3577 <- project(shipping_priority_Tasmania, "EPSG:3577")

# Create binary constraint using the same logic you had
rcl_matrix <- matrix(c(
  NA, NA, 1,    # NA values become 1 (suitable)
  0, 0, 1,      # No shipping (0) becomes 1 (suitable)
  0.0000001, max(values(shipping_priority_3577), na.rm = TRUE), 0  # Any shipping activity becomes 0 (unsuitable)
), ncol = 3, byrow = TRUE)

# Reclassify
shipping_constraint <- classify(shipping_priority_3577, rcl_matrix)

# Create verification plots (matching other constraints)
par(mfrow=c(1,2))
plot(shipping_constraint, 
     main = "Shipping Constraints\n(0 = Unsuitable, 1 = Suitable)",
     col = c("red", "green"))

plot(shipping_constraint, 
     main = "Shipping Constraints Verification")

# Print summary statistics
cat("\nSummary for shipping constraint:\n")
print(freq(shipping_constraint))

# Save with standardized naming
writeRaster(shipping_constraint,
            filename = here("output_data", "Constraints_2024", "shipping_constraint.tif"),
            overwrite = TRUE)
```


#Bathymetry constraints
```{r}
# Load and prepare bathymetry data
bathymetry2023 <- rast(here("raw_data/Australian Bathymetry and Topography 2023 250m/Australian_Bathymetry_and_Topography_2023_250m_MSL_cog.tif"))
e <- ext(140.995, 153.005, -47.255, -38.995)
bathymetry_tassie <- crop(bathymetry2023, e)
bathymetry_tassie_reproj <- project(bathymetry_tassie, "EPSG:3577")

# Create binary classification (your existing logic)
rcl_matrix_bathy <- matrix(c(
  -Inf, -10, 1,    # Deeper than 10m = suitable (1)
  -10, Inf, 0      # Shallower than 10m = unsuitable (0)
), ncol = 3, byrow = TRUE)

# Reclassify
bathy_constraint <- classify(bathymetry_tassie_reproj, rcl_matrix_bathy)

# Create verification plots (matching other constraints)
par(mfrow=c(1,2))
plot(bathy_constraint, 
     main = "Bathymetry Constraints\n(0 = Unsuitable, 1 = Suitable)",
     col = c("red", "green"))

plot(bathy_constraint, 
     main = "Bathymetry Constraints Verification")

# Print summary statistics
cat("\nSummary for bathymetry constraint:\n")
print(freq(bathy_constraint))

# Save with standardized naming
writeRaster(bathy_constraint,
            filename = here("output_data", "Constraints_2024", "bathymetry_constraint.tif"),
            overwrite = TRUE)
```
#territory_that is land_and constrains aquaculture
```{r}
Au_states <- st_read(here("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp"))
```


```{r}
# All relevant states terrestrial
states_shp <- Au_states %>%
  filter(STE_CODE21 %in% c("6", "2", "1", "4")) %>%  # Tasmania, Victoria, NSW, SA
  st_transform(3577) %>%
  mutate(state_name = case_when(
    STE_CODE21 == "6" ~ "Terrestrial Tasmania",
    STE_CODE21 == "2" ~ "Terrestrial Victoria",
    STE_CODE21 == "1" ~ "Terrestrial NSW",
    STE_CODE21 == "4" ~ "Terrestrial SA"
  ))
```
```{r}
land_constraint <- create_binary_constraint(
  vector_data = states_shp,
  constraint_name = "land",
  output_folder = "output_data/Constraints_2024")
```



```{r}
#tmap_mode("view")
tmap_mode("plot)
```

#saving the constraint results to use further

```{r}
tm_shape(shipping_constraint) +
  tm_raster(palette = c("blue", NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Shipping Constraint",
            breaks = c(0, 0.5, 1),
            legend.show = TRUE) +
tm_shape(kelp_constraint) +
  tm_raster(palette = c("green", NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Kelp Constraint",
            breaks = c(0, 0.5, 1),
            legend.show = TRUE) +  
tm_shape(reef_constraint) +
  tm_raster(palette = c("darkgreen", NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Reef Constraint",
            breaks = c(0, 0.5, 1),
            legend.show = TRUE) +  
tm_shape(bathy_constraint) +
  tm_raster(palette = c("lightgrey", NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Bathymetry Constraint",
            breaks = c(0, 0.5, 1),
            legend.show = TRUE) +  
tm_shape(marine_parks_constraint) +
  tm_raster(palette = c("darkgrey", NA),
            labels = c("Unsuitable", "Suitable"),
            title = "Marine Parks Constraint",
            breaks = c(0, 0.5, 1),
            legend.show = TRUE) +  
tm_shape(AMPAs_constraint) +
  tm_raster(palette = c("darkgrey", NA),
            labels = c("Unsuitable", "Suitable"),
            title = "Federal Marine Parks Constraint",
            breaks = c(0, 0.5, 1),
            legend.show = TRUE) +
tm_layout(legend.outside = TRUE,
          legend.outside.position = "right",
          legend.title.size = 0.8,
          legend.text.size = 0.6,
          main.title = "Aquaculture Constraints",
          main.title.position = "center")
```


```{r}
# First, let's create a template raster with the desired extent in the target projection
# Create the bounding box in WGS84 first
bbox_coords <- matrix(c(140.995, -47.255, 
                        153.005, -47.255, 
                        153.005, -38.995, 
                        140.995, -38.995, 
                        140.995, -47.255), ncol=2, byrow=TRUE)

# Create a polygon from the coordinates
bbox_poly <- vect(bbox_coords, type="polygon", crs="EPSG:4326")

# Project the polygon to Australian Albers
bbox_poly_albers <- project(bbox_poly, "EPSG:3577")

# Create the template raster based on the projected extent
template_3577 <- rast(ext(bbox_poly_albers), resolution=500, crs="EPSG:3577")

# Resample all constraints to match the template
kelp_aligned <- resample(kelp_constraint, template_3577)
reef_aligned <- resample(reef_constraint, template_3577)
bathy_aligned <- resample(bathy_constraint, template_3577)
marine_parks_aligned <- resample(marine_parks_constraint, template_3577)
AMPAs_aligned <- resample(AMPAs_constraint, template_3577)
shipping_aligned <- resample(shipping_constraint, template_3577)
land_aligned<- resample(land_constraint, template_3577)

# Calculate the total constraints layer
total_constraints <- kelp_aligned * reef_aligned * bathy_aligned * 
                    marine_parks_aligned * AMPAs_aligned * shipping_aligned * land_aligned

# Save the combined constraints
writeRaster(total_constraints,
            filename = here("output_data", "Constraints_2024", "total_constraints.tif"),
            overwrite = TRUE)

# Load viridis for better color palettes
library(viridis)

# Create a map showing all constraints with different colors for unsuitable areas
tm_shape(total_constraints) +
  tm_raster(palette = c("#440154", "#238A8D"), 
            labels = c("Unsuitable", "Suitable"),
            title = "Combined Constraints",
            breaks = c(0, 0.5, 1)) +
tm_shape(shipping_aligned) +
  tm_raster(palette = c(viridis(1, option="plasma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Shipping",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
  tm_shape(land_aligned) +
  tm_raster(palette = c(viridis(1, option="plasma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "land",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
tm_shape(kelp_aligned) +
  tm_raster(palette = c(viridis(1, option="magma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Kelp",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(reef_aligned) +
  tm_raster(palette = c(viridis(1, option="inferno"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Reef",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(bathy_aligned) +
  tm_raster(palette = c(viridis(1, option="cividis"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Bathymetry",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(marine_parks_aligned) +
  tm_raster(palette = c(viridis(1, option="mako"), NA),
            labels = c("Unsuitable", "Suitable"),
            title = "State Marine Parks",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(AMPAs_aligned) +
  tm_raster(palette = c(viridis(1, option="turbo"), NA),
            labels = c("Unsuitable", "Suitable"),
            title = "Federal Marine Parks",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
tm_shape(land_aligned) +
   tm_raster(palette = c(viridis(1, option="turbo"), NA),
            labels = c("Unsuitable", "Suitable"),
            title = "land area",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
tm_layout(legend.outside = TRUE,
          legend.outside.position = "right",
          legend.title.size = 0.8,
          legend.text.size = 0.6,
          main.title = "Aquaculture Constraints",
          main.title.position = "center")
```

```{r}
# Save the combined constraints raster (this line is already in your code)
writeRaster(total_constraints,
            filename = here("output_data", "Constraints_2024", "total_constraints.tif"),
            overwrite = TRUE)

# Create the visualization with viridis colors
constraint_map <- tm_shape(total_constraints) +
  tm_raster(palette = c("#440154", "#238A8D"), 
            labels = c("Unsuitable", "Suitable"),
            title = "Combined Constraints",
            breaks = c(0, 0.5, 1)) +
tm_shape(shipping_aligned) +
  tm_raster(palette = c(viridis(1, option="plasma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Shipping",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
  tm_shape(land_aligned) +
  tm_raster(palette = c(viridis(1, option="plasma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "land",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
tm_shape(kelp_aligned) +
  tm_raster(palette = c(viridis(1, option="magma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Kelp",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(reef_aligned) +
  tm_raster(palette = c(viridis(1, option="inferno"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Reef",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(bathy_aligned) +
  tm_raster(palette = c(viridis(1, option="cividis"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Bathymetry",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(marine_parks_aligned) +
  tm_raster(palette = c(viridis(1, option="mako"), NA),
            labels = c("Unsuitable", "Suitable"),
            title = "State Marine Parks",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(AMPAs_aligned) +
  tm_raster(palette = c(viridis(1, option="turbo"), NA),
            labels = c("Unsuitable", "Suitable"),
            title = "Federal Marine Parks",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
tm_shape(shipping_aligned) +
  tm_raster(palette = c(viridis(1, option="plasma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Shipping",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
tm_layout(legend.outside = TRUE,
          legend.outside.position = "right",
          legend.title.size = 0.8,
          legend.text.size = 0.6,
          main.title = "Aquaculture Constraints",
          main.title.position = "center")

# Save the map
# Create directory if it doesn't exist
dir.create(here("output_data", "Constraints_2024"), showWarnings = FALSE, recursive = TRUE)

# As PNG
tmap_save(constraint_map,
          filename = here("output_data", "Constraints_2024", "combined_constraints_map_viridis.png"),
          width = 10,  # Increased width to accommodate the legend
          height = 10,
          dpi = 300)

# As PDF (optional, for higher quality)
tmap_save(constraint_map,
          filename = here("output_data", "Constraints_2024", "combined_constraints_map_viridis.pdf"),
          width = 10,  # Increased width to accommodate the legend
          height = 10)

# Display the map in R
constraint_map
```

#constraint map with marine zones

#upload zones
```{r}
# Read marine zone shapefiles
#contains terrestrial areas-beware we have to exclude them
# 1.  Create bbox in Albers
bbox_albers <- st_bbox(c(xmin = 140.995, xmax = 153.005, ymin = -47.255, ymax = -38.995)) %>%
  st_as_sfc() %>%
  st_as_sf() %>%
  st_set_crs(4326) %>%
  st_transform(3577)

#2. Load and process all required data
maritime_boundaries_AU<- st_read(here("raw_data/AU_GA_SSLA-1973-AMB2014a_Maritime_boundaries_Australia/AU_GA_SSLA_1973_AMB2014a_ts_1990_poly.shp"))%>%
 st_transform("EPSG:3577")%>%
 st_make_valid()

coastal_waters <- st_read(here("raw_data/Coastal_Waters_areas_(AMB2020)/Coastal_Waters_areas_(AMB2020).shp"))%>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

commonwealth_waters <- st_read(here("raw_data/Commonwealth_Marine_Regions/Commonwealth_Marine_Regions.shp")) %>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

terrestrial_areas <- st_read(here("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp")) %>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

# 3. Crop all layers to bbox
terrestrial_areas_crop <- st_intersection(terrestrial_areas, bbox_albers)
coastal_waters_crop <- st_intersection(coastal_waters, bbox_albers)
commonwealth_crop <- st_intersection(commonwealth_waters, bbox_albers)
maritime_boundaries_crop<-st_intersection(maritime_boundaries_AU,bbox_albers)

state_waters<-st_union(coastal_waters_crop, maritime_boundaries_crop)
state_waters_final <- st_difference(state_waters, st_union(terrestrial_areas_crop))

# 4. Create High Seas
all_managed_waters_and_land <- bind_rows(
  st_set_geometry(commonwealth_crop, "geometry") %>% mutate(zone_type = "Commonwealth"),
  st_set_geometry(state_waters_final, "geometry") %>% mutate(zone_type = "State"),
  st_set_geometry(terrestrial_areas_crop, "geometry") %>% mutate(zone_type = "terrestrial_areas")
)

high_seas <- st_difference(bbox_albers, st_union(all_managed_waters_and_land))
```


#build the map with zones
```{r}
# Create the visualization with viridis colors
constraint_map_with_zones <- tm_shape(total_constraints) +
  tm_raster(palette = c("#440154", "#238A8D"), 
            labels = c("Unsuitable", "Suitable"),
            title = "Combined Constraints",
            breaks = c(0, 0.5, 1)) +
tm_shape(shipping_aligned) +
  tm_raster(palette = c(viridis(1, option="plasma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Shipping",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
  tm_shape(land_aligned) +
  tm_raster(palette = c(viridis(1, option="plasma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "land",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
tm_shape(kelp_aligned) +
  tm_raster(palette = c(viridis(1, option="magma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Kelp",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(reef_aligned) +
  tm_raster(palette = c(viridis(1, option="inferno"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Reef",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(bathy_aligned) +
  tm_raster(palette = c(viridis(1, option="cividis"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Bathymetry",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(marine_parks_aligned) +
  tm_raster(palette = c(viridis(1, option="mako"), NA),
            labels = c("Unsuitable", "Suitable"),
            title = "State Marine Parks",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +  
tm_shape(AMPAs_aligned) +
  tm_raster(palette = c(viridis(1, option="turbo"), NA),
            labels = c("Unsuitable", "Suitable"),
            title = "Federal Marine Parks",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
tm_shape(shipping_aligned) +
  tm_raster(palette = c(viridis(1, option="plasma"), NA), 
            labels = c("Unsuitable", "Suitable"),
            title = "Shipping",
            breaks = c(0, 0.5, 1),
            alpha = 0.7) +
  tm_shape(state_waters_final) +
  tm_polygons(palette = c(viridis(1, option="plasma"), NA), 
            title = "State waters",
            alpha = 0.2) +
 tm_shape(commonwealth_crop) +
  tm_polygons(palette = c(viridis(1, option="plasma"), NA), 
            title = "Commonwealth waters",
            alpha = 0.2) +
  tm_shape(high_seas) +
  tm_polygons(palette = c(viridis(1, option="plasma"), NA), 
            title = "High Seas",
            alpha = 0.2) +
tm_layout(legend.outside = TRUE,
          legend.outside.position = "right",
          legend.title.size = 0.8,
          legend.text.size = 0.6,
          main.title = "Aquaculture Constraints",
          main.title.position = "center")

# Save the map
# Create directory if it doesn't exist
dir.create(here("output_data", "Constraints_2024"), showWarnings = FALSE, recursive = TRUE)

# As PNG
tmap_save(constraint_map_with_zones,
          filename = here("output_data", "Constraints_2024", "combined_constraint_map_with_zones_viridis.png"),
          width = 10,  # Increased width to accommodate the legend
          height = 10,
          dpi = 300)

# As PDF (optional, for higher quality)
tmap_save(constraint_map,
          filename = here("output_data", "Constraints_2024", "combined_constraint_map_with_zones_viridis.pdf"),
          width = 10,  # Increased width to accommodate the legend
          height = 10)

# Display the map in R
constraint_map_with_zones
```

#after we have mapped the constraints to aquaculture go to code 14_km2_suitability_over_time_results_EF_Oct25

