---
title: "14_km2_suitability_over_time_results_EF_Oct25"
date: 1st version "2025-02-14"" this version"2025-10-27"
author: Marina Christofidis (marina.christofidis@griffithuni.edu.au)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#load packages that can be used
```{r}
library(terra)
library(tidyverse)
library(rasterVis)
library(here)
library(dplyr)
library(readr)
library(tmap)
library(leaflet)
library(sf)
library(ggplot2)
library(viridisLite)
library(ggplot2)
library(viridis)
library(tidyr)
library(readr)
library(packcircles)
```


#Loop through Raster Files of combined Pattern and Analogue to generate a Raster with the Area of the different categories of analogues with distance from the coast, by puting areas within maritime territories 

```{r}
# Load required libraries
library(terra)
library(tidyverse)
library(here)
library(dplyr)
library(readr)
library(sf)
library(ggplot2)
library(viridis)
library(tidyr)
library(knitr)
library(kableExtra)
library(patchwork)
```

```{r}
# STEP 1: CREATE CORRECTED DATA EXCLUDING TERRESTRIAL AREA
# Read marine zone shapefiles
# 1.  Create bbox in Albers

bbox_albers <- st_bbox(c(xmin = 140.995, xmax = 153.005, ymin = -47.255, ymax = -38.995)) %>%
  st_as_sfc() %>%
  st_as_sf() %>%
  st_set_crs(4326) %>%
  st_transform(3577)

#2. Load and process all required data


maritime_boundaries_AU<- st_read(here("raw_data/AU_GA_SSLA-1973-AMB2014a_Maritime_boundaries_Australia/AU_GA_SSLA_1973_AMB2014a_ts_1990_poly.shp"))%>%
 st_transform("EPSG:3577")%>%
 st_make_valid()

coastal_waters <- st_read(here("raw_data/Coastal_Waters_areas_(AMB2020)/Coastal_Waters_areas_(AMB2020).shp"))%>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

commonwealth_waters <- st_read(here("raw_data/Commonwealth_Marine_Regions/Commonwealth_Marine_Regions.shp")) %>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

terrestrial_areas <- st_read(here("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp")) %>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

# 3. Crop all layers to bbox

terrestrial_areas_crop <- st_intersection(terrestrial_areas, bbox_albers)
coastal_waters_crop <- st_intersection(coastal_waters, bbox_albers)
commonwealth_crop <- st_intersection(commonwealth_waters, bbox_albers)
maritime_boundaries_crop<-st_intersection(maritime_boundaries_AU,bbox_albers)


state_waters<-st_difference(coastal_waters_crop, st_union(terrestrial_areas_crop))


# 4. Create High Seas
all_managed_waters_and_land <- bind_rows(
  st_set_geometry(commonwealth_crop, "geometry") %>% mutate(zone_type = "Commonwealth"),
  st_set_geometry(state_waters, "geometry") %>% mutate(zone_type = "State"),
  st_set_geometry(terrestrial_areas_crop, "geometry") %>% mutate(zone_type = "terrestrial_areas")
)

high_seas <- st_difference(bbox_albers, st_union(all_managed_waters_and_land))
```

```{r}
marine_zones <- list(
  "State Waters" = state_waters,
  "Commonwealth Waters" = commonwealth_crop,
  "High Seas" = high_seas
)

# Initialize the results dataframe
area_results_marine_corrected <- data.frame(
  SSP = character(),
  Decade = character(),
  Pattern = character(),
  Marine_Zone = character(),
  No_Analog_km2 = numeric(),
  Low_Confidence_km2 = numeric(),
  Medium_Confidence_km2 = numeric(),
  High_Confidence_km2 = numeric(),
  stringsAsFactors = FALSE
)

# Define patterns
patterns <- c("suitable", "optimal")

# Path to folder with rasters
ESM_Agreement_results_folder <- here("output_data/Combined_Results/ESM_agreement")
raster_files <- list.files(ESM_Agreement_results_folder, pattern = "\\.tif$", full.names = TRUE)

# Process each pattern and file
for (pattern in patterns) {
  for (file in raster_files) {
    if (grepl(pattern, basename(file))) {
      cat("Processing:", basename(file), "\n")
      
      # Read and project raster
      r <- rast(file)
      if (crs(r) != "EPSG:3577") {
        r <- project(r, "EPSG:3577")
      }
      
      # Extract filename components
      file_name <- basename(file)
      parts <- unlist(strsplit(file_name, "_"))
      ssp <- parts[1]
      decade_range <- paste(parts[2], parts[3], sep = "_")
      
      # Calculate areas for each marine zone using the pre-defined polygons
      for (zone_name in names(marine_zones)) {
        zone_vect <- vect(marine_zones[[zone_name]])
        zone_mask <- mask(r, zone_vect)
        area_raster <- cellSize(zone_mask, unit = "m")
        
        no_analog_area <- as.numeric(global(area_raster * (zone_mask == 0), 
                                          sum, na.rm = TRUE)[, 1]) / 1e6
        low_conf_area <- as.numeric(global(area_raster * (zone_mask == 1), 
                                         sum, na.rm = TRUE)[, 1]) / 1e6
        medium_conf_area <- as.numeric(global(area_raster * (zone_mask == 2), 
                                            sum, na.rm = TRUE)[, 1]) / 1e6
        high_conf_area <- as.numeric(global(area_raster * (zone_mask == 3), 
                                          sum, na.rm = TRUE)[, 1]) / 1e6
        
        # Replace NAs with 0
        no_analog_area <- ifelse(is.na(no_analog_area), 0, no_analog_area)
        low_conf_area <- ifelse(is.na(low_conf_area), 0, low_conf_area)
        medium_conf_area <- ifelse(is.na(medium_conf_area), 0, medium_conf_area)
        high_conf_area <- ifelse(is.na(high_conf_area), 0, high_conf_area)
        
        # Add results to dataframe
        area_results_marine_corrected <- area_results_marine_corrected %>%
          add_row(
            SSP = ssp,
            Decade = decade_range,
            Pattern = pattern,
            Marine_Zone = zone_name,
            No_Analog_km2 = no_analog_area,
            Low_Confidence_km2 = low_conf_area,
            Medium_Confidence_km2 = medium_conf_area,
            High_Confidence_km2 = high_conf_area
          )
        
        cat("Processed", zone_name, "for", ssp, decade_range, pattern, "\n")
      }
    }
  }
}

# Create output directories
dir.create(here("output_data", "ESM_Agreement_Plots_Area_CORRECTED"), recursive = TRUE, showWarnings = FALSE)
dir.create(here("Figures", "Marine_territory_plots_CORRECTED"), recursive = TRUE, showWarnings = FALSE)

# Save corrected results
write.csv(area_results_marine_corrected, 
          here("output_data", "ESM_Agreement_Plots_Area_CORRECTED", "area_results_marine_zones_CORRECTED.csv"), 
          row.names = FALSE)

# STEP 2: DATA CLEANING AND PREPARATION FOR VISUALIZATION
# Clean and prepare data for visualization
area_results_high_corrected <- area_results_marine_corrected %>%
  select(SSP, Decade, Pattern, Marine_Zone, High_Confidence_km2) %>%
  rename(Area_km2 = High_Confidence_km2) %>%
  # Clean up SSP names
  mutate(
    SSP_clean = case_when(
      SSP == "ssp119" ~ "SSP1-1.9",
      SSP == "ssp126" ~ "SSP1-2.6", 
      SSP == "ssp245" ~ "SSP2-4.5",
      SSP == "ssp370" ~ "SSP3-7.0",
      SSP == "ssp585" ~ "SSP5-8.5",
      TRUE ~ SSP
    ),
    # Ensure Marine_Zone is clean
    Marine_Zone_Clean = as.character(Marine_Zone),
    # Set factor order for consistent plotting
    Marine_Zone_Clean = factor(Marine_Zone_Clean, levels = c("State Waters", "Commonwealth Waters", "High Seas"))
  ) %>%
  # Remove any rows with missing data
  filter(!is.na(Pattern), !is.na(Marine_Zone_Clean), !is.na(Area_km2)) %>%
  # Ensure we only have the expected patterns
  filter(Pattern %in% c("suitable", "optimal"))

# Debug: Check the cleaned data
cat("Data cleaning results:\n")
cat("Unique Marine Zones:", paste(unique(area_results_high_corrected$Marine_Zone_Clean), collapse = ", "), "\n")
cat("Unique Patterns:", paste(unique(area_results_high_corrected$Pattern), collapse = ", "), "\n")
cat("Unique SSPs:", paste(unique(area_results_high_corrected$SSP_clean), collapse = ", "), "\n")
cat("Total rows:", nrow(area_results_high_corrected), "\n")

# Current aquaculture usage
current_area <- 25.88

# STEP 3: CREATE VISUALIZATION FUNCTIONS
# Function to create plots for each marine territory (high confidence only)
create_territory_plots_high_conf_corrected <- function(data, territory) {
  # Filter data for specific marine territory
  territory_data <- data %>%
    filter(Marine_Zone_Clean == territory) %>%
    filter(!is.na(Pattern), !is.na(SSP_clean), !is.na(Area_km2))
  
  # Check if we have data for this territory
  if(nrow(territory_data) == 0) {
    cat("Warning: No data found for territory:", territory, "\n")
    return(NULL)
  }
  
  # Check patterns available
  available_patterns <- unique(territory_data$Pattern)
  cat("Territory:", territory, "has patterns:", paste(available_patterns, collapse = ", "), "\n")
  cat("Number of data points:", nrow(territory_data), "\n")
  
  # 1. Line plot showing trends for all SSPs
  p1 <- ggplot(territory_data, 
               aes(x = Decade, y = Area_km2, color = SSP_clean, group = SSP_clean)) +
    geom_line(size = 1) +
    geom_point(size = 3) +
    facet_wrap(~Pattern, scales = "free_y", drop = FALSE) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom") +
    scale_color_manual(values = c("SSP1-1.9" = "#440154FF",   # Purple
                                 "SSP1-2.6" = "#31688EFF",    # Blue 
                                 "SSP2-4.5" = "#35B779FF",    # Teal/Green
                                 "SSP3-7.0" = "#90D743FF",    # Light Green
                                 "SSP5-8.5" = "#FDE725FF"),   # Yellow
                       na.value = "grey50") + 
    labs(title = paste(territory, "- High Confidence Area Changes Over Time (CORRECTED)"),
         subtitle = "High Seas now properly excludes terrestrial areas",
         x = "Decade", 
         y = "Area (km²)",
         color = "SSP Scenario")
  
  # 2. Bar plot showing changes over decades with current usage reference
  p2 <- ggplot(territory_data, 
               aes(x = Decade, y = Area_km2, fill = SSP_clean)) +
    geom_bar(stat = "identity", position = "dodge") +
    geom_hline(yintercept = current_area, 
               linetype = "dashed", 
               color = "magenta",
               size = 1) +
    facet_wrap(~Pattern, scales = "free_y", drop = FALSE) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom") +
    scale_fill_manual(values = c("SSP1-1.9" = "#440154FF",   
                                "SSP1-2.6" = "#31688EFF",    
                                "SSP2-4.5" = "#35B779FF",    
                                "SSP3-7.0" = "#90D743FF",    
                                "SSP5-8.5" = "#FDE725FF"),
                      na.value = "grey50") +
    labs(title = paste(territory, "- High Confidence Areas vs Current Usage (CORRECTED)"),
         subtitle = paste("magenta line shows current usage:", current_area, "km²"),
         x = "Decade", 
         y = "Area (km²)",
         fill = "SSP Scenario")
  
  # Save individual plots
  tryCatch({
    ggsave(here("Figures", "Marine_territory_plots_CORRECTED", 
                paste0(make.names(territory), "_high_conf_trends_CORRECTED.png")), 
           p1, width = 12, height = 8)
    
    ggsave(here("Figures", "Marine_territory_plots_CORRECTED", 
                paste0(make.names(territory), "_high_conf_bars_CORRECTED.png")), 
           p2, width = 12, height = 8)
    
    # Create and save combined plot
    combined <- (p1 / p2) +
      plot_annotation(title = paste("High Confidence Areas Analysis (CORRECTED):", territory),
                     theme = theme_minimal())
    
    ggsave(here("Figures", "Marine_territory_plots_CORRECTED", 
                paste0(make.names(territory), "_high_conf_combined_CORRECTED.png")), 
           combined, width = 15, height = 12)
    
    cat("Successfully saved plots for", territory, "\n")
    
  }, error = function(e) {
    cat("Error saving plots for", territory, ":", e$message, "\n")
  })
  
  return(list(trends = p1, bars = p2))
}

# STEP 4: GENERATE PLOTS FOR ALL TERRITORIES
# Get territories (ensure they're character, not factor levels)
territories <- unique(as.character(area_results_high_corrected$Marine_Zone_Clean))
territories <- territories[!is.na(territories)]

cat("Creating plots for territories:", paste(territories, collapse = ", "), "\n")

# Create plots for each marine territory
all_plots_corrected <- list()
for(territory in territories) {
  cat("\n--- Processing territory:", territory, "---\n")
  plots <- create_territory_plots_high_conf_corrected(area_results_high_corrected, territory)
  if(!is.null(plots)) {
    all_plots_corrected[[territory]] <- plots
  }
}

# STEP 5: CREATE COMBINED COMPARISON PLOTS
# Function to create individual bar plots for combination
create_bar_plot_corrected <- function(data, territory) {
  territory_data <- data %>% 
    filter(Marine_Zone_Clean == territory) %>%
    filter(!is.na(Pattern), !is.na(SSP_clean), !is.na(Area_km2))
  
  if(nrow(territory_data) == 0) {
    return(NULL)
  }
  
  ggplot(territory_data, 
         aes(x = Decade, y = Area_km2, fill = SSP_clean)) +
    geom_bar(stat = "identity", position = "dodge") +
    geom_hline(yintercept = current_area, 
               linetype = "dashed", 
               color = "magenta",
               size = 0.8) +
    facet_wrap(~Pattern, scales = "free_y", drop = FALSE) +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom",
          plot.title = element_text(size = 10)) +
    scale_fill_manual(values = c("SSP1-1.9" = "#440154FF",   
                                "SSP1-2.6" = "#31688EFF",    
                                "SSP2-4.5" = "#35B779FF",    
                                "SSP3-7.0" = "#90D743FF",    
                                "SSP5-8.5" = "#FDE725FF"),
                      na.value = "grey50") +
    labs(title = territory,
         x = "Decade", 
         y = "Area (km²)",
         fill = "SSP Scenario")
}

# Create individual plots for combination
plot_list_corrected <- list()
for(territory in territories) {
  plot <- create_bar_plot_corrected(area_results_high_corrected, territory)
  if(!is.null(plot)) {
    plot_list_corrected[[territory]] <- plot
  }
}

# Create combined plot if we have plots to combine
if(length(plot_list_corrected) > 0) {
  tryCatch({
    # Combine plots - vertical arrangement
    if(length(plot_list_corrected) >= 3) {
      final_plot_vertical <- plot_list_corrected[[1]] / plot_list_corrected[[2]] / plot_list_corrected[[3]] +
        plot_layout(guides = "collect") & 
        theme(legend.position = "bottom")
    } else if(length(plot_list_corrected) == 2) {
      final_plot_vertical <- plot_list_corrected[[1]] / plot_list_corrected[[2]] +
        plot_layout(guides = "collect") & 
        theme(legend.position = "bottom")
    } else {
      final_plot_vertical <- plot_list_corrected[[1]]
    }
    
    final_plot_vertical <- final_plot_vertical +
      plot_annotation(
        title = "Comparison of High Confidence Areas Across Marine Territories (CORRECTED)",
        subtitle = "High Seas now properly excludes terrestrial areas | magenta line = Current usage",
        theme = theme(plot.title = element_text(size = 14, hjust = 0.5))
      )
    
    ggsave(here("Figures", "Marine_territory_plots_CORRECTED", "combined_territories_bars_vertical_CORRECTED.png"), 
           final_plot_vertical, 
           width = 12, 
           height = 18)
    
    cat("Successfully created combined territory plot\n")
    
  }, error = function(e) {
    cat("Error creating combined plot:", e$message, "\n")
  })
}

# STEP 6: SUMMARY ANALYSES
# Summary table
summary_table_corrected <- area_results_high_corrected %>%
  group_by(Marine_Zone_Clean, Pattern, SSP_clean, Decade) %>%
  summarize(
    Area_km2 = sum(Area_km2, na.rm = TRUE),
    Percent_of_Current = (Area_km2 / current_area) * 100,
    .groups = "drop"
  )

# Threshold analysis - when areas drop below current usage
threshold_analysis_corrected <- area_results_high_corrected %>%
  group_by(Marine_Zone_Clean, Pattern, SSP_clean) %>%
  arrange(Decade) %>%
  mutate(
    Below_Current = Area_km2 < current_area,
    First_Below = if_else(Below_Current & !lag(Below_Current, default = FALSE), 
                         Decade, NA_character_)
  ) %>%
  summarize(
    First_Decade_Below = na.omit(First_Below)[1],
    Minimum_Area = min(Area_km2, na.rm = TRUE),
    Maximum_Area = max(Area_km2, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  mutate(
    Status = case_when(
      is.na(First_Decade_Below) & Minimum_Area >= current_area ~ "Always above current area",
      is.na(First_Decade_Below) & Minimum_Area < current_area ~ "Already below current area",
      TRUE ~ paste("Drops below current area in", First_Decade_Below)
    )
  )

# Save analyses
write.csv(summary_table_corrected, 
          here("Figures", "Marine_territory_plots_CORRECTED", "area_percentage_summary_CORRECTED.csv"), 
          row.names = FALSE)

write.csv(threshold_analysis_corrected, 
          here("Figures", "Marine_territory_plots_CORRECTED", "threshold_analysis_CORRECTED.csv"), 
          row.names = FALSE)

# Create percentage change over time plot
tryCatch({
  percentage_change_plot <- ggplot(summary_table_corrected, 
         aes(x = Decade, 
             y = Percent_of_Current, 
             color = SSP_clean,
             group = SSP_clean)) +
    geom_line(size = 1) +
    geom_point(size = 2) +
    facet_grid(Pattern ~ Marine_Zone_Clean, scales = "free_y") +
    theme_minimal() +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          legend.position = "bottom") +
    scale_color_manual(values = c("SSP1-1.9" = "#440154FF",   
                                 "SSP1-2.6" = "#31688EFF",    
                                 "SSP2-4.5" = "#35B779FF",    
                                 "SSP3-7.0" = "#90D743FF",    
                                 "SSP5-8.5" = "#FDE725FF"),
                       na.value = "grey50") +
    labs(title = "Percentage of Current Area Available Over Time",
         subtitle = paste("Current area:", current_area, "km² | High Seas calculations now exclude terrestrial areas"),
         x = "Decade",
         y = "Percentage of Current Area (%)",
         color = "SSP Scenario") +
    geom_hline(yintercept = 100, 
               linetype = "dashed", 
               color = "magenta", 
               linewidth = 0.5)
  
  ggsave(here("Figures", "Marine_territory_plots_CORRECTED", "percentage_change_over_time_CORRECTED.png"), 
         percentage_change_plot,
         width = 15, 
         height = 8)
  
  cat("Successfully created percentage change plot\n")
  
}, error = function(e) {
  cat("Error creating percentage change plot:", e$message, "\n")
})

# STEP 7: FINAL SUMMARY
cat("\n=== CORRECTED MARINE ZONE ANALYSIS COMPLETE ===\n")
cat("- Data:", here("output_data", "ESM_Agreement_Plots_Area_CORRECTED"), "\n")
cat("- Plots:", here("Figures", "Marine_territory_plots_CORRECTED"), "\n")

if(exists("threshold_analysis_corrected")) {
  cat("\nThreshold Analysis Summary:\n")
  print(threshold_analysis_corrected)
}

cat("\nProcessing completed successfully!\n")
```


```{r}
# Load your CSV data
area_results_sum <- read_csv(here("output_data/ESM_Agreement_Plots_Area_CORRECTED/area_results_marine_zones_CORRECTED.csv"), show_col_types = FALSE)
```

```{r}
# Create a dataframe for the current aquaculture value
current_aqua <- data.frame(
  Decade = "Current",
  High_Confidence_km2 = 25.88,
  SSP = "Current",
  Pattern = "suitable"
)
```

```{r}
# Combine with your main data
df_combined <- area_results_sum %>%
  select(SSP, Decade, Pattern, High_Confidence_km2) %>%
  rbind(current_aqua)
```

#GOOD plot of the amount of area available currently and along the decades to come in each SSP for each pattern

```{r}
current_aqua <- data.frame(
  Decade = "Current",
  High_Confidence_km2 = 25.88,
  SSP = "Current",
  Pattern = "suitable"
)
# Combine with your main data
df_combined <- area_results_sum %>%
  select(SSP, Decade, Pattern, High_Confidence_km2) %>%
  rbind(current_aqua)

# Define the order of decades you want
decade_order <- c("Current", "2021_2030", "2031_2040", "2041_2050", "2051_2060", 
                 "2061_2070", "2071_2080", "2081_2090", "2091_2100")

line_plot_area_available<- ggplot(df_combined, aes(x = Decade, y = High_Confidence_km2, 
                        color = SSP, 
                        linetype = Pattern)) +
  geom_line(aes(group = interaction(SSP, Pattern))) +
  geom_point() +
  scale_color_viridis(discrete = TRUE) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  scale_x_discrete(limits = decade_order) +
  theme_light() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  ) +
  labs(
    x = "Decade",
    y = "Area (km²)",
    color = "SSP Scenario",
    linetype = "Pattern"
  ) +
  scale_y_continuous(labels = scales::comma)

ggsave(here("Figures/Area_plot/Combined_area_line_plot.png"), 
       plot = line_plot_area_available, width = 10, height = 6)
```

```{r}
# First, arrange the data by SSP, Pattern, and Decade
area_results_sum <- area_results_sum %>%
  arrange(SSP, Pattern, Decade)

# Calculate percentage change for each decade relative to the first decade
area_results_sum <- area_results_sum %>%
  group_by(SSP, Pattern) %>%
  mutate(
    first_value = first(High_Confidence_km2),
    percentage_area_loss = ((High_Confidence_km2 - first_value) / first_value) * 100  # This is the modified line
  ) %>%
  ungroup()

# Now create the plot
line_plot_decadal_loss <- ggplot(area_results_sum, aes(x = Decade, y = percentage_area_loss, 
                            color = SSP, 
                            linetype = Pattern)) +
  geom_hline(yintercept = 0, linetype = "dotted", color = "gray50") +  # Reference line at 0% change
  geom_line(aes(group = interaction(SSP, Pattern))) +
  geom_point() +
  scale_color_viridis(discrete = TRUE) +
  scale_linetype_manual(values = c("dashed", "solid")) +
  theme_light() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank()
  ) +
  labs(
    x = "Decade",
    y = "Percentage Change in Area (%)",
    color = "SSP Scenario",
    linetype = "Pattern"
  ) +
  scale_y_continuous(labels = scales::comma)

ggsave(here("Figures/Area_plot/line_plot_decadal_loss.png"), 
       plot = line_plot_decadal_loss, width = 10, height = 6)
```


# Go to code 15_climate_MSP_combined_analysis_viridis_EF_Oct25 to overlap constraints with climate calculations

