---
title: "15-MSP_and_Climate_and_constraints_map_plotting"
output: html_document
date: first version"2025-01-16"/ this version 27 Oct 2025
author: Marina Christofidis (marina.christofidis@griffithuni.edu.au)
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#In this code we will map the constraints and the climate analogues and make the composite map of the maps created. 

#load packages that can me used
```{r}
library(terra)
library(tidyverse)
library(rasterVis)
library(here)
library(dplyr)
library(readr)
library(tmap)
library(leaflet)
library(sf)
library(ggplot2)
library(viridisLite)
library(ggplot2)
library(viridis)
library(tidyr)
library(readr)
library(knitr)
library(kableExtra)
library(raster)
library(cowplot)
library(patchwork)
library(png)
library(grid)
library(webshot2)
library(magick)

```
#upload the tasmanian shapefile and the total constraints raster made before
```{r}
tassie_shp <- st_read(here("raw_data/tassie_shp.gpkg"))
```

```{r}
total_constraints<- rast(here("output_data/Constraints_2024/total_constraints.tif"))
```


#This code:
#1. Loads your constraint raster
#2. Defines a function that:
#   - Processes each climate raster
#   - Combines it with constraints
#   - Creates visualizations
#  - Saves both data and maps
#3. Processes all files for both optimal and suitable patterns
#4. Creates organized output folders
#5. Includes error checking throughout
```{r}
# Create a NEW output folder for the combined climate and MSP analysis

combined_climate_MSP_output_folder_viridis_2025<- here("output_data", "Climate_MSP_Constraints_2025")
dir.create(combined_climate_MSP_output_folder_viridis_2025, recursive = TRUE, showWarnings = FALSE)

# Print the new output folder path
cat("Results will be saved to:", combined_climate_MSP_output_folder_viridis_2025, "\n")

#--------------------------------------------------------------------------
# Locate the climate raster files to process
#--------------------------------------------------------------------------

# Path to the climate projection files
climate_files_path <- here("output_data", "Combined_results", "ESM_agreement")

# Get all raster files in that directory
raster_files <- list.files(
  path = climate_files_path,
  pattern = "\\.tif$",
  full.names = TRUE
)

# Check if files were found
if(length(raster_files) == 0) {
  stop("No raster files found in: ", climate_files_path)
} else {
  cat("Found", length(raster_files), "raster files to process\n")
}

#--------------------------------------------------------------------------
# Define the Main Processing Function
#--------------------------------------------------------------------------

process_climate_MSP_constraints <- function(climate_raster_path, constraint_raster, output_folder, pattern) {
  # Print which file is being processed
  cat("Processing file:", basename(climate_raster_path), "\n")
  
  # Read the climate raster with error checking
  climate_raster <- try(rast(climate_raster_path))
  if(inherits(climate_raster, "try-error")) {
    cat("Error reading climate raster:", climate_raster_path, "\n")
    return(NULL)
  }
  
  # Verify both input rasters exist
  if(is.null(climate_raster) || is.null(constraint_raster)) {
    cat("Invalid raster input\n")
    return(NULL)
  }
  
  # Ensure climate raster is in the correct projection (Australian Albers)
  if(crs(climate_raster) != "EPSG:3577") {
    climate_raster <- project(climate_raster, "EPSG:3577")
  }
  
  # Align constraint raster with climate raster
  constraint_aligned <- resample(constraint_raster, climate_raster)
  
  # Multiply climate and constraint rasters to get combined analysis
  # Areas unsuitable due to constraints will be masked (multiplied by 0)
  combined_MSP_climate_analysis <- climate_raster * constraint_aligned
  
  # Extract information from filename to use in output names and titles
  file_name <- basename(climate_raster_path)
  parts <- unlist(strsplit(file_name, "_"))
  ssp <- parts[1]  # SSP scenario
  decade_range <- paste(parts[2], parts[3], sep = "_")  # Time period
  
  # Create visualization
  try({
    # Build map using tmap
    combined_MSP_climate_map_viridis <- tm_shape(climate_raster) +
      # Add climate suitability layer
      tm_raster(palette = c("#fcd225", "#c03a83", "#8606a6", "#0d0887"),
                labels = c("No Analogue", 
                          "Low Confidence Analogue", 
                          "Medium Confidence Analogue", 
                          "High Confidence Analogue"),
                breaks = c(-0.1, 0.5, 1.5, 2.5, 3.5),  # Control legend categories
                title = "Climate Suitability") +
      # Add constraints layer
      tm_shape(constraint_aligned) +
      tm_raster(palette = c("black", NA), 
                alpha = 0.5,
                labels = c("Unsuitable", ""),
                title = "Constraints",
                breaks = c(0, 0.5, 1)) +
      # Add Tasmania outline
      tm_shape(st_transform(tassie_shp, crs(climate_raster))) +
      tm_polygons(col = col = "white", border = "#373737", alpha = 0.2) +
      # Set map layout
      tm_layout(
        legend.outside = TRUE,
        legend.outside.position = "right",
        main.title = paste("Climate Analogues with Constraints:", ssp, decade_range, "-", pattern),
        main.title.position = "center",
        legend.text.size = 0.7,
        legend.title.size = 0.8,
        frame = TRUE
      )
    
    # Create separate folders for optimal and suitable patterns
    pattern_folder <- file.path(output_folder, pattern)
    dir.create(pattern_folder, recursive = TRUE, showWarnings = FALSE)
    
    # Save outputs:
    # 1. The combined analysis raster
    writeRaster(combined_MSP_climate_analysis,
                filename = file.path(pattern_folder, 
                                   paste0("combined_MSP_climate_", ssp, "_", 
                                         decade_range, "_", pattern, ".tif")),
                overwrite = TRUE)
    
    # 2. The visualization map
    tmap_save(combined_MSP_climate_map_viridis,
              filename = file.path(pattern_folder,
                                 paste0("combined_MSP_climate_map_viridis_", ssp, "_",
                                      decade_range, "_", pattern, ".png")),
              width = 8,
              height = 10,
              dpi = 300)
  })
  
  return(combined_MSP_climate_analysis)
}

#--------------------------------------------------------------------------
# Process All Files
#--------------------------------------------------------------------------

# Define which patterns to process
patterns <- c("optimal", "suitable")

# Process each pattern separately
for(pattern in patterns) {
  # Get files for current pattern
  pattern_files <- raster_files[grep(pattern, raster_files)]
  
  # Check if any files match the pattern
  if(length(pattern_files) == 0) {
    cat("No files found matching pattern:", pattern, "\n")
    next
  }
  
  test_file <- pattern_files[1]
  
  # Test with one file first
  cat("\nTesting with", pattern, "file:", basename(test_file), "\n")
  test_result <- try(process_climate_MSP_constraints(test_file, 
                                                   total_constraints, 
                                                   combined_climate_MSP_output_folder_viridis_2025,
                                                   pattern))
  
  # If test succeeds, process all files for this pattern
  if(!inherits(test_result, "try-error")) {
    cat("\nTest successful for", pattern, "pattern, processing all files...\n")
    combined_MSP_climate_results <- lapply(pattern_files, function(file) {
      try(process_climate_MSP_constraints(file, 
                                        total_constraints, 
                                        combined_climate_MSP_output_folder_viridis_2025,
                                        pattern))
    })
  } else {
    cat("Test failed for pattern:", pattern, "\n")
  }
}

cat("\nProcessing complete. Results saved to:", combined_climate_MSP_output_folder_viridis_2025, "\n")
```

#the first maps created were tilted therefore we made this other code
#non-tilted view for aesthetic reasons, we can create maps with a custom orientation. #function to produce non-tilted maps:

```{r}

# Create output folder for the combined climate and MSP analysis
combined_climate_MSP_output_folder_viridis_2025 <- here("output_data", "Climate_MSP_Constraints_2025")
dir.create(combined_climate_MSP_output_folder_viridis_2025, recursive = TRUE, showWarnings = FALSE)

# Print the output folder path
cat("Results will be saved to:", combined_climate_MSP_output_folder_viridis_2025, "\n")

#--------------------------------------------------------------------------
# Check versions of packages for diagnostics
#--------------------------------------------------------------------------
cat("Package versions:\n")
# Use a safer approach to display package versions
cat("terra version:", as.character(packageVersion("terra")), "\n")
cat("sf version:", as.character(packageVersion("sf")), "\n")

#--------------------------------------------------------------------------
# Locate the climate raster files to process
#--------------------------------------------------------------------------

# Path to the climate projection files
climate_files_path <- here("output_data", "Combined_results", "ESM_agreement")

# Get all raster files in that directory
raster_files <- list.files(
  path = climate_files_path,
  pattern = "\\.tif$",
  full.names = TRUE
)

# Check if files were found
if(length(raster_files) == 0) {
  stop("No raster files found in: ", climate_files_path)
} else {
  cat("Found", length(raster_files), "raster files to process\n")
}

#--------------------------------------------------------------------------
#  load Tasmania shapefile - ROI-in case map is not found they will be created despite that
#--------------------------------------------------------------------------
use_shapefile <- FALSE
tassie_shp <- NULL

# Try to find the shapefile in these locations
possible_paths <- c(
  here("raw_data", "tassie_shp.gpkg"),
  here("raw_data", "Tassie_Coast.shp")
)

cat("Searching for Tasmania shapefile...\n")
for (path in possible_paths) {
  cat("Checking:", path, "\n")
  if (file.exists(path)) {
    cat("Found shapefile at:", path, "\n")
    
    # Try to read the shapefile
    tryCatch({
      tassie_shp <- st_read(path, quiet = TRUE)
      use_shapefile <- TRUE
      cat("Tasmania shapefile loaded successfully\n")
      break
    }, error = function(e) {
      cat("Error loading shapefile:", conditionMessage(e), "\n")
    })
  }
}

if (!use_shapefile) {
  cat("WARNING: Tasmania shapefile not found or could not be loaded. Maps will be created without Tasmania outline.\n")
  cat("Available files in raw_data directory:\n")
  raw_files <- list.files(here("raw_data"), recursive = TRUE)
  cat(paste(raw_files, collapse = "\n"), "\n")
}

#--------------------------------------------------------------------------
# Load the constraints raster
#--------------------------------------------------------------------------
cat("Loading total constraints raster...\n")
constraints_path <- here("output_data", "Constraints_2024", "total_constraints.tif")

if(file.exists(constraints_path)) {
  total_constraints <- rast(constraints_path)
  cat("Constraints raster loaded successfully\n")
} else {
  stop("Total constraints raster not found at: ", constraints_path)
}

#--------------------------------------------------------------------------
# Define a minimal processing function that just creates the data files
#--------------------------------------------------------------------------

process_climate_constraints_minimal <- function(climate_raster_path, constraint_raster, output_folder, pattern) {
  tryCatch({
    # Print which file is being processed
    cat("Processing file:", basename(climate_raster_path), "\n")
    
    # Read the climate raster
    climate_raster <- rast(climate_raster_path)
    cat("Climate raster loaded successfully\n")
    
    # Extract information from filename
    file_name <- basename(climate_raster_path)
    parts <- unlist(strsplit(file_name, "_"))
    ssp <- parts[1]  # SSP scenario
    decade_range <- paste(parts[2], parts[3], sep = "_")  # Time period
    
    # Create output folder for this pattern
    pattern_folder <- file.path(output_folder, pattern)
    dir.create(pattern_folder, recursive = TRUE, showWarnings = FALSE)
    
    # Define output files
    raster_output_file <- file.path(pattern_folder, 
                                  paste0("combined_MSP_climate_", ssp, "_", 
                                        decade_range, "_", pattern, ".tif"))
    
    # Ensure climate raster is in Albers projection for analysis
    if(crs(climate_raster) != "EPSG:3577") {
      cat("Reprojecting climate raster to Albers...\n")
      climate_raster <- project(climate_raster, "EPSG:3577")
    }
    
    # Make sure constraint raster is also in Albers
    if(crs(constraint_raster) != "EPSG:3577") {
      cat("Reprojecting constraint raster to Albers...\n")
      constraint_raster <- project(constraint_raster, "EPSG:3577")
    }
    
    # Step 1: Align and multiply rasters
    cat("Aligning constraint raster with climate raster...\n")
    constraint_aligned <- resample(constraint_raster, climate_raster)
    
    cat("Creating combined analysis raster...\n")
    combined_analysis <- climate_raster * constraint_aligned
    
    # Step 2: Save the analysis raster
    cat("Saving combined analysis raster to:", raster_output_file, "\n")
    writeRaster(combined_analysis, filename = raster_output_file, overwrite = TRUE)
    
    # Skip visualization for now to ensure we at least get the data files
    cat("Successfully created combined analysis raster\n")
    return(TRUE)
    
  }, error = function(e) {
    cat("ERROR processing file:", basename(climate_raster_path), "\n")
    cat("Error message:", conditionMessage(e), "\n")
    return(FALSE)
  })
}

#--------------------------------------------------------------------------
# Process All Files - minimal approach to ensure we get the data
#--------------------------------------------------------------------------

# Define which patterns to process
patterns <- c("optimal", "suitable")

# Process each pattern separately
for(pattern in patterns) {
  # Get files for current pattern
  pattern_files <- raster_files[grep(pattern, raster_files)]
  
  # Check if any files match the pattern
  if(length(pattern_files) == 0) {
    cat("No files found matching pattern:", pattern, "\n")
    next
  }
  
  cat("\nFound", length(pattern_files), "files for pattern:", pattern, "\n")
  
  # Process all files for this pattern
  successful_files <- 0
  failed_files <- 0
  
  for(i in seq_along(pattern_files)) {
    file <- pattern_files[i]
    cat("\nProcessing file", i, "of", length(pattern_files), ":", basename(file), "\n")
    
    # Process the file - just create the data raster
    result <- process_climate_constraints_minimal(
      file, 
      total_constraints,
      combined_climate_MSP_output_folder_viridis_2025,
      pattern
    )
    
    # Track success/failure
    if(result) {
      successful_files <- successful_files + 1
    } else {
      failed_files <- failed_files + 1
    }
    
    # Add a brief pause between files
    Sys.sleep(1)
    
    # Explicitly run garbage collection to free memory
    gc()
  }
  
  cat("\nPattern:", pattern, "- Successfully processed:", successful_files, "files, Failed:", failed_files, "files\n")
}

cat("\nData processing complete. Results saved to:", combined_climate_MSP_output_folder_viridis_2025, "\n")

# Print a summary of what was created
pattern_folders <- list.dirs(combined_climate_MSP_output_folder_viridis_2025, recursive = FALSE, full.names = FALSE)
if(length(pattern_folders) > 0) {
  for(folder_name in pattern_folders) {
    folder_path <- file.path(combined_climate_MSP_output_folder_viridis_2025, folder_name)
    tif_files <- list.files(folder_path, pattern = "\\.tif$")
    
    cat("\nPattern:", folder_name)
    cat("\n  Raster files created:", length(tif_files), "\n")
  }
} else {
  cat("\nNo pattern folders were created. Check for errors in the processing.\n")
}

cat("\nTo create visualization maps, we can run a separate script after the data files are generated.\n")
```

#making composite maps of climate projections and constraints
```{r}


# Create output folders
combined_climate_MSP_output_folder_viridis_2025 <- here("output_data", "Climate_MSP_Constraints_2025")
composite_maps_folder_viridis <- here("output_data", "Climate_MSP_Constraints_NonTilted_2025", "Composite_Maps")

dir.create(combined_climate_MSP_output_folder_viridis_2025, recursive = TRUE, showWarnings = FALSE)
dir.create(composite_maps_folder_viridis, recursive = TRUE, showWarnings = FALSE)

# Print the output folder path
cat("Results will be saved to:", combined_climate_MSP_output_folder_viridis_2025, "\n")
cat("Composite maps will be saved to:", composite_maps_folder_viridis, "\n")

#--------------------------------------------------------------------------
# Locate the climate raster files to process
#--------------------------------------------------------------------------

# Path to the climate projection files
climate_files_path <- here("output_data", "Combined_results", "ESM_agreement")

# Get all raster files in that directory
raster_files <- list.files(
  path = climate_files_path,
  pattern = "\\.tif$",
  full.names = TRUE
)

# Check if files were found
if(length(raster_files) == 0) {
  stop("No raster files found in: ", climate_files_path)
} else {
  cat("Found", length(raster_files), "raster files to process\n")
}

#--------------------------------------------------------------------------
# Try to load Tasmania shapefile - but continue without it if not found
#--------------------------------------------------------------------------
use_shapefile <- FALSE
tassie_shp <- NULL

# Try to find the shapefile in various locations
possible_paths <- c(
  here("raw_data", "tassie_shp.gpkg"),
  here("raw_data", "Tassie_Coast.shp")
)

cat("Searching for Tasmania shapefile...\n")
for (path in possible_paths) {
  cat("Checking:", path, "\n")
  if (file.exists(path)) {
    cat("Found shapefile at:", path, "\n")
    
    # Try to read the shapefile
    tryCatch({
      tassie_shp <- st_read(path, quiet = TRUE)
      use_shapefile <- TRUE
      cat("Tasmania shapefile loaded successfully\n")
      break
    }, error = function(e) {
      cat("Error loading shapefile:", conditionMessage(e), "\n")
    })
  }
}

if (!use_shapefile) {
  cat("WARNING: Tasmania shapefile not found or could not be loaded. Maps will be created without Tasmania outline.\n")
}

#--------------------------------------------------------------------------
# Load the constraints raster
#--------------------------------------------------------------------------
cat("Loading total constraints raster...\n")
constraints_path <- here("output_data", "Constraints_2024", "total_constraints.tif")

if(file.exists(constraints_path)) {
  total_constraints <- rast(constraints_path)
  cat("Constraints raster loaded successfully\n")
} else {
  stop("Total constraints raster not found at: ", constraints_path)
}

#--------------------------------------------------------------------------
# Define the processing function that creates non-tilted data and maps
#--------------------------------------------------------------------------

process_climate_constraints_with_maps <- function(climate_raster_path, constraint_raster, output_folder, pattern) {
  tryCatch({
    # Print which file is being processed
    cat("Processing file:", basename(climate_raster_path), "\n")
    
    # Read the climate raster
    climate_raster <- rast(climate_raster_path)
    cat("Climate raster loaded successfully\n")
    
    # Extract information from filename
    file_name <- basename(climate_raster_path)
    parts <- unlist(strsplit(file_name, "_"))
    ssp <- parts[1]  # SSP scenario
    decade_range <- paste(parts[2], parts[3], sep = "_")  # Time period
    
    # Create output folder for this pattern
    pattern_folder <- file.path(output_folder, pattern)
    dir.create(pattern_folder, recursive = TRUE, showWarnings = FALSE)
    
    # Define output files
    raster_output_file <- file.path(pattern_folder, 
                                  paste0("combined_MSP_climate_", ssp, "_", 
                                        decade_range, "_", pattern, ".tif"))
    map_output_file <- file.path(pattern_folder,
                               paste0("combined_MSP_climate_map_viridis_", ssp, "_",
                                     decade_range, "_", pattern, ".png"))
    
    # Ensure climate raster is in Albers projection for analysis
    if(crs(climate_raster) != "EPSG:3577") {
      cat("Reprojecting climate raster to Albers...\n")
      climate_raster <- project(climate_raster, "EPSG:3577")
    }
    
    # Make sure constraint raster is also in Albers
    if(crs(constraint_raster) != "EPSG:3577") {
      cat("Reprojecting constraint raster to Albers...\n")
      constraint_raster <- project(constraint_raster, "EPSG:3577")
    }
    
    # Step 1: Align and multiply rasters
    cat("Aligning constraint raster with climate raster...\n")
    constraint_aligned <- resample(constraint_raster, climate_raster)
    
    cat("Creating combined analysis raster...\n")
    combined_analysis <- climate_raster * constraint_aligned
    
    # Step 2: Save the analysis raster
    cat("Saving combined analysis raster to:", raster_output_file, "\n")
    writeRaster(combined_analysis, filename = raster_output_file, overwrite = TRUE)
    
    # Step 3: Create visualization in WGS84 (non-tilted)
    cat("Creating visualization in WGS84...\n")
    
    # Project both rasters to WGS84 for mapping
    climate_wgs84 <- project(climate_raster, "EPSG:4326")
    constraint_wgs84 <- project(constraint_aligned, "EPSG:4326")
    
    # Get raster data for ggplot
    climate_df <- as.data.frame(climate_wgs84, xy = TRUE)
    colnames(climate_df)[3] <- "value"
    
    constraint_df <- as.data.frame(constraint_wgs84, xy = TRUE)
    colnames(constraint_df)[3] <- "value"
    
    # Define bounding box for Tasmania region
    bbox <- c(140, -45, 155, -39)
    
    # Create a ggplot map
    p <- ggplot() +
      # Add climate layer
      geom_raster(data = climate_df, 
                  aes(x = x, y = y, fill = factor(value))) +
      # Add constraint layer
      geom_raster(data = constraint_df %>% filter(value == 0), 
            aes(x = x, y = y), 
            fill = "grey80", alpha = 1) +
      # Add Tasmania outline if available
      {if (use_shapefile) geom_sf(
  data = st_transform(tassie_shp, "EPSG:4326"),
  color = "#373737",  # border color
  fill = "white",      # interior fill
  size = 0.3
)} +
      # Set color scheme
      scale_fill_manual(
        values = c("0" = "#fcd225", "1" = "#c03a83", "2" = "#8606a6", "3" = "#0d0887", "NA" = NA),
        labels = c("No Analogue", "Low Confidence", "Medium Confidence", "High Confidence"),
        name = "Climate Viability"
      ) +
      # Set coordinate system and limits
      coord_sf(xlim = c(bbox[1], bbox[3]), ylim = c(bbox[2], bbox[4])) +
      theme_void() +  # Use theme_void() instead of theme_map()
  theme(
    plot.title = element_text(size = 10, face = "bold", hjust = 0.5),
    legend.position = "none",
    plot.margin = margin(0.5, 0.5, 0.5, 0.5, "pt"),  # Minimal margins
    axis.title = element_blank(),  # Remove axis titles
    axis.text = element_blank(),   # Remove axis text
    axis.ticks = element_blank()   # Remove axis ticks
  )
    
    # Save the individual map
    ggsave(map_output_file, p, width = 4, height = 4, dpi = 300)
    
    cat("Successfully created map:", map_output_file, "\n")
    
    # Return information about this map for the composite
    return(list(
      path = map_output_file,
      ssp = ssp,
      decade = decade_range,
      pattern = pattern,
      plot = p
    ))
    
  }, error = function(e) {
    cat("ERROR processing file:", basename(climate_raster_path), "\n")
    cat("Error message:", conditionMessage(e), "\n")
    return(NULL)
  })
}

#--------------------------------------------------------------------------
# Process All Files - creating data and maps
#--------------------------------------------------------------------------

# Define which patterns to process
patterns <- c("optimal", "suitable")

# Storage for map information
all_maps <- list()

# Process each pattern separately
for(pattern in patterns) {
  # Get files for current pattern
  pattern_files <- raster_files[grep(pattern, raster_files)]
  
  # Check if any files match the pattern
  if(length(pattern_files) == 0) {
    cat("No files found matching pattern:", pattern, "\n")
    next
  }
  
  cat("\nFound", length(pattern_files), "files for pattern:", pattern, "\n")
  
  # Create storage for this pattern's maps
  pattern_maps <- list()
  
  # Process all files for this pattern
  for(i in seq_along(pattern_files)) {
    file <- pattern_files[i]
    cat("\nProcessing file", i, "of", length(pattern_files), ":", basename(file), "\n")
    
    # Process the file and get map info
    map_info <- process_climate_constraints_with_maps(
      file, 
      total_constraints,
      combined_climate_MSP_output_folder_viridis_2025,
      pattern
    )
    
    # Store map info if successful
    if(!is.null(map_info)) {
      pattern_maps[[length(pattern_maps) + 1]] <- map_info
    }
    
    # Add a brief pause between files and clear memory
    Sys.sleep(0.5)
    gc()
  }
  
  # Store all maps for this pattern
  all_maps[[pattern]] <- pattern_maps
  
  cat("\nCompleted processing for pattern:", pattern, "\n")
}

cat("\nAll individual maps and data created. Now generating composite maps...\n")

#--------------------------------------------------------------------------
# Create composite maps for each pattern
#--------------------------------------------------------------------------

# Extract available decades and SSPs
decades <- unique(sapply(unlist(all_maps, recursive = FALSE), function(x) x$decade))
ssps <- unique(sapply(unlist(all_maps, recursive = FALSE), function(x) x$ssp))

# Order them
decades <- sort(decades)
ssps <- sort(ssps)

cat("Available decades:", paste(decades, collapse=", "), "\n")
cat("Available SSPs:", paste(ssps, collapse=", "), "\n")

# Create composite maps for each pattern
for(pattern in patterns) {
  cat("\nCreating composite map for pattern:", pattern, "\n")
  
  pattern_maps <- all_maps[[pattern]]
  
  if(length(pattern_maps) == 0) {
    cat("No maps available for pattern:", pattern, "\n")
    next
  }
  
  # Create a dataframe to make it easier to work with
  map_df <- data.frame(
    path = sapply(pattern_maps, function(x) x$path),
    ssp = sapply(pattern_maps, function(x) x$ssp),
    decade = sapply(pattern_maps, function(x) x$decade),
    stringsAsFactors = FALSE
  )
  
  # Convert SSP and decade to factors with correct order
  map_df$ssp <- factor(map_df$ssp, levels = ssps)
  map_df$decade <- factor(map_df$decade, levels = decades)
  
  # Load all PNG files
  plot_list <- list()
  
  for(i in 1:nrow(map_df)) {
    plot_list[[i]] <- pattern_maps[[i]]$plot +
      labs(title = paste0(map_df$ssp[i], " - ", map_df$decade[i]))
  }
  
  
  # Create legend (for the composite map) - updated to show grey80 for constraints
legend_plot <- ggplot() +
  # Create dummy data for legend including constrained areas
  geom_point(data = data.frame(
    x = c(1:4, 5),
    y = 1,
    value = factor(c(0:3, "constrained"))
  ), aes(x = x, y = y, color = value)) +
  scale_color_manual(
    values = c("0" = "#fcd225", "1" = "#c03a83", "2" = "#8606a6", "3" = "#0d0887", "constrained" = "grey80"),
    labels = c("No Analogue", "Low Confidence", "Medium Confidence", "High Confidence", "Unsuitable"),
    name = "Climate Suitability"
  ) +
    theme_map() +
    theme(legend.position = "bottom") +
    guides(color = guide_legend(nrow = 1))
  
  # Extract the legend
  legend <- get_legend(legend_plot)
  
  # Calculate grid dimensions
  n_decades <- length(decades)
  n_ssps <- length(ssps)
  
  # Create an ordered list of plots for the grid
  ordered_plots <- matrix(list(), nrow = n_ssps, ncol = n_decades)
  colnames(ordered_plots) <- decades
  rownames(ordered_plots) <- ssps
  
  # Fill in the matrix with plots
  for(i in 1:nrow(map_df)) {
    ssp <- as.character(map_df$ssp[i])
    decade <- as.character(map_df$decade[i])
    ordered_plots[ssp, decade] <- plot_list[i]
  }
  
  # Flatten the matrix by rows
  plot_grid <- NULL
  for(i in 1:n_ssps) {
    row_plots <- do.call(wrap_plots, c(ordered_plots[i,], ncol = n_decades))
    if(is.null(plot_grid)) {
      plot_grid <- row_plots
    } else {
      plot_grid <- plot_grid / row_plots
    }
  }
  
  # Add decade labels at the top
  decade_labels <- plot_grid(
    plotlist = lapply(decades, function(d) {
      ggplot() + 
        annotate("text", x = 0.5, y = 0.5, label = d, size = 3) + 
        theme_map()
    }),
    ncol = length(decades)
  )
  
  # Add SSP labels on the left
  ssp_labels <- plot_grid(
    plotlist = lapply(ssps, function(s) {
      ggplot() + 
        annotate("text", x = 0.5, y = 0.5, label = s, size = 3, angle = 90) + 
        theme_map()
    }),
    nrow = length(ssps)
  )
  
  # Combine everything
  final_plot <- plot_grid(
    decade_labels, 
    plot_grid(ssp_labels, plot_grid, ncol = 2, rel_widths = c(0.05, 0.95)),
    legend,
    ncol = 1,
    rel_heights = c(0.05, 0.9, 0.05)
  )
  
  # Save the composite map
  composite_filename <- file.path(composite_maps_folder_viridis, paste0("composite_map_", pattern, ".png"))
  save_plot(composite_filename, final_plot, base_width = 12, base_height = 8, dpi = 300)
  
  cat("Composite map saved to:", composite_filename, "\n")
  
  # Also create a simplified version with just the grid of maps
  ggsave(
    file.path(composite_maps_folder_viridis, paste0("composite_map_simple_", pattern, ".png")),
    plot_grid,
    width = 12, height = 8, dpi = 300
  )
}

cat("\nAll processing complete!\n")
cat("Individual maps and data are saved in:", combined_climate_MSP_output_folder_viridis_2025, "\n")
cat("Composite maps are saved in:", composite_maps_folder_viridis, "\n")
```


#code adjusted to make a better composite map 11 aug 2025 with ajustments 16oct2025
# Note: This script will attempt to use magick for image cropping
# Install if needed: install.packages("magick")
```{r}

library(png)
library(grid)
library(webshot2)
library(here)

# Define input and output directories
input_folder <- here("output_data", "Climate_MSP_Constraints_2025")
output_folder <- here("output_data", "Climate_MSP_Constraints_NonTilted_2025", "Composite_maps")

# Create output directory if it doesn't exist
if (!dir.exists(output_folder)) {
  dir.create(output_folder, recursive = TRUE)
}

# Get all PNG files from both pattern folders
optimal_folder <- file.path(input_folder, "optimal")
suitable_folder <- file.path(input_folder, "suitable")

# List all PNG files from both folders
optimal_files <- if(dir.exists(optimal_folder)) {
  list.files(optimal_folder, pattern = "\\.png$", full.names = TRUE)
} else {
  character(0)
}

suitable_files <- if(dir.exists(suitable_folder)) {
  list.files(suitable_folder, pattern = "\\.png$", full.names = TRUE)
} else {
  character(0)
}

# Combine all files
plot_files <- c(optimal_files, suitable_files)

if (length(plot_files) == 0) {
  stop("No PNG files found in optimal or suitable folders in ", input_folder)
}

# Function to format SSP labels properly
format_ssp_label <- function(ssp_raw) {
  # Convert from formats like "ssp119" to "SSP1-1.9"
  ssp_upper <- toupper(ssp_raw)
  
  # Handle different SSP formats
  if (grepl("SSP119", ssp_upper)) return("SSP1-1.9")
  if (grepl("SSP126", ssp_upper)) return("SSP1-2.6")
  if (grepl("SSP245", ssp_upper)) return("SSP2-4.5")
  if (grepl("SSP370", ssp_upper)) return("SSP3-7.0")
  if (grepl("SSP585", ssp_upper)) return("SSP5-8.5")
  
  # Fallback: return as uppercase if no match
  return(ssp_upper)
}

# Function to format decade labels properly
format_decade_label <- function(decade_raw) {
  # Convert from formats like "2021_2030" to "2021-2030"
  if (grepl("_", decade_raw)) {
    parts <- strsplit(decade_raw, "_")[[1]]
    if (length(parts) == 2) {
      start_year <- parts[1]
      end_year <- parts[2]
      return(paste0(start_year, "-", end_year))
    }
  }
  
  # Fallback: return original if can't parse
  return(decade_raw)
}

# Extract metadata from filenames
extract_metadata <- function(filename) {
  basename_file <- basename(filename)
  
  # Determine pattern from the folder path
  if (grepl("/optimal/", filename)) {
    pattern <- "optimal"
  } else if (grepl("/suitable/", filename)) {
    pattern <- "suitable"
  } else {
    pattern <- "unknown"
  }
  
  # Extract SSP and decade from filename
  # Assuming format like: optimal_ssp119_2021_2030.png or similar
  parts <- strsplit(basename_file, "_")[[1]]
  
  # Remove .png extension from last part
  last_part <- parts[length(parts)]
  parts[length(parts)] <- sub("\\.png$", "", last_part)
  
  # Try to identify SSP and decade parts
  ssp_raw <- NA
  decade_range <- NA
  
  # Look for SSP pattern
  for(i in 1:length(parts)) {
    if(grepl("^ssp[0-9]+$", parts[i], ignore.case = TRUE)) {
      ssp_raw <- parts[i]
      # Try to find decade parts after SSP
      if(i + 2 <= length(parts) && 
         grepl("^[0-9]{4}$", parts[i+1]) && 
         grepl("^[0-9]{4}$", parts[i+2])) {
        decade_range <- paste(parts[i+1], parts[i+2], sep="_")
      }
      break
    }
  }
  
  return(list(
    ssp = ssp_raw,
    ssp_formatted = if(!is.na(ssp_raw)) format_ssp_label(ssp_raw) else NA,
    decade = decade_range,
    decade_formatted = if(!is.na(decade_range)) format_decade_label(decade_range) else NA,
    pattern = pattern,
    path = filename
  ))
}

# Get metadata for all files
all_metadata <- lapply(plot_files, extract_metadata)

# Get unique patterns, SSPs, and decades (using raw values for processing)
patterns <- unique(sapply(all_metadata, function(x) x$pattern))
ssps <- unique(sapply(all_metadata, function(x) x$ssp))
decades <- unique(sapply(all_metadata, function(x) x$decade))

# Ensure they are character vectors (atomic)
patterns <- as.character(patterns)
ssps <- as.character(ssps)
decades <- as.character(decades)

# Remove any NA values
patterns <- patterns[!is.na(patterns)]
ssps <- ssps[!is.na(ssps)]
decades <- decades[!is.na(decades)]

# Sort them
ssps <- sort(ssps)
decades <- sort(decades)
patterns <- sort(patterns)

# Create formatted versions for display
ssps_formatted <- sapply(ssps, function(x) format_ssp_label(x))
decades_formatted <- sapply(decades, function(x) format_decade_label(x))

# Create proper mapping for sorted display
ssp_mapping <- setNames(ssps_formatted, ssps)
decade_mapping <- setNames(decades_formatted, decades)

cat("Available decades:", paste(decades, collapse=", "), "\n")
cat("Available SSPs:", paste(ssps, collapse=", "), "\n")
cat("Formatted decades:", paste(decades_formatted, collapse=", "), "\n")
cat("Formatted SSPs:", paste(ssps_formatted, collapse=", "), "\n")

# Function to find matching map
find_map <- function(pattern_metadata, ssp, decade) {
  for(i in 1:length(pattern_metadata)) {
    if(pattern_metadata[[i]]$ssp == ssp && 
       pattern_metadata[[i]]$decade == decade) {
      return(pattern_metadata[[i]]$path)
    }
  }
  return(NA)
}

# Create composite maps for each pattern
for(pattern in patterns) {
  cat("\nCreating composite map for pattern:", pattern, "\n")
  
  # Filter files for this pattern
  pattern_metadata <- all_metadata[sapply(all_metadata, function(x) x$pattern == pattern)]
  
  if(length(pattern_metadata) == 0) {
    cat("No maps available for pattern:", pattern, "\n")
    next
  }
  
  # Create individual maps directory with v2 suffix
  individual_maps_dir <- file.path(output_folder, 
                                  paste0("individual_maps_", pattern, "_v2"))
  if(!dir.exists(individual_maps_dir)) {
    dir.create(individual_maps_dir, recursive = TRUE)
  }
  
  # Save individual maps with cropping
  for(s in 1:length(ssps)) {
    for(d in 1:length(decades)) {
      current_ssp <- ssps[s]
      current_decade <- decades[d]
      
      # Create filename for this map
      map_filename <- file.path(individual_maps_dir, 
                               paste0(pattern, "_", current_ssp, "_", current_decade, ".png"))
      
      # Find matching map
      map_path <- find_map(pattern_metadata, current_ssp, current_decade)
      
      if(!is.na(map_path) && file.exists(map_path)) {
        
        # Read, crop (to remove borders and keep only map), and save the image
        tryCatch({
          library(magick)
          img <- image_read(map_path)
          
          # Get image dimensions
          info <- image_info(img)
          width <- info$width
          height <- info$height
          
          # Crop to remove borders AND TITLES from all sides
          # Remove borders: left 15%, right 15%, top 20% (to remove title), bottom 5%
          crop_left <- floor(width * 0.15)     # Start 15% from left
          crop_top <- floor(height * 0.20)     # Start 20% from top (to remove title)
          crop_width <- floor(width * 0.70)    # Keep 70% of width (15% + 70% = 85%, removing 15% from right)
          crop_height <- floor(height * 0.75)  # Keep 75% of height (20% + 75% = 95%, removing 5% from bottom)
          
          # Crop: geometry format is "WIDTHxHEIGHT+X_OFFSET+Y_OFFSET"
          crop_geometry <- paste0(crop_width, "x", crop_height, "+", crop_left, "+", crop_top)
          cropped_img <- image_crop(img, crop_geometry)
          
          # Save cropped image
          image_write(cropped_img, map_filename)
          
        }, error = function(e) {
          # If magick fails, just copy the original file
          cat("Warning: Could not crop image", map_path, ". Using original.\n")
          cat("Error:", e$message, "\n")
          file.copy(map_path, map_filename, overwrite = TRUE)
        })
        
      } else {
        # Create a blank image
        png(map_filename, width = 300, height = 300)
        plot.new()
        box("figure", col = "lightgrey")
        dev.off()
      }
    }
  }
  
  # Create an ultra-clean HTML table for viewing with v2 suffix
  html_file <- file.path(output_folder, 
                        paste0("composite_map_", pattern, "_minimal_v2.html"))
  
  html_content <- c(
    "<!DOCTYPE html>",
    "<html>",
    "<head>",
    paste0("<title>", pattern, " Climate Analogues</title>"),
    "<style>",
    "* { margin: 0; padding: 0; box-sizing: border-box; }",
    "body { font-family: 'Segoe UI', Tahoma, Geneva, Verdana, sans-serif; background: #f8f9fa; padding: 15px; }",
    ".container { max-width: 1400px; margin: 0 auto; background: white; border-radius: 8px; overflow: hidden; box-shadow: 0 4px 12px rgba(0,0,0,0.1); }",
    ".header { background: linear-gradient(135deg, #667eea 0%, #764ba2 100%); color: white; padding: 20px; text-align: center; }",
    ".title { font-size: 28px; font-weight: 600; margin-bottom: 5px; }",
    ".subtitle { font-size: 14px; opacity: 0.9; }",
    ".grid-container { display: grid; padding: 0; gap: 2px; background: #e9ecef; border-spacing: 2px; }",
    paste0(".grid-container { grid-template-columns: 80px repeat(", length(decades), ", 1fr); }"),
    ".grid-header { background: #495057; color: white; font-weight: 600; font-size: 13px; display: flex; align-items: center; justify-content: center; padding: 12px 8px; }",
    ".grid-cell { background: white; position: relative; padding: 2px; border: 1px solid #eee; }",
    ".grid-cell::after { content: ''; display: block; padding-bottom: 75%; /* Maintain aspect ratio */ }",
    ".grid-cell img { position: absolute; top: 0; left: 0; width: 100%; height: 100%; object-fit: cover; }",
    ".row-header { background: #6c757d; color: white; font-weight: 600; font-size: 12px; writing-mode: horizontal-tb; display: flex; align-items: center; justify-content: center; padding: 8px; }",
    ".legend { padding: 20px; background: #f8f9fa; border-top: 1px solid #dee2e6; }",
    ".legend-title { font-weight: 600; margin-bottom: 10px; color: #495057; font-size: 14px; }",
    ".legend-items { display: flex; justify-content: center; flex-wrap: wrap; gap: 15px; }",
    ".legend-item { display: flex; align-items: center; font-size: 16px; }",
    ".legend-color { width: 18px; height: 18px; border-radius: 3px; margin-right: 6px; border: 1px solid rgba(0,0,0,0.1); }",
    "@media (max-width: 768px) { .grid-container { grid-template-columns: 60px repeat(", length(decades), ", 1fr); } .title { font-size: 20px; } }",
    "</style>",
    "</head>",
    "<body>",
    "<div class='container'>",
    "<div class='grid-container'>"
  )
  
  # Add headers row with formatted decade labels
  html_content <- c(html_content, "<div class='grid-header'></div>") # Empty corner
  for(d in 1:length(decades)) {
    formatted_decade <- decade_mapping[decades[d]]
    html_content <- c(html_content, paste0("<div class='grid-header'>", formatted_decade, "</div>"))
  }
  
  # Add data rows with formatted SSP labels
  for(s in 1:length(ssps)) {
    current_ssp <- ssps[s]
    formatted_ssp <- ssp_mapping[current_ssp]
    html_content <- c(html_content, paste0("<div class='row-header'>", formatted_ssp, "</div>"))
    
    for(d in 1:length(decades)) {
      current_decade <- decades[d]
      # Updated path to use v2 folder
      img_path <- paste0("individual_maps_", pattern, "_v2/", 
                        pattern, "_", current_ssp, "_", current_decade, ".png")
      formatted_decade <- decade_mapping[current_decade]
      html_content <- c(html_content, paste0("<div class='grid-cell'><img src='", img_path, 
                                          "' alt='", formatted_ssp, " - ", formatted_decade, "'></div>"))
    }
  }
  
  # Close grid and add legend
  # Fixed HTML generation section - replace the problematic legend part

# Close grid and add legend - 
html_content <- c(
  html_content,
  "</div>",
  "<div class='legend'>",
  "<div class='legend-title'>  Confidence level(Agreement among ESMs) </div>",
  "<div class='legend-items'>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #E5E5E5;'></div>Constrained areas</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #fcd225;'></div>No analogue (&lt;25%)</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #c03a83;'></div>Low confidence (≥25% to &lt;50%)</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #8606a6;'></div>Medium confidence(≥50% to &lt;75%)</div>",
  "<div class='legend-item'><div class='legend-color' style='background-color: #0d0887;'></div>High confidence (≥75%)</div>",
  "</div>",
  "</div>",
  "</div>",
  "</body>",
  "</html>"
)

# Write the HTML file
writeLines(html_content, html_file)
cat("Minimal HTML view saved to:", html_file, "\n")
  
  
  # Create high-quality PNG composite using base R with minimal spacing
  output_file <- file.path(output_folder, 
                          paste0("composite_map_", pattern, "_tight_v2.png"))
  
  # Write the HTML file
writeLines(html_content, html_file)
cat("Minimal HTML view saved to:", html_file, "\n")

# Convert HTML to PNG
png_output_file <- file.path(output_folder, 
                            paste0("composite_map_", pattern, "_minimal_v2.png"))

if(require(webshot2, quietly = TRUE)) {
  webshot2::webshot(
    url = html_file,
    file = png_output_file,
    vwidth = 1400,
    vheight = 1000,
    zoom = 2,
    delay = 2,
    cliprect = "viewport"
  )
  cat("HTML converted to PNG:", png_output_file, "\n")
} else {
  cat("webshot2 not available. Install with: install.packages('webshot2')\n")
}
  
  # Calculate dimensions
  n_ssps <- length(ssps)
  n_decades <- length(decades)
  
  # Create high-resolution PNG
  png(output_file, width = n_decades * 4 + 1.5, height = n_ssps * 3 + 2, 
      units = "in", res = 300, bg = "white")
  
  # Set up minimal margins and tight layout
  par(mar = c(0.5, 1, 1.5, 0.1), oma = c(0, 0, 0, 0))
  
  # Create plotting area
  plot.new()
  plot.window(xlim = c(0, n_decades + 0.8), ylim = c(0, n_ssps + 0.3))
  
  # Add title at the top
  text(x = (n_decades + 0.8)/2, y = n_ssps + 0.15, 
       labels = paste(toupper(substr(pattern, 1, 1)), 
                    substr(pattern, 2, nchar(pattern)), 
                    "Climate Analogues"),
       cex = 1.4, font = 2, col = "#2c3e50")
  
  # Add decade headers with formatted labels and minimal spacing
  for(d in 1:n_decades) {
    formatted_decade <- decade_mapping[decades[d]]
    text(x = d - 0.1, y = n_ssps - 0.05, labels = formatted_decade, 
         cex = 0.9, font = 2, col = "#34495e")
  }
  
  # Add formatted SSP labels on the left with minimal spacing
  for(s in 1:n_ssps) {
    formatted_ssp <- ssp_mapping[ssps[s]]
    text(x = -0.15, y = n_ssps - s + 0.5, labels = formatted_ssp, 
         cex = 0.9, font = 2, srt = 0, col = "#34495e")
  }
  
  # Draw maps with minimal gaps
  for(s in 1:n_ssps) {
    for(d in 1:n_decades) {
      # Tight cell boundaries - much smaller gaps
      x_min <- d - 0.48
      x_max <- d + 0.48
      y_min <- n_ssps - s + 0.02
      y_max <- n_ssps - s + 0.98
      
      # Add subtle border
      rect(x_min, y_min, x_max, y_max, border = "#bdc3c7", lwd = 0.3)
      
      # Load and display image
      current_ssp <- ssps[s]
      current_decade <- decades[d]
      map_path <- find_map(pattern_metadata, current_ssp, current_decade)
      
      if(!is.na(map_path) && file.exists(map_path)) {
        
        tryCatch({
          img <- png::readPNG(map_path)
          rasterImage(img, x_min, y_min, x_max, y_max)
        }, error = function(e) {
          # Draw placeholder for missing images
          rect(x_min, y_min, x_max, y_max, col = "#ecf0f1", border = "#bdc3c7")
          text((x_min + x_max)/2, (y_min + y_max)/2, "No Data", 
               cex = 0.7, col = "#7f8c8d")
        })
      } else {
        # Draw placeholder
        rect(x_min, y_min, x_max, y_max, col = "#ecf0f1", border = "#bdc3c7")
        text((x_min + x_max)/2, (y_min + y_max)/2, "No Data", 
             cex = 0.7, col = "#7f8c8d")
      }
    }
  }
  
  dev.off()
  
  cat("Tight grid PNG saved to:", output_file, "\n")
}

cat("\nAll processing complete!\n")
cat("Clean composites saved in:", output_folder, "\n")

```

# Go to code 16_km2_area_climate_and_constraints_plots_EF_Oct25


