---
title: "18_Marine territories Map with inset"

date: 1st version "2025-05-16" this version"2025-10-27"
author: Marina Christofidis (marina.christofidis@griffithuni.edu.au)

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown


#making the map
```{r}
library(sf)
library(dplyr)
library(here)
library(ggplot2)
library(viridis)
library(tmap)

```


```{r}
# 1.  Create bbox in Albers
bbox_albers <- st_bbox(c(xmin = 140.995, xmax = 153.005, ymin = -47.255, ymax = -38.995)) %>%
  st_as_sfc() %>%
  st_as_sf() %>%
  st_set_crs(4326) %>%
  st_transform(3577)

#2. Load and process all required data


coastal_waters <- st_read(here("raw_data/Coastal_Waters_areas_(AMB2020)/Coastal_Waters_areas_(AMB2020).shp"))%>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

commonwealth_waters <- st_read(here("raw_data/Commonwealth_Marine_Regions/Commonwealth_Marine_Regions.shp")) %>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

terrestrial_areas <- st_read(here("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp")) %>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

# 3. Crop all layers to bbox

terrestrial_areas_crop <- st_intersection(terrestrial_areas, bbox_albers)
coastal_waters_crop <- st_intersection(coastal_waters, bbox_albers)
commonwealth_crop <- st_intersection(commonwealth_waters, bbox_albers)



state_waters<-st_difference(coastal_waters_crop, st_union(terrestrial_areas_crop))


# 4. Create High Seas
all_managed_waters_and_land <- bind_rows(
  st_set_geometry(commonwealth_crop, "geometry") %>% mutate(zone_type = "Commonwealth"),
  st_set_geometry(state_waters, "geometry") %>% mutate(zone_type = "State"),
  st_set_geometry(terrestrial_areas_crop, "geometry") %>% mutate(zone_type = "terrestrial_areas")
)

high_seas <- st_difference(bbox_albers, st_union(all_managed_waters_and_land))
```

```{r}
# 6. Create the map
territories_map_viridis <- ggplot() +
  # Add High Seas
  geom_sf(data = high_seas, 
          aes(fill = "High Seas"),
          color = NA) +
  # Add Commonwealth waters
  geom_sf(data = commonwealth_crop, 
          aes(fill = "Commonwealth Waters"),
          color = NA) +
  # Add State waters
  geom_sf(data = state_waters, 
          aes(fill = "State Waters"),
          color = NA) +
  # Add all terrestrial areas
  geom_sf(data = terrestrial_areas_crop, 
          aes(fill = "terrestrial_areas"),
          color = "black") +
  
  # Use viridis palette
  scale_fill_viridis_d(
    name = "Territories",
    option = "mako",
    begin = 0.2,
    end = 0.9,
    direction = -1
  ) +
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text = element_text(size = 8),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12),
    panel.grid.major = element_line(color = "gray80"),
    panel.grid.minor = element_line(color = "gray90")
  ) +
  labs(
    title = "Australian Marine Territories Around Tasmania",
    x = "Longitude",
    y = "Latitude"
  ) +
  coord_sf(
    crs = 3577,
    xlim = st_bbox(bbox_albers)[c(1,3)],
    ylim = st_bbox(bbox_albers)[c(2,4)]
  )

# Save the plot
ggsave(here("Figures", "Australian_territories_Tasmania_viridis.png"), 
       territories_map_viridis, 
       width = 10, 
       height = 8, 
       dpi = 300)

```

```{r}
plot(territories_map_viridis)
```




#BEST MAP
```{r}
finfish_farms<-st_read(here("raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp"))
```


#best map no grids
```{r}

finfish_farms <- st_read(here("raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp"))%>%
  st_transform("EPSG:3577")%>%
  st_make_valid()


# Create the map
territories_map <- ggplot() +
  # High Seas (base layer)
  geom_sf(data = high_seas,
          aes(color = "High Seas"),
          fill = "lightblue",
          alpha = 0.6) +
  
  # Land areas
  geom_sf(data = terrestrial_areas_crop, 
          fill = "grey40",
          color = "black") +
  
  # Commonwealth Waters boundary
  geom_sf(data = commonwealth_crop,
          aes(color = "Commonwealth Waters"),
          fill = NA,
          size = 1) +
  
  # State Waters boundary
  geom_sf(data = state_waters,
          aes(color = "State Waters"),
          size = 1) +
  
  # Finfish farms
  geom_sf(data = finfish_farms,
          aes(color = "Finfish Farms"),
          size = 2,
          shape = 21,
          fill = "salmon") +
  
  scale_color_manual(
    name = "Maritime Zones and Sites",
    values = c(
      "High Seas" = "lightblue",
      "Commonwealth Waters" = mako(5)[2],
      "State Waters" = mako(5)[4],
      "Finfish Farms" = "salmon"
    )
  ) +
  
  theme_minimal() +
  theme(
    legend.position = "bottom",
    axis.text = element_text(size = 8),
    legend.text = element_text(size = 10),
    legend.title = element_text(size = 12),
    panel.grid = element_blank()  # Removes all grid lines
  ) +
  labs(
    title = "Maritime Boundaries and Finfish Farms Around Tasmania",
    x = "Longitude",
    y = "Latitude"
  ) +
  coord_sf(
    xlim = st_bbox(bbox_albers)[c(1,3)],
    ylim = st_bbox(bbox_albers)[c(2,4)]
  ) +
  guides(
    color = guide_legend(order = 2),
    fill = guide_legend(order = 1)
  )

# Create Figures directory if it doesn't exist
if (!dir.exists(here("Figures"))) {
  dir.create(here("Figures"))
}

# Save the plot with new name
ggsave(here("Figures", "Tasmania_Maritime_Boundaries_No_Grid.png"), 
       territories_map, 
       width = 10, 
       height = 8, 
       dpi = 300,
       bg = "white")

plot(territories_map)
```
#size of marine areas
```{r}

# Load required libraries
library(sf)
library(dplyr)
library(here)

# Function to calculate area in km² for any spatial object
calculate_area_km2 <- function(spatial_obj, obj_name = "Unknown") {
  
  # Check if object exists and is spatial
  if (!inherits(spatial_obj, "sf")) {
    stop(paste("Object", obj_name, "is not an sf object"))
  }
  
  # Get the current CRS
  current_crs <- st_crs(spatial_obj)
  cat("CRS for", obj_name, ":", current_crs$input, "\n")
  
  # Since data is already in Australian Albers (equal-area projection),
  # we can calculate areas directly without transformation
  
  # Calculate area in m² and convert to km²
  areas_m2 <- st_area(spatial_obj)
  areas_km2 <- as.numeric(areas_m2) / 1000000  # Convert m² to km²
  
  # Add area column to the spatial object
  spatial_obj$area_km2 <- areas_km2
  
  # Create summary statistics
  total_area <- sum(areas_km2, na.rm = TRUE)
  n_features <- nrow(spatial_obj)
  
  # Print summary
  cat("\n=== AREA SUMMARY FOR", toupper(obj_name), "===\n")
  cat("Number of features:", n_features, "\n")
  cat("Total area:", format(total_area, big.mark = ",", digits = 2), "km²\n")
  cat("Average area per feature:", format(mean(areas_km2, na.rm = TRUE), big.mark = ",", digits = 2), "km²\n")
  cat("Largest feature:", format(max(areas_km2, na.rm = TRUE), big.mark = ",", digits = 2), "km²\n")
  cat("Smallest feature:", format(min(areas_km2, na.rm = TRUE), big.mark = ",", digits = 2), "km²\n")
  cat("==========================================\n\n")
  
  return(spatial_obj)
}

# List of your shapefile objects
shapefile_names <- c("bbox_albers", "terrestrial_areas_crop", "commonwealth_crop", 
                     "state_waters", "high_seas")

# Initialize results list
area_results <- list()

# Calculate areas for each shapefile
for (name in shapefile_names) {
  
  # Check if object exists in environment
  if (exists(name)) {
    
    cat("Processing:", name, "\n")
    
    # Get the spatial object
    spatial_obj <- get(name)
    
    # Calculate areas
    result <- calculate_area_km2(spatial_obj, name)
    
    # Store results
    area_results[[name]] <- result
    
  } else {
    cat("Warning: Object", name, "not found in environment\n")
  }
}

# Create a summary table of total areas
summary_table <- data.frame(
  Shapefile = character(),
  Total_Area_km2 = numeric(),
  Number_of_Features = integer(),
  stringsAsFactors = FALSE
)

for (name in names(area_results)) {
  if (!is.null(area_results[[name]])) {
    total_area <- sum(area_results[[name]]$area_km2, na.rm = TRUE)
    n_features <- nrow(area_results[[name]])
    
    summary_table <- rbind(summary_table, 
                          data.frame(Shapefile = name,
                                   Total_Area_km2 = total_area,
                                   Number_of_Features = n_features))
  }
}

# Display final summary table
cat("=== OVERALL SUMMARY ===\n")
print(summary_table)

# Optional: Save individual results with area calculations using here package
# Create output directory if it doesn't exist
output_dir <- here("output_data")
if (!dir.exists(output_dir)) {
  dir.create(output_dir, recursive = TRUE)
  cat("Created directory:", output_dir, "\n")
}

# save the results
 for (name in names(area_results)) {
   if (!is.null(area_results[[name]])) {
#     Ensure output directory exists before each write
     if (!dir.exists(output_dir)) {
       dir.create(output_dir, recursive = TRUE)
     }
   
  output_name <- here("output_data", paste0("territory_areas_", name, ".shp"))
#     
#     # Try to write with error handling
#     tryCatch({
#       st_write(area_results[[name]], output_name, delete_dsn = TRUE, quiet = TRUE)
#       cat("Successfully saved:", output_name, "\n")
#     }, error = function(e) {
#       cat("Error saving", name, ":", e$message, "\n")
#       cat("Attempting alternative save method...\n")
#       
#       # Alternative: try without delete_dsn
#       tryCatch({
#         if (file.exists(output_name)) file.remove(output_name)
#         st_write(area_results[[name]], output_name, quiet = TRUE)
#         cat("Successfully saved with alternative method:", output_name, "\n")
#       }, error = function(e2) {
#         cat("Failed to save", name, "with both methods\n")
#       })
#     })
#   }
# }

# Function to get detailed area information for a specific shapefile
get_detailed_areas <- function(shapefile_name) {
  if (shapefile_name %in% names(area_results)) {
    obj <- area_results[[shapefile_name]]
    if (!is.null(obj) && "area_km2" %in% names(obj)) {
      
      # Create detailed summary
      areas_df <- data.frame(
        Feature_ID = 1:nrow(obj),
        Area_km2 = obj$area_km2,
        stringsAsFactors = FALSE
      )
      
      # Add any existing ID columns if available
      if ("FID" %in% names(obj)) areas_df$FID <- obj$FID
      if ("ID" %in% names(obj)) areas_df$ID <- obj$ID
      if ("NAME" %in% names(obj)) areas_df$Name <- obj$NAME
      
      return(areas_df)
    }
  }
  return(NULL)
}

# Example usage for detailed areas:
# detailed_areas <- get_detailed_areas("terrestrial_areas_crop")
# print(detailed_areas)
```


```{r}
qtm(terrestrial_areas_crop)
```
```{r}
qtm(state_waters)
```
```{r}
 # Land areas
  st_shape(terrestrial_areas_crop) 
    tm_polygons (col"black") +
  tm_shape(commonwealth_crop)+
         tm_polygons(col = "blue", alpha=0.5)+
  tm_shape( state_waters)+
       tm_polygons(col = "green", alpha=0.2)+
    tm_shape(high_seas)+
      tm_polygons(col="lightblue")
  
```
#high seas map
```{r}
  high_seas_map<- tm_shape(high_seas)+
      tm_polygons(col="#3B528B")+
tm_shape(terrestrial_areas_crop) +
    tm_polygons(col="darkgrey")

  ggsave(here("Figures", "High_seas_map.png"), 
       high_seas_map, 
       width = 10, 
       height = 8, 
       dpi = 300,
       bg = "white")
```
```{r}
# High seas map
high_seas_map <- tm_shape(high_seas) +
  tm_polygons(col= "#A6DBA0", alpha=0.8) +
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "darkgrey")

tmap_save(high_seas_map, 
          filename = here("Figures", "High_seas_map.png"),
          width = 10, 
          height = 8, 
          dpi = 300)
```


#commonwealth map
```{r}
# Commonwealth map
commonwealth_map <- tm_shape(commonwealth_crop) +
  tm_polygons(col = "#21908C", alpha = 0.5) +
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "darkgrey")

tmap_save(commonwealth_map, 
          filename = here("Figures", "commonwealth_map.png"),
          width = 10, 
          height = 8, 
          dpi = 300)
   
```

#state waters map
```{r}
# State waters map
state_waters_map <- tm_shape(state_waters) +
  tm_polygons(col = "#3B528B", alpha=0.7) +
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "darkgrey")

tmap_save(state_waters_map, 
          filename = here("Figures", "state_waters_map.png"),
          width = 10, 
          height = 8, 
          dpi = 300)
```


```{r}
high_seas_map
state_waters_map
commonwealth_map
```


```{r}
marine_zones_map<- 
  tm_shape(commonwealth_crop)+
         tm_polygons(col = "#21908C", alpha=0.5)+
  tm_shape( state_waters)+
       tm_polygons(col = "#3B528B", alpha=0.7)+
    tm_shape(high_seas)+
      tm_polygons(col= "#A6DBA0", alpha=0.8)+
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "darkgrey")
  
    tmap_save(marine_zones_map, 
          filename = here("Figures", "marine_zones_map.png"),
          width = 10, 
          height = 8, 
          dpi = 300)
```

#marine_zones_map_lines
```{r}
marine_zones_map_lines<- 
  tm_shape(commonwealth_crop)+
         tm_borders(col = "#21908C", alpha=0.5)+
  tm_shape( state_waters)+
       tm_borders(col = "#3B528B", alpha=0.7)+
    tm_shape(high_seas)+
      tm_borders(col= "#A6DBA0", alpha=0.8)+
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "darkgrey")
  
    tmap_save(marine_zones_map_lines, 
          filename = here("Figures", "marine_zones_map_lines.png"),
          width = 10, 
          height = 8, 
          dpi = 300)
```

# High seas map line
```{r}
# High seas map line
high_seas_map_line<- tm_shape(high_seas) +
  tm_borders(col= "#A6DBA0", alpha=0.8) +
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "darkgrey")

tmap_save(high_seas_map_line, 
          filename = here("Figures", "High_seas_map_line.png"),
          width = 10, 
          height = 8, 
          dpi = 300)
```


#commonwealth map line
```{r}
# Commonwealth map
commonwealth_map_line <- tm_shape(commonwealth_crop) +
  tm_borders(col = "#21908C", alpha = 0.5) +
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "darkgrey")

tmap_save(commonwealth_map_line, 
          filename = here("Figures", "commonwealth_map_line.png"),
          width = 10, 
          height = 8, 
          dpi = 300)
   
```

#state waters map line
```{r}
# State waters map
state_waters_map_line <- tm_shape(state_waters) +
  tm_borders(col = "#3B528B", alpha=0.7) +
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "darkgrey")

tmap_save(state_waters_map_line, 
          filename = here("Figures", "state_waters_map_line.png"),
          width = 10, 
          height = 8, 
          dpi = 300)
```




```{r}
#view your map
tmap_options(check.and.fix = TRUE)

marine_zones_map_simple <- 
  tm_shape(commonwealth_crop) + tm_polygons(col = "#21908C", alpha = 0.5) +
  tm_shape(state_waters) + tm_polygons(col = "#3B528B", alpha = 0.7) +
  tm_shape(high_seas) + tm_polygons(col = "#A6DBA0", alpha = 0.8) +
  tm_shape(terrestrial_areas_crop) + tm_polygons(col = "darkgrey")

# Switch to interactive mode and click where you want labels
#tmap_mode("view")
marine_zones_map_simple

tmap_mode("plot")

```

#best map with viridis
#best map no grids
```{r}
finfish_farms <- st_read(here("raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp"))%>%
  st_transform("EPSG:3577")%>%
  st_make_valid()
```



```{r}
tmap_options(check.and.fix = TRUE)

# Create the map
territories_map_aqua_viridis <-    tm_shape(high_seas) +
    tm_polygons(col = "#A6DBA0", alpha = 0.6) +
    tm_shape(terrestrial_areas_crop) +
    tm_polygons(col = "grey40", alpha = 0.6) +
    tm_shape(commonwealth_crop) +
    tm_polygons(col = "#21908C", alpha = 0.6) +
    tm_shape(state_waters) +
    tm_polygons(col = "#3B528B", alpha = 0.6) +
     tm_shape(finfish_farms) +
    tm_polygons(col = "#FA8072", border.col = "#FA8072", lwd = 2)+ 

# Save the plot
tmap_save(territories_map_aqua_viridis, 
          filename = here("Figures", "Tasmania_Maritime_Boundaries_aqua_viridis.png"),
          width = 10, 
          height = 8, 
          dpi = 300)

print(territories_map_aqua_viridis)
```

#map with legend_viridis more transparent 
```{r}
tmap_options(check.and.fix = TRUE)

# Create the map with labels for legend
territories_map_aqua_viridis_alpha_legend <- tm_shape(high_seas) +
    tm_polygons(col = "#A6DBA0", alpha = 0.2, title = "High Seas") +
    tm_shape(terrestrial_areas_crop) +
    tm_polygons(col = "grey40", alpha = 0.6, title = "Terrestrial Areas") +
    tm_shape(commonwealth_crop) +
    tm_polygons(col = "#21908C", alpha = 0.2, title = "Commonwealth Waters") +
    tm_shape(state_waters) +
    tm_polygons(col = "#3B528B", alpha = 0.2, title = "State Waters") +
    tm_shape(finfish_farms) +
    tm_polygons(col = "#FA8072", border.col = "#FA8072", lwd = 2, title = "Finfish Farms") +
  tm_add_legend(type = "fill",
                  labels = c("High Seas", "Terrestrial Areas", "Commonwealth Waters", 
                            "State Waters", "Finfish Farms"),
                  col = c("#E8F2E6", "#999999", "#D4E7E5", "#D0D4E0", "#FA8072"),
                  title = "Maritime Boundaries") +
    tm_layout(legend.outside = TRUE,
              legend.outside.position = "bottom",
              legend.outside.size = 0.2,
              legend.title.size = 1.2,
              legend.text.size = 0.8)

# Save the plot
tmap_save(territories_map_aqua_viridis_alpha_legend, 
          filename = here("Figures", "Tasmania_Maritime_Boundaries_aqua_viridis_alpha_legend.png"),
          width = 12,  # Increased width to accommodate legend
          height = 8, 
          dpi = 300)

print(territories_map_aqua_viridis_legend)
```


#INSET MAP
```{r}
# Load required libraries
library(sf)
library(dplyr)
library(here)
library(tmap)
library(grid)
library(png)

# Load your spatial data
# (update these if you've renamed your objects)
# Assume you already created the cropped versions for Tasmania
# high_seas_full, commonwealth_full, state_waters_full, terrestrial_areas_full
# high_seas_crop, commonwealth_crop, state_waters_crop, terrestrial_areas_crop
# finfish_farms
# ─────────────────────────────────────────────
# 1. Load and transform data
# ─────────────────────────────────────────────

# Load shapefiles and transform to EPSG:3577
terrestrial_areas <- st_read(here("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp")) %>%
  st_transform("EPSG:3577") %>%
  st_make_valid()

coastal_waters <- st_read(here("raw_data/Coastal_Waters_areas_(AMB2020)/Coastal_Waters_areas_(AMB2020).shp")) %>%
  st_transform("EPSG:3577") %>%
  st_make_valid()

commonwealth_waters <- st_read(here("raw_data/Commonwealth_Marine_Regions/Commonwealth_Marine_Regions.shp")) %>%
  st_transform("EPSG:3577") %>%
  st_make_valid()

finfish_farms <- st_read(here("raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp"))%>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

australia <- st_read("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp")
marine_regions <- st_read("raw_data/Commonwealth_Marine_Regions.shp")
# ─────────────────────────────────────────────
# 2. Define Tasmania bbox and crop for inset
# ─────────────────────────────────────────────

bbox_albers <- st_bbox(c(xmin = 140.995, xmax = 153.005, ymin = -47.255, ymax = -38.995)) %>%
  st_as_sfc() %>%
  st_set_crs(4326) %>%
  st_transform(3577)

# Crop for inset
terrestrial_areas_crop <- st_intersection(terrestrial_areas, bbox_albers)
coastal_waters_crop <- st_intersection(coastal_waters, bbox_albers)
commonwealth_crop <- st_intersection(commonwealth_waters, bbox_albers)

state_waters_crop <- st_difference(coastal_waters_crop, st_union(terrestrial_areas_crop))

all_managed_crop <- bind_rows(
  st_set_geometry(commonwealth_crop, "geometry") %>% mutate(zone_type = "Commonwealth"),
  st_set_geometry(state_waters_crop, "geometry") %>% mutate(zone_type = "State"),
  st_set_geometry(terrestrial_areas_crop, "geometry") %>% mutate(zone_type = "Terrestrial")
)

high_seas_crop <- st_difference(bbox_albers, st_union(all_managed_crop))

# ─────────────────────────────────────────────
# 3. Prepare full Australia data for main map
# ─────────────────────────────────────────────

terrestrial_areas_full <- terrestrial_areas
coastal_waters_full <- coastal_waters
commonwealth_full <- commonwealth_waters

state_waters_full <- st_difference(coastal_waters_full, st_union(terrestrial_areas_full))

all_managed_full <- bind_rows(
  st_set_geometry(commonwealth_full, "geometry") %>% mutate(zone_type = "Commonwealth"),
  st_set_geometry(state_waters_full, "geometry") %>% mutate(zone_type = "State"),
  st_set_geometry(terrestrial_areas_full, "geometry") %>% mutate(zone_type = "Terrestrial")
)

high_seas_full <- st_difference(st_as_sfc(st_bbox(terrestrial_areas_full)), st_union(all_managed_full))

# 1. Create a bounding box around Tasmania
tas_bbox <- st_bbox(terrestrial_areas_crop) %>%
  st_as_sfc() %>%
  st_sf()

# 2. Add bounding box to main map using colorblind-friendly color
highlight_color <- "#FDE725FF"  # bright yellow-green from viridis


# === 1. MAIN MAP OF AUSTRALIA ===
# 3. Updated MAIN MAP with Tasmania highlight
main_map <- tm_shape(high_seas_full) +
  tm_polygons(col = "#A6DBA0", alpha = 0.6, title = "High Seas") +
  tm_shape(terrestrial_areas_full) +
  tm_polygons(col = "grey40", alpha = 0.6, title = "Land") +
  tm_shape(commonwealth_full) +
  tm_polygons(col = "#21908C", alpha = 0.6, title = "Commonwealth Waters") +
  tm_shape(state_waters_full) +
  tm_polygons(col = "#3B528B", alpha = 0.6, title = "State Waters") +
  tm_shape(finfish_farms) +
  tm_polygons(col = "#FA8072", border.col = "#FA8072", lwd = 2, title = "Finfish Farms") +
  tm_shape(tas_bbox) +  # the new bounding box layer
  tm_borders(col = highlight_color, lwd = 1, lty = "solid") +  # visible frame
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "bottom",
            legend.outside.size = 0.2,
            legend.title.size = 1.2,
            legend.text.size = 0.8)


# === 2. INSET MAP OF TASMANIA ===
inset_map <- tm_shape(high_seas_crop) +
  tm_polygons(col = "#A6DBA0", alpha = 0.6) +
  tm_shape(commonwealth_crop) +
  tm_polygons(col = "#21908C", alpha = 0.6) +
  tm_shape(state_waters_crop) +
  tm_polygons(col = "#3B528B", alpha = 0.6) +
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "grey40", alpha = 0.6) +
  tm_shape(finfish_farms) +
  tm_polygons(col = "#FA8072", border.col = "#FA8072", lwd = 2) +
  tm_layout(frame = TRUE, 
            bg.color = "white", 
            legend.show = FALSE, 
            title = "Tasmania", 
            title.size = 1)

# === 3. EXPORT BOTH MAPS AS IMAGES ===
# Save as temporary images
main_file <- here("Figures", "Australia_map_temp.png")
inset_file <- here("Figures", "Tasmania_inset_temp.png")

# Create Figures folder if it doesn't exist
if (!dir.exists(here("Figures"))) dir.create(here("Figures"))

# Save maps to PNG
tmap_save(main_map, filename = main_file, width = 12, height = 8, dpi = 300)
tmap_save(inset_map, filename = inset_file, width = 4, height = 3, dpi = 300)

# === 4. COMBINE WITH GRID ===
# Read the PNGs
main_img <- readPNG(main_file)
inset_img <- readPNG(inset_file)

# Plot in RStudio or export
grid.newpage()
grid.raster(main_img)
vp <- viewport(x = 0.8, y = 0.25, width = 0.35, height = 0.35, just = c("left", "bottom"))
pushViewport(vp)
grid.raster(inset_img)
popViewport()

# === 5. OPTIONAL: EXPORT FINAL COMPOSITE MAP ===
# Save the composite map to file
png(filename = here("Figures", "Australia_with_Tasmania_inset.png"),
    width = 12, height = 8, units = "in", res = 300)
grid.newpage()
grid.raster(main_img)
pushViewport(viewport(x = 0.8, y = 0.25, width = 0.35, height = 0.35, just = c("left", "bottom")))
grid.raster(inset_img)
popViewport()
dev.off()
```


#IMPROVED INSET MAP
```{r}
# Load required libraries
library(sf)
library(dplyr)
library(here)
library(tmap)
library(grid)
library(png)

# ─────────────────────────────────────────────
# 1. Load and transform data
# ─────────────────────────────────────────────

# Load shapefiles and transform to EPSG:3577
terrestrial_areas <- st_read(here("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp")) %>%
  st_transform("EPSG:3577") %>%
  st_make_valid()

coastal_waters <- st_read(here("raw_data/Coastal_Waters_areas_(AMB2020)/Coastal_Waters_areas_(AMB2020).shp")) %>%
  st_transform("EPSG:3577") %>%
  st_make_valid()

commonwealth_waters <- st_read(here("raw_data/Commonwealth_Marine_Regions/Commonwealth_Marine_Regions.shp")) %>%
  st_transform("EPSG:3577") %>%
  st_make_valid()

finfish_farms <- st_read(here("raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp"))%>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

# ─────────────────────────────────────────────
# 2. Create tighter bounding box for main map to reduce whitespace
# ─────────────────────────────────────────────

# Create a tighter bounding box around Australia + reasonable marine area
australia_bbox <- st_bbox(terrestrial_areas)
# Expand by reasonable margins (in meters for EPSG:3577)
expanded_bbox <- st_bbox(c(
  xmin = australia_bbox["xmin"] - 50000,  # 50km west
  xmax = australia_bbox["xmax"] + 200000,  # 200km east  
  ymin = australia_bbox["ymin"] - 800000,  # 800km south
  ymax = australia_bbox["ymax"] + 200000   # 200km north
)) %>%
  st_as_sfc() %>%
  st_set_crs(3577)

# ─────────────────────────────────────────────
# 3. Define Tasmania bbox and crop for inset
# ─────────────────────────────────────────────

# Tasmania bounding box in WGS84, then transform
bbox_albers <- st_bbox(c(xmin = 140.995, xmax = 153.005, ymin = -47.255, ymax = -38.995)) %>%
  st_as_sfc() %>%
  st_set_crs(4326) %>%
  st_transform(3577)

# Crop data for inset
terrestrial_areas_crop <- st_intersection(terrestrial_areas, bbox_albers)
coastal_waters_crop <- st_intersection(coastal_waters, bbox_albers)
commonwealth_crop <- st_intersection(commonwealth_waters, bbox_albers)

state_waters_crop <- st_difference(coastal_waters_crop, st_union(terrestrial_areas_crop))

all_managed_crop <- bind_rows(
  st_set_geometry(commonwealth_crop, "geometry") %>% mutate(zone_type = "Commonwealth"),
  st_set_geometry(state_waters_crop, "geometry") %>% mutate(zone_type = "State"),
  st_set_geometry(terrestrial_areas_crop, "geometry") %>% mutate(zone_type = "Terrestrial")
)

high_seas_crop <- st_difference(bbox_albers, st_union(all_managed_crop))

# ─────────────────────────────────────────────
# 4. Prepare cropped Australia data for main map (to reduce whitespace)
# ─────────────────────────────────────────────

terrestrial_areas_full <- st_intersection(terrestrial_areas, expanded_bbox)
coastal_waters_full <- st_intersection(coastal_waters, expanded_bbox)
commonwealth_full <- st_intersection(commonwealth_waters, expanded_bbox)

state_waters_full <- st_difference(coastal_waters_full, st_union(terrestrial_areas_full))

all_managed_full <- bind_rows(
  st_set_geometry(commonwealth_full, "geometry") %>% mutate(zone_type = "Commonwealth"),
  st_set_geometry(state_waters_full, "geometry") %>% mutate(zone_type = "State"),
  st_set_geometry(terrestrial_areas_full, "geometry") %>% mutate(zone_type = "Terrestrial")
)

high_seas_full <- st_difference(expanded_bbox, st_union(all_managed_full))

# Create Tasmania highlight box for main map
tas_bbox <- bbox_albers %>%
  st_sf()

highlight_color <- "#26619C"  # bright yellow-green

# ─────────────────────────────────────────────
# 5. Create maps with improved layout
# ─────────────────────────────────────────────

# MAIN MAP with tighter bounds
main_map <- tm_shape(high_seas_full) +
  tm_polygons(col = "#A6DBA0", alpha = 0.2, title = "High Seas") +
  tm_shape(terrestrial_areas_full) +
  tm_polygons(col = "grey40", alpha = 0.6, title = "Land") +
  tm_shape(commonwealth_full) +
  tm_polygons(col = "#21908C", alpha = 0.2, title = "Commonwealth Waters") +
  tm_shape(state_waters_full) +
  tm_polygons(col = "#3B528B", alpha = 0.2, title = "State Waters") +
  tm_shape(finfish_farms) +
  tm_polygons(col = "#FA8072", border.col = "#FA8072", lwd = 2, title = "Finfish Farms") +
  tm_shape(tas_bbox) +
  tm_borders(col = highlight_color, lwd = 1, lty = "solid") +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "bottom",
            legend.outside.size = 0.15,
            legend.title.size = 1.0,
            legend.text.size = 0.7,
            frame = FALSE)

# INSET MAP with proper frame
inset_map <- tm_shape(high_seas_crop) +
  tm_polygons(col = "#A6DBA0", alpha = 0.2) +
  tm_shape(commonwealth_crop) +
  tm_polygons(col = "#21908C", alpha = 0.2) +
  tm_shape(state_waters_crop) +
  tm_polygons(col = "#3B528B", alpha = 0.2) +
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "grey40", alpha = 0.6) +
  tm_shape(finfish_farms) +
  tm_polygons(col = "#FA8072", border.col = "#FA8072", lwd = 2) +
  tm_layout(frame = TRUE, 
            frame.lwd = 2,
            bg.color = "white", 
            legend.show = FALSE, 
            title = "Tasmania", 
            title.size = 1.2,
            title.position = c("center", "top"))

# ─────────────────────────────────────────────
# 6. Export maps and create composite with better positioning
# ─────────────────────────────────────────────

# Create output directory
if (!dir.exists(here("Figures"))) dir.create(here("Figures"))

# Save as temporary images
main_file <- here("Figures", "Australia_map_temp_improved.png")
inset_file <- here("Figures", "Tasmania_inset_temp_improved.png")

# Save maps to PNG with better dimensions
tmap_save(main_map, filename = main_file, width = 14, height = 9, dpi = 300)
tmap_save(inset_map, filename = inset_file, width = 5, height = 4, dpi = 300)

# Read the PNGs
main_img <- readPNG(main_file)
inset_img <- readPNG(inset_file)

# ─────────────────────────────────────────────
# 7. Create composite with better inset positioning
# ─────────────────────────────────────────────

# Save the improved composite map
png(filename = here("Figures", "Australia_with_Tasmania_inset_improved.png"),
    width = 14, height = 9, units = "in", res = 300)

# Plot main map
grid.newpage()
grid.raster(main_img)

# Position inset in bottom-left area (away from Tasmania location on main map)
# Using more conservative positioning to ensure it stays within bounds
pushViewport(viewport(x = 0.15, y = 0.15, width = 0.3, height = 0.3, 
                     just = c("center", "center")))
grid.raster(inset_img)
grid.rect(gp = gpar(col = highlight_color, fill = NA, lwd = 3))  # Add border
popViewport()

dev.off()

# Also display in RStudio
grid.newpage()
grid.raster(main_img)
pushViewport(viewport(x = 0.15, y = 0.15, width = 0.3, height = 0.3, 
                     just = c("center", "center")))
grid.raster(inset_img)
grid.rect(gp = gpar(col = highlight_color, fill = NA, lwd = 3))
popViewport()

# Print completion message
cat("Improved map saved as: Australia_with_Tasmania_inset_improved.png\n")

```
#INSET MAP New try

```{r}
# Load required libraries
library(sf)
library(dplyr)
library(here)
library(tmap)
library(grid)
library(png)

# ─────────────────────────────────────────────
# 1. Load and transform data
# ─────────────────────────────────────────────

# Load shapefiles and transform to EPSG:3577
terrestrial_areas <- st_read(here("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp")) %>%
  st_transform("EPSG:3577") %>%
  st_make_valid()

coastal_waters <- st_read(here("raw_data/Coastal_Waters_areas_(AMB2020)/Coastal_Waters_areas_(AMB2020).shp")) %>%
  st_transform("EPSG:3577") %>%
  st_make_valid()

commonwealth_waters <- st_read(here("raw_data/Commonwealth_Marine_Regions/Commonwealth_Marine_Regions.shp")) %>%
  st_transform("EPSG:3577") %>%
  st_make_valid()

finfish_farms <- st_read(here("raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp"))%>%
  st_transform("EPSG:3577")%>%
  st_make_valid()

# ─────────────────────────────────────────────
# 2. Create tighter bounding box for main map to reduce whitespace
# ─────────────────────────────────────────────

# Create a tighter bounding box around Australia + marine area
# First get the extent of commonwealth waters to determine western boundary
commonwealth_bbox <- st_bbox(commonwealth_waters)
australia_bbox <- st_bbox(terrestrial_areas)

# Use commonwealth waters western boundary + small margin, but reasonable margins elsewhere
expanded_bbox <- st_bbox(c(
  xmin = commonwealth_bbox["xmin"] - 50000,   # Just 50km west of commonwealth waters
  xmax = australia_bbox["xmax"] + 200000,     # 200km east of land
  ymin = australia_bbox["ymin"] - 800000,     # 800km south of land
  ymax = australia_bbox["ymax"] + 200000      # 200km north of land
)) %>%
  st_as_sfc() %>%
  st_set_crs(3577)

# ─────────────────────────────────────────────
# 3. Define Tasmania bbox and crop for inset
# ─────────────────────────────────────────────

# Tasmania bounding box in WGS84, then transform
bbox_albers <- st_bbox(c(xmin = 140.995, xmax = 153.005, ymin = -47.255, ymax = -38.995)) %>%
  st_as_sfc() %>%
  st_set_crs(4326) %>%
  st_transform(3577)

# Crop data for inset
terrestrial_areas_crop <- st_intersection(terrestrial_areas, bbox_albers)
coastal_waters_crop <- st_intersection(coastal_waters, bbox_albers)
commonwealth_crop <- st_intersection(commonwealth_waters, bbox_albers)

state_waters_crop <- st_difference(coastal_waters_crop, st_union(terrestrial_areas_crop))

all_managed_crop <- bind_rows(
  st_set_geometry(commonwealth_crop, "geometry") %>% mutate(zone_type = "Commonwealth"),
  st_set_geometry(state_waters_crop, "geometry") %>% mutate(zone_type = "State"),
  st_set_geometry(terrestrial_areas_crop, "geometry") %>% mutate(zone_type = "Terrestrial")
)

high_seas_crop <- st_difference(bbox_albers, st_union(all_managed_crop))

# ─────────────────────────────────────────────
# 4. Prepare cropped Australia data for main map (to reduce whitespace)
# ─────────────────────────────────────────────

terrestrial_areas_full <- st_intersection(terrestrial_areas, expanded_bbox)
coastal_waters_full <- st_intersection(coastal_waters, expanded_bbox)
commonwealth_full <- st_intersection(commonwealth_waters, expanded_bbox)

state_waters_full <- st_difference(coastal_waters_full, st_union(terrestrial_areas_full))

all_managed_full <- bind_rows(
  st_set_geometry(commonwealth_full, "geometry") %>% mutate(zone_type = "Commonwealth"),
  st_set_geometry(state_waters_full, "geometry") %>% mutate(zone_type = "State"),
  st_set_geometry(terrestrial_areas_full, "geometry") %>% mutate(zone_type = "Terrestrial")
)

high_seas_full <- st_difference(expanded_bbox, st_union(all_managed_full))

# Create Tasmania highlight box for main map using the oceanic bounding box
tas_bbox <- bbox_albers %>%
  st_sf()

highlight_color <- "#FDE725FF"  # bright yellow-green

# ─────────────────────────────────────────────
# 5. Create maps with improved layout
# ─────────────────────────────────────────────

# MAIN MAP with tighter bounds
main_map <- tm_shape(high_seas_full) +
  tm_polygons(col = "#A6DBA0", alpha = 0.2, title = "High Seas") +
  tm_shape(terrestrial_areas_full) +
  tm_polygons(col = "grey40", alpha = 0.6, title = "Land") +
  tm_shape(commonwealth_full) +
  tm_polygons(col = "#21908C", alpha = 0.2, title = "Commonwealth Waters") +
  tm_shape(state_waters_full) +
  tm_polygons(col = "#3B528B", alpha = 0.2, title = "State Waters") +
  tm_shape(finfish_farms) +
  tm_polygons(col = "#FA8072", border.col = "#FA8072", lwd = 2, title = "Finfish Farms") +
  tm_shape(tas_bbox) +
  tm_borders(col = highlight_color, lwd = 4, lty = "solid") +
  tm_layout(legend.outside = TRUE,
            legend.outside.position = "bottom",
            legend.outside.size = 0.15,
            legend.title.size = 1.0,
            legend.text.size = 0.7,
            frame = FALSE)

# INSET MAP with proper coordinate handling to prevent tilting
inset_map <- tm_shape(high_seas_crop) +
  tm_polygons(col = "#A6DBA0", alpha = 0.2) +
  tm_shape(commonwealth_crop) +
  tm_polygons(col = "#21908C", alpha = 0.2) +
  tm_shape(state_waters_crop) +
  tm_polygons(col = "#3B528B", alpha = 0.2) +
  tm_shape(terrestrial_areas_crop) +
  tm_polygons(col = "grey40", alpha = 0.6) +
  tm_shape(finfish_farms) +
  tm_polygons(col = "#FA8072", border.col = "#FA8072", lwd = 2) +
  tm_layout(frame = FALSE,           # Remove frame
            bg.color = "white", 
            legend.show = FALSE, 
            title = "Tasmania", 
            title.size = 1.2,
            title.position = c("center", "top"),
            inner.margins = c(0, 0, 0, 0),  # Remove inner margins
            outer.margins = c(0, 0, 0, 0))  # Remove outer margins

# ─────────────────────────────────────────────
# 6. Export maps and create composite with better positioning
# ─────────────────────────────────────────────

# Create output directory
if (!dir.exists(here("Figures"))) dir.create(here("Figures"))

# Save as temporary images
main_file <- here("Figures", "Australia_map_temp_improved.png")
inset_file <- here("Figures", "Tasmania_inset_temp_improved.png")

# Save maps to PNG with better dimensions and no borders
tmap_save(main_map, filename = main_file, width = 14, height = 9, dpi = 300)
tmap_save(inset_map, filename = inset_file, width = 5, height = 4, dpi = 300)

# Read the PNGs
main_img <- readPNG(main_file)
inset_img <- readPNG(inset_file)

# ─────────────────────────────────────────────
# 7. Create composite with better inset positioning
# ─────────────────────────────────────────────

# Save the improved composite map
png(filename = here("Figures", "Australia_with_Tasmania_inset_improved.png"),
    width = 14, height = 9, units = "in", res = 300)

# Plot main map
grid.newpage()
grid.raster(main_img)

# Position inset on the right side (away from Tasmania location on main map)
# Using positioning that keeps it within bounds but on the right
pushViewport(viewport(x = 0.75, y = 0.2, width = 0.25, height = 0.25, 
                     just = c("center", "center")))
grid.raster(inset_img)
grid.rect(gp = gpar(col = highlight_color, fill = NA, lwd = 3))  # Add border around inset
popViewport()

dev.off()

# Also display in RStudio
grid.newpage()
grid.raster(main_img)
pushViewport(viewport(x = 0.75, y = 0.2, width = 0.25, height = 0.25, 
                     just = c("center", "center")))
grid.raster(inset_img)
grid.rect(gp = gpar(col = highlight_color, fill = NA, lwd = 3))
popViewport()

# Print completion message
cat("Improved map saved as: Australia_with_Tasmania_inset_improved.png\n")

```




#INSET MAP GGPLOT
```{r}
# TASMANIA STUDY AREA MAP - GGPLOT2 VERSION
```{r}
# Load required libraries
library(sf)
library(dplyr)
library(here)
library(ggplot2)

cat("=== GGPLOT2 TASMANIA STUDY AREA MAP ===\n")

# ─────────────────────────────────────────────
# 1. Load and clean data (same as before)
# ─────────────────────────────────────────────

cat("Loading data...\n")
terrestrial_areas <- st_read(here("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp")) %>%
  st_transform(3577) %>%
  st_make_valid() %>%
  filter(!st_is_empty(.))

coastal_waters <- st_read(here("raw_data/Coastal_Waters_areas_(AMB2020)/Coastal_Waters_areas_(AMB2020).shp")) %>%
  st_transform(3577) %>%
  st_make_valid()

commonwealth_waters <- st_read(here("raw_data/Commonwealth_Marine_Regions/Commonwealth_Marine_Regions.shp")) %>%
  st_transform(3577) %>%
  st_make_valid()

finfish_farms <- st_read(here("raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp")) %>%
  st_transform(3577) %>%
  st_make_valid()

# ─────────────────────────────────────────────
# 2. Create Tasmania study area and map extent
# ─────────────────────────────────────────────

cat("Creating Tasmania study area...\n")
tas_study_box <- st_bbox(c(
  xmin = 140.995, xmax = 153.005, 
  ymin = -47.255, ymax = -38.995
)) %>%
  st_as_sfc() %>%
  st_set_crs(4326) %>%
  st_transform(3577) %>%
  st_sf()

# Create map extent
tas_bounds <- st_bbox(tas_study_box)
aus_bounds <- st_bbox(terrestrial_areas)

map_extent <- st_bbox(c(
  xmin = min(tas_bounds["xmin"], aus_bounds["xmin"]) - 500000,
  xmax = max(tas_bounds["xmax"], aus_bounds["xmax"]) + 500000,
  ymin = min(tas_bounds["ymin"], aus_bounds["ymin"]) - 300000,
  ymax = max(tas_bounds["ymax"], aus_bounds["ymax"]) + 500000
)) %>%
  st_as_sfc() %>%
  st_set_crs(3577)

# ─────────────────────────────────────────────
# 3. Process spatial data (same as before)
# ─────────────────────────────────────────────

cat("Processing spatial data...\n")
terrestrial_full <- tryCatch(
  st_intersection(terrestrial_areas, map_extent),
  error = function(e) terrestrial_areas
)

coastal_full <- tryCatch(
  st_intersection(coastal_waters, map_extent),
  error = function(e) coastal_waters
)

commonwealth_full <- tryCatch(
  st_intersection(commonwealth_waters, map_extent),
  error = function(e) commonwealth_waters
)

state_waters_full <- tryCatch(
  st_difference(coastal_full, st_union(terrestrial_full)),
  error = function(e) coastal_full
)

high_seas_full <- tryCatch(
  st_difference(map_extent, st_union(c(terrestrial_full, coastal_full, commonwealth_full))),
  error = function(e) {
    st_difference(map_extent, st_union(terrestrial_full))
  }
)

# ─────────────────────────────────────────────
# 4. Create ggplot2 map with proper legend
# ─────────────────────────────────────────────

cat("Creating ggplot2 map...\n")

# Define colors
colors <- c(
  "High Seas" = "#A6DBA0",
  "Land" = "grey40", 
  "Commonwealth Waters" = "#21908C",
  "State Waters" = "#3B528B",
  "Finfish Farms" = "#FA8072",
  "Tasmania Study Area" = "#0F52BA"
)

# Create the map
ggplot_map <- ggplot() +
  # High seas
  geom_sf(data = high_seas_full, 
          aes(fill = "High Seas"), 
          alpha = 0.2, color = NA) +
  # Land
  geom_sf(data = terrestrial_full, 
          aes(fill = "Land"), 
          alpha = 0.6, color = "grey40", size = 0.1) +
  # Commonwealth waters
  geom_sf(data = commonwealth_full, 
          aes(fill = "Commonwealth Waters"), 
          alpha = 0.2, color = NA) +
  # State waters
  geom_sf(data = state_waters_full, 
          aes(fill = "State Waters"), 
          alpha = 0.3, color = NA) +
  # Finfish farms
  geom_sf(data = finfish_farms, 
          aes(fill = "Finfish Farms"), 
          alpha = 1.0, color = "#FA8072", size = 2) +
  # Tasmania study area box
  geom_sf(data = tas_study_box, 
          aes(color = "Tasmania Study Area"), 
          fill = "transparent", size = 4) +
  # Colors and legend
  scale_fill_manual(
    name = "Map Legend",
    values = colors,
    guide = guide_legend(override.aes = list(alpha = c(0.2, 1.0, 0.2, 0.6, 0.3)))
  ) +
  scale_color_manual(
    name = "",
    values = colors,
    guide = guide_legend(override.aes = list(fill = "transparent", alpha = 1))
  ) +
  # Theme and layout
  theme_void() +
  theme(
    legend.position = c(0.02, 0.02),
    legend.justification = c(0, 0),
    legend.background = element_rect(fill = "white", color = "black", size = 0.5),
    legend.margin = margin(5, 5, 5, 5),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 10),
    plot.margin = margin(5, 5, 5, 5)
  ) +
  # Set coordinate limits
  coord_sf(expand = FALSE)

# ─────────────────────────────────────────────
# 5. Save the map
# ─────────────────────────────────────────────

cat("Saving ggplot2 map...\n")
if (!dir.exists(here("Figures"))) dir.create(here("Figures"))

output_file <- here("Figures", "Tasmania_Study_Area_ggplot2_5aug.png")

ggsave(
  filename = output_file,
  plot = ggplot_map,
  width = 16, height = 10, 
  dpi = 300, units = "in",
  bg = "white"
)

cat("ggplot2 map saved successfully:", output_file, "\n")

# Display the map
print(ggplot_map)
```


```{r}
# COMPLETE FIXED TASMANIA MAP CODE AUG 5
```{r}
# Load required libraries
library(sf)
library(dplyr)
library(here)
library(ggplot2)
library(cowplot)
# ─────────────────────────────────────────────
# 1. Load and clean data (same as before)
# ─────────────────────────────────────────────

cat("Loading data...\n")
terrestrial_areas <- st_read(here("raw_data/AustralianStates_SHP/STE_2021_AUST_GDA2020.shp")) %>%
  st_transform(3577) %>%
  st_make_valid() %>%
  filter(!st_is_empty(.))

coastal_waters <- st_read(here("raw_data/Coastal_Waters_areas_(AMB2020)/Coastal_Waters_areas_(AMB2020).shp")) %>%
  st_transform(3577) %>%
  st_make_valid()

commonwealth_waters <- st_read(here("raw_data/Commonwealth_Marine_Regions/Commonwealth_Marine_Regions.shp")) %>%
  st_transform(3577) %>%
  st_make_valid()

finfish_farms <- st_read(here("raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp")) %>%
  st_transform(3577) %>%
  st_make_valid()

# ─────────────────────────────────────────────
# 2. Create Tasmania study area and map extent
# ─────────────────────────────────────────────

cat("Creating Tasmania study area...\n")
tas_study_box <- st_bbox(c(
  xmin = 140.995, xmax = 153.005, 
  ymin = -47.255, ymax = -38.995
)) %>%
  st_as_sfc() %>%
  st_set_crs(4326) %>%
  st_transform(3577) %>%
  st_sf()

# Create map extent
tas_bounds <- st_bbox(tas_study_box)
aus_bounds <- st_bbox(terrestrial_areas)

map_extent <- st_bbox(c(
  xmin = min(tas_bounds["xmin"], aus_bounds["xmin"]) - 500000,
  xmax = max(tas_bounds["xmax"], aus_bounds["xmax"]) + 500000,
  ymin = min(tas_bounds["ymin"], aus_bounds["ymin"]) - 300000,
  ymax = max(tas_bounds["ymax"], aus_bounds["ymax"]) + 500000
)) %>%
  st_as_sfc() %>%
  st_set_crs(3577)

# ─────────────────────────────────────────────
# 3. Process spatial data (same as before)
# ─────────────────────────────────────────────

cat("Processing spatial data...\n")
terrestrial_full <- tryCatch(
  st_intersection(terrestrial_areas, map_extent),
  error = function(e) terrestrial_areas
)

coastal_full <- tryCatch(
  st_intersection(coastal_waters, map_extent),
  error = function(e) coastal_waters
)

commonwealth_full <- tryCatch(
  st_intersection(commonwealth_waters, map_extent),
  error = function(e) commonwealth_waters
)

state_waters_full <- tryCatch(
  st_difference(coastal_full, st_union(terrestrial_full)),
  error = function(e) coastal_full
)

high_seas_full <- tryCatch(
  st_difference(map_extent, st_union(c(terrestrial_full, coastal_full, commonwealth_full))),
  error = function(e) {
    st_difference(map_extent, st_union(terrestrial_full))
  }
)
```

#MAP CREATION
```{r}
cat("Creating Tasmania maps with prominent finfish farms...\n")

# ─────────────────────────────────────────────
# 1. Define colors and create Tasmania variables
# ─────────────────────────────────────────────

colors <- c(
  "High Seas" = "#CCEBC5",
  "Land" = "#636363", 
  "Commonwealth Waters" = "#80B1D3",
  "State Waters" = "#377EB8",
  "Finfish Farms" = "#E41A1C"
)

# Create Tasmania study area bounding box
tas_study_box <- st_bbox(c(
  xmin = 140.995, xmax = 153.005, 
  ymin = -47.255, ymax = -38.995
)) %>%
  st_as_sfc() %>%
  st_set_crs(4326) %>%
  st_transform(3577) %>%
  st_sf()

# Define Tasmania extent variables for inset
tas_bbox <- st_bbox(tas_study_box)
tas_buffer <- 50000  # 50km buffer around Tasmania study area

# ─────────────────────────────────────────────
# 2. Create Tasmania inset map (clean, no borders/title/legend)
# ─────────────────────────────────────────────

inset_map <- ggplot() +
  geom_sf(data = high_seas_tas, fill = "#CCEBC5", alpha = 0.2, color = NA) +
  geom_sf(data = commonwealth_tas, fill = "#80B1D3", alpha = 0.3, color = NA) +
  geom_sf(data = state_waters_tas, fill = "#377EB8", alpha = 0.3, color = NA) +
  geom_sf(data = terrestrial_tas, fill = "#636363", alpha = 0.6, color = "#636363", size = 0.1) +
  geom_sf(data = finfish_farms, fill = "#E41A1C", alpha = 1.0, color = "#E41A1C", size = 3) +
  geom_sf(data = tas_study_box, fill = "transparent", color = "#0F52BA", size = 4) +
  theme_void() +
  theme(
    panel.background = element_blank(),  # No background
    plot.background = element_blank(),   # No background
    plot.margin = margin(0, 0, 0, 0),    # No margins
    legend.position = "none"             # No legend
  ) +
  coord_sf(
    expand = FALSE,
    xlim = c(tas_bbox["xmin"] - tas_buffer, tas_bbox["xmax"] + tas_buffer),
    ylim = c(tas_bbox["ymin"] - tas_buffer, tas_bbox["ymax"] + tas_buffer)
  )

# ─────────────────────────────────────────────
# 3. Create the main map
# ─────────────────────────────────────────────

main_map <- ggplot() +
  geom_sf(data = high_seas_full, aes(fill = "High Seas"), alpha = 0.2, color = NA) +
  geom_sf(data = terrestrial_full, aes(fill = "Land"), alpha = 0.6, color = "#636363", size = 0.1) +
  geom_sf(data = commonwealth_full, aes(fill = "Commonwealth Waters"), alpha = 0.3, color = NA) +
  geom_sf(data = state_waters_full, aes(fill = "State Waters"), alpha = 0.3, color = NA) +
  geom_sf(data = finfish_farms, aes(fill = "Finfish Farms"), alpha = 1.0, color = "#E41A1C", size = 2) +
  geom_sf(data = tas_study_box, aes(color = "Tasmania Study Area"), fill = "transparent", size = 3) +
  scale_fill_manual(
    name = "Map Legend",
    values = colors,
    guide = guide_legend(
      override.aes = list(alpha = c(0.2, 0.6, 0.3, 0.3, 1.0), color = "black", size = 1.5)
    )
  ) +
  scale_color_manual(
    name = "",
    values = c("Tasmania Study Area" = "#0F52BA"),
    guide = guide_legend(
      override.aes = list(fill = NA, color = "#0F52BA", size = 3, linetype = "solid")
    )
  ) +
  theme_void() +
  theme(
    legend.position = c(0.25, 0.50),     # adjust
    legend.justification = c(1, 0),      # Anchor position
    legend.background = element_rect(fill = "white", color = "black", size = 0.5),
    legend.margin = margin(5, 5, 5, 5),
    legend.title = element_text(size = 10, face = "bold"),
    legend.text = element_text(size = 7),
    plot.margin = margin(5, 5, 5, 5)
  ) +
  coord_sf(expand = FALSE)

# ─────────────────────────────────────────────
# 4. Function to combine main and inset maps
# ─────────────────────────────────────────────

create_combined_map <- function() {
  ggdraw() +
    draw_plot(main_map) +
    draw_plot(inset_map, x = 0.01, y = 0.02, width = 0.4, height = 0.45)  # Far west and bottom
}

# ─────────────────────────────────────────────
# 5. Save maps
# ─────────────────────────────────────────────

if (!dir.exists(here("Figures"))) dir.create(here("Figures"))

# Save main map
cat("Saving main map...\n")
ggsave(
  filename = here("Figures", "Main_Map_Updated_5aug.png"),
  plot = main_map,
  width = 16,
  height = 10,
  dpi = 300,
  bg = "white"
)

# Save inset map
cat("Saving inset map...\n")
ggsave(
  filename = here("Figures", "Inset_Map_Updated_5aug.png"),
  plot = inset_map,
  width = 8,
  height = 6,
  dpi = 300,
  bg = "white"
)

# Save combined map
cat("Saving combined map...\n")
combined_plot <- create_combined_map()
ggsave(
  filename = here("Figures", "Tasmania_Study_Area_with_Inset_Updated_5aug.png"),
  plot = combined_plot,
  width = 16,
  height = 10,
  dpi = 300,
  bg = "white"
)

cat("All maps saved successfully!\n")

# Display the maps
print("Main map:")
print(main_map)
print("Combined map with inset:")
print(combined_plot)

```
#FLIPPED APPROACH
```{r}
# TASMANIA MAIN MAP WITH AUSTRALIA INSET (Following DataWim Approach)
```{r}
# Load required libraries
library(sf)
library(dplyr)
library(here)
library(ggplot2)
library(cowplot)

cat("Creating Tasmania-focused map with Australia inset...\n")

# ─────────────────────────────────────────────
# 1. Define colors and create Tasmania variables
# ─────────────────────────────────────────────

colors <- c(
  "high seas" = "#CCEBC5",
  "Land" = "#636363", 
  "Commonwealth waters" = "#80B1D3",
  "state waters" = "#2E7D32",
  "Finfish farms" = "#E41A1C"
)

# Create Tasmania study area bounding box
tas_study_box <- st_bbox(c(
  xmin = 140.995, xmax = 153.005, 
  ymin = -47.255, ymax = -38.995
)) %>%
  st_as_sfc() %>%
  st_set_crs(4326) %>%
  st_transform(3577) %>%
  st_sf()

# Define Tasmania extent variables
tas_bbox <- st_bbox(tas_study_box)
tas_buffer <- 50000  # 50km buffer around Tasmania study area

# ─────────────────────────────────────────────
# 2. Create Tasmania extent for cropping data
# ─────────────────────────────────────────────

tas_extent <- st_polygon(list(cbind(
  c(tas_bbox["xmin"] - tas_buffer, tas_bbox["xmax"] + tas_buffer, 
    tas_bbox["xmax"] + tas_buffer, tas_bbox["xmin"] - tas_buffer, 
    tas_bbox["xmin"] - tas_buffer),
  c(tas_bbox["ymin"] - tas_buffer, tas_bbox["ymin"] - tas_buffer, 
    tas_bbox["ymax"] + tas_buffer, tas_bbox["ymax"] + tas_buffer, 
    tas_bbox["ymin"] - tas_buffer)
))) %>%
  st_sfc(crs = 3577) %>%
  st_sf()

# Crop data to Tasmania region
terrestrial_tas <- tryCatch(
  st_intersection(terrestrial_full, tas_extent),
  error = function(e) st_crop(terrestrial_full, tas_bbox)
)

commonwealth_tas <- tryCatch(
  st_intersection(commonwealth_full, tas_extent),
  error = function(e) st_crop(commonwealth_full, tas_bbox)
)

state_waters_tas <- tryCatch(
  st_intersection(state_waters_full, tas_extent),
  error = function(e) st_crop(state_waters_full, tas_bbox)
)

high_seas_tas <- tryCatch(
  st_intersection(high_seas_full, tas_extent),
  error = function(e) st_crop(high_seas_full, tas_bbox)
)

# ─────────────────────────────────────────────
# 3. Create MAIN MAP - Tasmania Study Area (Large, Detailed)
# ─────────────────────────────────────────────

main_map_tasmania <- ggplot() +
  # High seas background
  geom_sf(data = high_seas_tas, aes(fill = "high seas"), alpha = 0.2, color = NA) +
  
  # Commonwealth waters
  geom_sf(data = commonwealth_tas, aes(fill = "Commonwealth waters"), alpha = 0.3, color = NA) +
  
  # State waters
  geom_sf(data = state_waters_tas, aes(fill = "state waters"), alpha = 0.3, color = NA) +
  
  # Land areas
  geom_sf(data = terrestrial_tas, aes(fill = "Land"), alpha = 0.8, color = "#636363", size = 0.2) +
  
  # Finfish farms - very prominent in main map
  geom_sf(data = finfish_farms, aes(fill = "Finfish farms"), alpha = 1.0, color = "#E41A1C", size = 6) +
  
  # Tasmania study area boundary - prominent border
  geom_sf(data = tas_study_box, aes(color = "Tasmania Study Area"), fill = "transparent", size = 4) +
  
  scale_fill_manual(
    name = "Map Legend",
    values = colors,
    guide = guide_legend(
      override.aes = list(alpha = c(0.3, 1.0, 0.2, 0.8, 0.3), color = "black", size = 2)
    )
  ) +
  
  scale_color_manual(
    name = "",
    values = c("Tasmania Study Area" = "#0F52BA"),
    guide = guide_legend(
      override.aes = list(fill = NA, color = "#0F52BA", size = 3, linetype = "solid")
    )
  ) +
  
  theme_void() +
  theme(
    legend.position = c(0.02, 0.02),     # Bottom left
    legend.justification = c(0, 0),
    legend.background = element_rect(fill = "white", color = "black", size = 0.5),
    legend.margin = margin(5, 5, 5, 5),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 10),
    plot.margin = margin(5, 5, 5, 5),
    plot.title = element_text(size = 16, face = "bold", hjust = 0.5)
  ) +
  
  coord_sf(
    expand = FALSE,
    xlim = c(tas_bbox["xmin"] - tas_buffer, tas_bbox["xmax"] + tas_buffer),
    ylim = c(tas_bbox["ymin"] - tas_buffer, tas_bbox["ymax"] + tas_buffer)
  ) 
  
  #labs(title = "Tasmania Study Area - Marine Zones and Finfish Farms")

# ─────────────────────────────────────────────
# 4. Create INSET MAP - Australia Overview (Small, Context)
# ─────────────────────────────────────────────

inset_map_australia <- ggplot() +
  # High seas background
  geom_sf(data = high_seas_full, fill = "#CCEBC5", alpha = 0.3, color = NA) +
  
  # Land areas
  geom_sf(data = terrestrial_full, fill = "#636363", alpha = 0.8, color = "black", size = 0.1) +
  
  # Commonwealth waters
  geom_sf(data = commonwealth_full, fill = "#80B1D3", alpha = 0.4, color = NA) +
  
  # State waters
  geom_sf(data = state_waters_full, fill = "#2E7D32", alpha = 0.4, color = NA) +
  
  # Tasmania study area - highlighted box for context
  geom_sf(data = tas_study_box, fill = "transparent", color = "#0F52BA", size = 2) +
  
  theme_void() +
  theme(
    panel.background = element_rect(fill = "white", color = "black", size = 1),
    plot.background = element_rect(fill = "white", color = "black", size = 1),
    plot.margin = margin(2, 2, 2, 2),
    plot.title = element_text(size = 10, hjust = 0.5, face = "bold")
  ) +
  
  coord_sf(expand = FALSE) 
  
  #labs(title = "Australia Context")

# ─────────────────────────────────────────────
# 5. Function to combine Tasmania main map with Australia inset
# ─────────────────────────────────────────────

create_publication_map <- function() {
  ggdraw() +
    draw_plot(main_map_tasmania) +
    draw_plot(inset_map_australia, x = 0.7, y = 0.7, width = 0.28, height = 0.28)
}

# ─────────────────────────────────────────────
# 6. Save maps following publication standards
# ─────────────────────────────────────────────

if (!dir.exists(here("Figures"))) dir.create(here("Figures"))

# Save Tasmania main map
cat("Saving Tasmania main map...\n")
ggsave(
  filename = here("Figures", "Tasmania_Main_Map_Publication.png"),
  plot = main_map_tasmania,
  width = 12,
  height = 10,
  dpi = 300,
  bg = "white"
)

# Save Australia context inset
cat("Saving Australia context inset...\n")
ggsave(
  filename = here("Figures", "Australia_Context_Inset.png"),
  plot = inset_map_australia,
  width = 6,
  height = 5,
  dpi = 300,
  bg = "white"
)

# Save publication-quality combined map
cat("Saving publication-quality combined map...\n")
publication_map <- create_publication_map()
ggsave(
  filename = here("Figures", "Tasmania_Publication_Map_with_Australia_Inset.png"),
  plot = publication_map,
  width = 12,
  height = 10,
  dpi = 300,
  bg = "white"
)

cat("Publication-quality maps saved successfully!\n")

# Display the maps
print("Tasmania main map:")
print(main_map_tasmania)
print("Publication map with Australia inset:")
print(publication_map)
```
#BUBBLE FLIPPED APPROACH

```{r}
# TASMANIA MAP WITH BUBBLE FINFISH FARMS
```{r}
# Load required libraries
library(sf)
library(dplyr)
library(here)
library(ggplot2)
library(cowplot)

cat("Creating Tasmania map with bubble finfish farms...\n")

# ─────────────────────────────────────────────
# 1. Define colors and create Tasmania variables
# ─────────────────────────────────────────────

colors <- c(
  "high seas" = "#CCEBC5",
  "Land" = "#636363", 
  "Commonwealth waters" = "#80B1D3",
  "state waters" = "#2E7D32",
  "Finfish farms" = "#E41A1C"
)

# Create Tasmania study area bounding box
tas_study_box <- st_bbox(c(
  xmin = 140.995, xmax = 153.005, 
  ymin = -47.255, ymax = -38.995
)) %>%
  st_as_sfc() %>%
  st_set_crs(4326) %>%
  st_transform(3577) %>%
  st_sf()

# Define Tasmania extent variables
tas_bbox <- st_bbox(tas_study_box)
tas_buffer <- 50000  # 50km buffer around Tasmania study area

# ─────────────────────────────────────────────
# 2. Create Tasmania extent for cropping data
# ─────────────────────────────────────────────

tas_extent <- st_polygon(list(cbind(
  c(tas_bbox["xmin"] - tas_buffer, tas_bbox["xmax"] + tas_buffer, 
    tas_bbox["xmax"] + tas_buffer, tas_bbox["xmin"] - tas_buffer, 
    tas_bbox["xmin"] - tas_buffer),
  c(tas_bbox["ymin"] - tas_buffer, tas_bbox["ymin"] - tas_buffer, 
    tas_bbox["ymax"] + tas_buffer, tas_bbox["ymax"] + tas_buffer, 
    tas_bbox["ymin"] - tas_buffer)
))) %>%
  st_sfc(crs = 3577) %>%
  st_sf()

# Crop data to Tasmania region
terrestrial_tas <- tryCatch(
  st_intersection(terrestrial_full, tas_extent),
  error = function(e) st_crop(terrestrial_full, tas_bbox)
)

commonwealth_tas <- tryCatch(
  st_intersection(commonwealth_full, tas_extent),
  error = function(e) st_crop(commonwealth_full, tas_bbox)
)

state_waters_tas <- tryCatch(
  st_intersection(state_waters_full, tas_extent),
  error = function(e) st_crop(state_waters_full, tas_bbox)
)

high_seas_tas <- tryCatch(
  st_intersection(high_seas_full, tas_extent),
  error = function(e) st_crop(high_seas_full, tas_bbox)
)

# ─────────────────────────────────────────────
# 3. Prepare finfish farms for bubble plotting
# ─────────────────────────────────────────────

# Convert finfish farms to centroids (points) for bubble plotting
finfish_centroids <- st_centroid(finfish_farms)

# You can also add a size variable if you want different sized bubbles
# For example, if you have area data:
# finfish_centroids$bubble_size <- sqrt(st_area(finfish_farms)) / 1000  # Scale as needed


# ─────────────────────────────────────────────
# 4. Create MAIN MAP - Tasmania Study Area with Bubble Farms
# ─────────────────────────────────────────────

main_map_tasmania <- ggplot() +
  # High seas background
  geom_sf(data = high_seas_tas, aes(fill = "high seas"), alpha = 0.2, color = NA) +
  
  # Commonwealth waters
  geom_sf(data = commonwealth_tas, aes(fill = "Commonwealth waters"), alpha = 0.3, color = NA) +
  
  # State waters
  geom_sf(data = state_waters_tas, aes(fill = "state waters"), alpha = 0.3, color = NA) +
  
  # Land areas
  geom_sf(data = terrestrial_tas, aes(fill = "Land"), alpha = 0.8, color = "#636363", size = 0.2) +
  
  # Finfish farms as BUBBLES - much more visible!
  geom_sf(data = finfish_centroids, 
          aes(fill = "Finfish farms"),
          shape = 21,           # Circle shape
          size = 2,             # Bubble size
          color = "black",      # Black outline
          stroke = 1.5,         # Outline thickness
          alpha = 0.9) +
  
  # Tasmania study area boundary - prominent border
  geom_sf(data = tas_study_box, aes(color = "Tasmania Study Area"), fill = "transparent", size = 4) +
  
  scale_fill_manual(
    name = "Map Legend",
    values = colors,
    guide = guide_legend(
      override.aes = list(
        alpha = c(0.3, 1.0, 0.3, 0.8, 0.3), 
        color = c("black", "black", "black", "black", "black"), 
        size = c(2, 2, 2, 2, 5),
        shape = c(22, 22, 22, 22, 21)  # Circles for finfish farms
      )
    )
  ) +
  
  scale_color_manual(
    name = "",
    values = c("Tasmania Study Area" = "#0F52BA"),
    guide = guide_legend(
      override.aes = list(fill = NA, color = "#0F52BA", size = 3, linetype = "solid")
    )
  ) +
  
  theme_void() +
  theme(
    legend.position = c(0.02, 0.02),
    legend.justification = c(0, 0),
    legend.background = element_rect(fill = "white", color = "black", size = 0.5),
    legend.margin = margin(5, 5, 5, 5),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 10),
    plot.margin = margin(5, 5, 5, 5)
  ) +
  
  coord_sf(
    expand = FALSE,
    xlim = c(tas_bbox["xmin"] - tas_buffer, tas_bbox["xmax"] + tas_buffer),
    ylim = c(tas_bbox["ymin"] - tas_buffer, tas_bbox["ymax"] + tas_buffer)
  )

# ─────────────────────────────────────────────
# 5. Create INSET MAP - Australia Overview
# ─────────────────────────────────────────────

inset_map_australia <- ggplot() +
  # High seas background
  geom_sf(data = high_seas_full, fill = "#CCEBC5", alpha = 0.3, color = NA) +
  
  # Land areas
  geom_sf(data = terrestrial_full, fill = "#636363", alpha = 0.8, color = "black", size = 0.1) +
  
  # Commonwealth waters
  geom_sf(data = commonwealth_full, fill = "#80B1D3", alpha = 0.4, color = NA) +
  
  # State waters
  geom_sf(data = state_waters_full, fill = "#2E7D32", alpha = 0.4, color = NA) +
  
  # Finfish farms as small bubbles in inset
  geom_sf(data = finfish_centroids, 
          fill = "#E41A1C",
          shape = 21,
          size = 0.4,            # Smaller in inset
          color = "black",
          stroke = 0.5,
          alpha = 0.9) +
  
  # Tasmania study area - highlighted box for context
  geom_sf(data = tas_study_box, fill = "transparent", color = "#0F52BA", size = 2) +
  
  theme_void() +
  theme(
    panel.background = element_rect(fill = "white", color = "black", size = 1),
    plot.background = element_rect(fill = "white", color = "black", size = 1),
    plot.margin = margin(2, 2, 2, 2)
  ) +
  
  coord_sf(expand = FALSE)

# ─────────────────────────────────────────────
# 6. Function to combine maps
# ─────────────────────────────────────────────

create_publication_map <- function() {
  ggdraw() +
    draw_plot(main_map_tasmania) +
    draw_plot(inset_map_australia, x = 0.7, y = 0.7, width = 0.28, height = 0.28)
}

# ─────────────────────────────────────────────
# 7. Save maps
# ─────────────────────────────────────────────

if (!dir.exists(here("Figures"))) dir.create(here("Figures"))

# Save Tasmania main map
cat("Saving Tasmania main map with bubble farms...\n")
ggsave(
  filename = here("Figures", "Tasmania_Main_Map_Bubble_Farms_Final.png"),
  plot = main_map_tasmania,
  width = 12,
  height = 10,
  dpi = 300,
  bg = "white"
)

# Save Australia context inset
cat("Saving Australia context inset with bubble farms...\n")
ggsave(
  filename = here("Figures", "Australia_Context_Inset_Bubble_Farms.png"),
  plot = inset_map_australia,
  width = 6,
  height = 5,
  dpi = 300,
  bg = "white"
)

# Save publication-quality combined map
cat("Saving publication map with bubble farms...\n")
publication_map <- create_publication_map()
ggsave(
  filename = here("Figures", "Tasmania_Publication_Final_Bubble_Farms.png"),
  plot = publication_map,
  width = 12,
  height = 10,
  dpi = 300,
  bg = "white"
)

cat("Bubble farm maps saved successfully!\n")

# Display the maps
print("Tasmania main map with bubble farms:")
print(main_map_tasmania)
print("Publication map:")
print(publication_map)
```

