---
title: "9_A_Values_historical_aquacultrure_sites_reproj"
date: 1st version "2024-11-21" this version"2025-10-27"
author: Marina Christofidis (marina.christofidis@griffithuni.edu.au)

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}

library(here)
library(terra)
library(tidyverse)
library(rasterVis)
library(here)
library(dplyr)
library(purrr)
library(stringr)
library(readr)
library(tmap)
library(leaflet)
library(sf)
```

#lets check amount of days per decade over 17C on aquaculture sites that had mortalities and the ones that didnt 

```{r}
daysover_17C_historical<- read_rds(here("raw_data/Data17/jplMUR41_daysover_17C_TAS_20110101-20201231.rds")) %>%
  unwrap()
plot(daysover_17C_historical)
```
#Where are the aquaculture sites today ?and how are they in terms of days over 17C a decade?
```{r}
finfish_aqua_TAS<-vect("D:/Documents_HD/USC_Climate_smart_aquaculture/R_Code/raw_data/TasmanianAquaculture_FinFisheries/TasmanianAquaculture_FinFisheries.shp")
```

```{r}
finfish_aqua_TAS_reproj<-project(finfish_aqua_TAS, daysover_17C_historical)
```

```{r}
finfish_aqua_TAS_sf <- st_as_sf(finfish_aqua_TAS_reproj)
```
```{r}
finfish_aqua_TAS_df<- as.data.frame(finfish_aqua_TAS_reproj, xy= TRUE)
```


#and how are the aquaculture sites in terms of days over 17C a decade?
#extract worked while intersect didnt 
```{r}
aqua_farms_daysover17C<-intersect(daysover_17C_historical, finfish_aqua_TAS_reproj)
aqua_farms_daysover17C_ex<- terra::extract(daysover_17C_historical, finfish_aqua_TAS_reproj)
```

```{r}
aqua_farms_daysover17C_exloc<- terra::extract(daysover_17C_historical, finfish_aqua_TAS_reproj, xy= TRUE)
```


```{r}
sf_extract_aqua_farms_daysover17C<-st_as_sf(aqua_farms_daysover17C_exloc, coords = c("x", "y"), crs = 4326) # Assuming WGS84 (EPSG:4326)
```

```{r}
tmap_mode("view")
```

```{r}
tm_shape(sf_extract_aqua_farms_daysover17C) +
  tm_dots(col = "X201", size = 0.1, palette = "viridis", title = "number of days over 17C in a decade") +
  tm_basemap("OpenStreetMap") +
  tm_layout(title = "Historical days over 17C", legend.outside = TRUE)
```


```{r}
qtm(daysover_17C_historical, "Esri.WorldImagery")
```

```{r}
tmap_mode("view")
```


```{r}

qtm(daysover_17C_historical, basemaps = "Esri.WorldImagery")+
  qtm(finfish_aqua_TAS_sf)
  
```
#avalilable styles for this kind of map: 
#"cont": continuous values.
#"fixed": Define your own custom breaks explicitly.
#"equal": Equal-width intervals across the range of values.
#"pretty": R creates "nice-looking" rounded breaks.
#"quantile": Each category has an equal number of data points.
#"jenks": Uses natural breaks (optimized for data distribution).
#"hclust", "kmeans", etc.: More advanced clustering-based methods.

```{r}
# Create the map with customized legend breaks
tm_shape(daysover_17C_historical) +
  tm_raster(style = "cont", breaks = seq(min(daysover_17C_historical[], na.rm = TRUE), 
                                         max(daysover_17C_historical[], na.rm = TRUE), 
                                         length.out = 20), 
            title = "Days Over 17°C") +
  tm_shape(finfish_aqua_TAS_sf) +
  tm_borders(col = "black") +
  tm_basemap("Esri.WorldImagery")
```

#other types of breaks
# Create the map with customized legend breaks
```{r}
tm_shape(daysover_17C_historical) +
  tm_raster(style = "fixed", breaks = seq(min(daysover_17C_historical[], na.rm = TRUE), 
                                         max(daysover_17C_historical[], na.rm = TRUE), 
                                         length.out = 20), 
            title = "Days Over 17°C") +
  tm_shape(finfish_aqua_TAS_sf) +
  tm_borders(col = "black") +
  tm_basemap("Esri.WorldImagery")
```

#lets check amount of days per decade over 21C on aquaculture sites that had mortalities and the ones that didnt 
```{r}
daysover_21.5C_historical<- read_rds(here("raw_data/Data/jplMUR41_daysover_21.5C_TAS_20110101-20201231.rds")) %>%
  unwrap()
plot(daysover_21.5C_historical)
```
#and how are the aquaculture sites in terms of days over 21.5C a decade?
# I dont understand why it comes as zero, that means the finfish is not on areas we have information on? 
```{r}
aqua_farms_daysover21.5C<-intersect(daysover_21.5C_historical, finfish_aqua_TAS_sf)
```


```{r}
qtm(daysover_21.5C_historical, basemaps = "Esri.WorldImagery")+
  qtm(finfish_aqua_TAS_sf)
```

# Create the map with customized legend breaks for 21.5C
```{r}
tm_shape(daysover_21.5C_historical) +
  tm_raster(style = "fixed", breaks = seq(min(daysover_21.5C_historical[], na.rm = TRUE), 
                                         max(daysover_21.5C_historical[], na.rm = TRUE), 
                                         length.out = 20), 
            title = "Days Over 21.5°C") +
  tm_shape(finfish_aqua_TAS_sf) +
  tm_borders(col = "black") +
  tm_basemap("Esri.WorldImagery")
```
#equal
```{r}
tm_shape(daysover_17C_historical) +
  tm_raster(style = "equal", breaks = seq(min(daysover_17C_historical[], na.rm = TRUE), 
                                         max(daysover_17C_historical[], na.rm = TRUE), 
                                         length.out = 20), 
            title = "Days Over 17°C") +
  tm_shape(finfish_aqua_TAS_sf) +
  tm_borders(col = "black") +
  tm_basemap("Esri.WorldImagery")
```


# Go to code 9_B_Reclass_17C_EF_Oct25 and 9_C_Reclass_21C_EF_Oct25
